---
title: "Regressions"
author: "Helena Davies"
date: "24/05/2021"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-09-27.rds")
dim(dat)
   colnames(dat)
   
   
dat %>% 
     group_by(ID) %>%
     filter(n()>1)
```

```{r change panworry to factor}
dat <- dat %>%
  mutate(panworry_factor =
           case_when(panworry_total_score > -1 &
                       panworry_total_score <= 20 ~ "0-20",
             
                     panworry_total_score > 20 &
                       panworry_total_score <= 40 ~ "21-40",
                     
                     panworry_total_score > 40 &
                      panworry_total_score <= 60 ~ "41-60",
                     
                      panworry_total_score > 60 &
                      panworry_total_score <= 80 ~ "61-80"
                     )
         )
```

### Re-ordering variables / converting to factors
First, re-order all variables to get desired reference category for plotting - put largest category as reference
Age
```{r Re-order age levels}
dat <- dat %>%
  mutate(age_category_COVID_baseline = factor(age_category_COVID_baseline,
                       levels = c("46-55", # Mid-life
                                   "16-25",
                                  "26-35",
                                  "36-45",
                                  "56-65", 
                                   "66-70",
                                   "71+")
                       )
         )

# Check
dat %>%
  freq(age_category_COVID_baseline)
```

Race
```{r Re-order race levels}
dat <- dat %>%
  mutate(race_binary = factor(race_binary,
                       levels = c("White", # Largest category
                                  "Racially minoritised"
                                  )))
dat %>%
  freq(race_binary)
```

Psychiatric disorder
```{r  Re-order psych disorder levels}
# First recode to "Yes" and "No"
dat <- dat %>%
  mutate(psych_disorder_factor =
           case_when(
            mental_health_diagnosis == "Psychiatric disorder" ~ "Yes", 
            mental_health_diagnosis == "No psychiatric disorder" ~ "No")
  )

# Check 
dat %>%
  freq(psych_disorder_factor)

# Then change order
dat <- dat %>%
  mutate(psych_disorder_factor = factor(psych_disorder_factor,
                       levels = c( "No", # Ref category
                                  "Yes"
                                  )))

# Check again
dat %>%
  freq(psych_disorder_factor)
```

Employment
```{r Re-order employment levels}
dat <- dat%>%
  mutate(paid_employment_key_worker = factor(paid_employment_key_worker,
                       levels = c("Paid employment",  
                                  "Key worker",
                                  "Not paid employment",
                                  "Retired",
                                  "Student"
                                  )
                       )
         )

# Check
dat %>%
  freq(paid_employment_key_worker)
```

# REGRESSION MODELS
## Binge eating
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation

Pandemic worry: If you include a continuous predictor in your logistic regression, the exponentiated coefficient represents the odds ratio for one unit change in the predictor. Often, one unit isn't meaningful and you want the odds ratio for, say, 10 units. To calculate this, just exponentiate the coefficient multiplied by 10: 𝑂𝑅10=exp(𝛽⋅10). 
```{r Binge eating age model}
model_age <- glm(NEW_binge_eating_pandemic ~  
                 age_category_COVID_baseline,
                 data = dat,
                 family = "binomial"
              )

binge_eating_age <- tidy(model_age,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_age) %>% 
  length()
```

```{r Binge eating sex extended model}
model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()
```

```{r Binge eating gender model}
model_gender <- glm(NEW_binge_eating_pandemic ~  
               minoritised_gender +
                   age_category_COVID_baseline,
                 data = dat,
                 family = "binomial"
              )

binge_eating_gender <- tidy(model_gender,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_gender) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_gender)
```

```{r Binge eating psych disorder model}
model_psych_disorder <- glm(NEW_binge_eating_pandemic ~  psych_disorder_factor +
              age_category_COVID_baseline +
                 sex_binary +
                 minoritised_gender +
                 race_binary +
                 paid_employment_key_worker + # also mediator?
                 vulnerable_group_member +
                 panworry_factor + # also mediator?
                 increased_loneliness_during_pandemic +  # also mediator?
                 positive_covid_test_before_BE_final +
                 lost_someone_before_BE_final +
                 main_eco_change_before_BE_final + # also mediator?
                 living_situation_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_psych_disorder <- tidy(model_psych_disorder,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_psych_disorder) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_psych_disorder)
```

```{r Binge eating employment model}
model_employment <- glm(NEW_binge_eating_pandemic ~ paid_employment_key_worker + 
                          age_category_COVID_baseline +
                 sex_binary +
                 race_binary +
                 vulnerable_group_member +
                 panworry_factor + # also mediator?
                 positive_covid_test_before_BE_final +
                 main_eco_change_before_BE_final + # also mediator?
                 living_situation_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_employment <- tidy(model_employment,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_employment) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_employment)
```

```{r Binge eating vulnerable group member model}
model_vulnerable_group_member <- glm(NEW_binge_eating_pandemic ~ vulnerable_group_member + 
                          age_category_COVID_baseline +
                 sex_binary,
                 data = dat,
                 family = "binomial"
              )

binge_eating_vulnerable_group_member <- tidy(model_vulnerable_group_member,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_vulnerable_group_member) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_vulnerable_group_member)
```

```{r Binge eating pandemic worry model}
model_panworry <- glm(NEW_binge_eating_pandemic ~ panworry_factor + 
                          age_category_COVID_baseline +
                   sex_binary +
                     race_binary +
                   psych_disorder_factor +
                   paid_employment_key_worker +
                   vulnerable_group_member +
                   increased_loneliness_during_pandemic + # also mediator?
                   positive_covid_test_before_BE_final + # also mediator?
                   lost_someone_before_BE_final + 
                   main_eco_change_before_BE_final + # also mediator?
                 living_situation_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_panworry <- tidy(model_panworry,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_panworry) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_panworry)
```

```{r Binge eating loneliness model}
model_loneliness <- glm(NEW_binge_eating_pandemic ~ increased_loneliness_during_pandemic +
                          age_category_COVID_baseline +
                   sex_binary +
                     race_binary +
                   psych_disorder_factor +
                   paid_employment_key_worker +
                   vulnerable_group_member +
                   panworry_factor +   # also mediator?
                   positive_covid_test_before_BE_final + 
                   lost_someone_before_BE_final + 
                   main_eco_change_before_BE_final + 
                 living_situation_change_before_BE_final, 
                 data = dat,
                 family = "binomial"
              )

binge_eating_loneliness <- tidy(model_loneliness,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_loneliness) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_loneliness)
```

```{r Binge eating lost someone model}
model_loss <- glm(NEW_binge_eating_pandemic ~ lost_someone_before_BE_final + 
                   age_category_COVID_baseline +
                   sex_binary +
                   race_binary +
                   vulnerable_group_member,
                 data = dat,
                 family = "binomial"
              )

binge_eating_loss <- tidy(model_loss,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_loss) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_loss)
```

```{r Binge eating main eco change model}
model_main_eco_change <- glm(NEW_binge_eating_pandemic ~ main_eco_change_before_BE_final + 
                   age_category_COVID_baseline +
                 sex_binary +
                 race_binary +
                 psych_disorder_factor + # also mediator?
                 paid_employment_key_worker + # also mediator?
                 vulnerable_group_member +
                 panworry_factor + # also mediator?
                 positive_covid_test_before_BE_final + # also mediator?
                 living_situation_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_main_eco_change <- tidy(model_main_eco_change,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_main_eco_change) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_main_eco_change)
```

```{r Binge eating living situation change model}
model_living_sit_change <- glm(NEW_binge_eating_pandemic ~ living_situation_change_before_BE_final +
                 age_category_COVID_baseline +
                 sex_binary +
                 race_binary +
                 psych_disorder_factor + # also mediator?
                 paid_employment_key_worker + # also mediator?
                 vulnerable_group_member +
                 panworry_factor + # also mediator?
                  main_eco_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_living_sit_change <- tidy(model_living_sit_change,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_living_sit_change) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_living_sit_change)
```

```{r Binge eating COVID19 illness model}
model_COVID19_illness <- glm(NEW_binge_eating_pandemic ~  positive_covid_test_before_BE_final +
                 age_category_COVID_baseline +
                 sex_binary +
                 race_binary +
                 paid_employment_key_worker + # also mediator?
                 vulnerable_group_member +
                 panworry_factor + # also mediator?
                 main_eco_change_before_BE_final + # also mediator?
                 living_situation_change_before_BE_final, # also mediator?
                 data = dat,
                 family = "binomial"
              )

binge_eating_COVID19_illness <- tidy(model_COVID19_illness,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_COVID19_illness) %>% 
  length()
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF binge eating}
car::vif(model_COVID19_illness)
```

Plot
```{r}
# Enter labels
boxLabels = c("Age: 16-25 years",
              "Age: 26-35 years",
              "Age: 36-45 years",
              "Age: 66-70 years",
              "Age: 71+ years")

# Enter OR and CI data. boxOdds are the odds ratios, 
# boxCILow is the lower bound of the CI, boxCIHigh is the upper bound.

df <- data.frame(yAxis = length(boxLabels):1,
                 boxOdds = c(0.9965588, 
                             0.9488022,
                             1.0084248,
                             0.6191922,
                             0.5265286),
                 boxCILow = c(0.8762611,
                             0.8467316,
                             0.9046767,
                             0.5494629,
                             0.4639614),
                 boxCIHigh = c(1.1318566, 
                               1.0623680,
                               1.1234824,
                               0.6968718,
                               0.5964766
                               ))

# Plot
p <- ggplot(df,
            aes(x = boxOdds,
                y = boxLabels)
            ) 

p <- ggplot(df,
             aes(x = boxOdds,
                 y = boxLabels)) + 
    geom_vline(aes(xintercept = 1),
               size = .25,
               linetype = "dashed") + 
    geom_errorbarh(aes(xmax = boxCIHigh,
                       xmin = boxCILow),
                   size = .5,
                   height = .2,
                   color = "gray50") +
    geom_point(size = 3.5,
               color = "orange") +
    scale_x_continuous(breaks = seq(from = 0.4,
                                         to = 1.2,
                                         by = 0.1), 
                       labels = seq(0.4,
                                    1.2,
                                    0.1),
                       limits = c(0.4,
                                  1.2)) +
    theme_bw()+
    theme(panel.grid.minor = element_blank()) +
    ylab("") +
    xlab("Odds ratio") + 
    ggtitle("New onset binge eating during the pandemic")

p
```







```{r Binge eating extended model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Sex" = "sex_binary",
         "Minoritised_gender" = "minoritised_gender",
         "Race" = "race_binary",
         "New_onset_binge_eating" = "NEW_binge_eating_pandemic",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_factor",
         "Pandemic_loneliness" = "increased_loneliness_during_pandemic",
         "COVID19_illness_or_positive_test" = "positive_covid_test_before_BE_final", 
         "Loss_due_to_COVID19" = "lost_someone_before_BE_final", 
         "Change_in_main_eco_activity" = "main_eco_change_before_BE_final", 
         "Change_in_living_situation" = "living_situation_change_before_BE_final" 
        )


# 1. Plot
explanatory <- c("Age",
                 "Sex",
                 "Minoritised_gender",
                 "Race",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "Pandemic_loneliness",
                 "COVID19_illness_or_positive_test",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation"
               )

dependent <- "New_onset_binge_eating"

BE_extended_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent,
                    explanatory, 
          breaks = c(0.5, 1, 5),
          table_text_size = 3.5,
          title_text_size = 15,
          dependent_label = "New onset binge eating during pandemic",
          remove_ref = FALSE,
            plot_opts=list(geom_point(aes(size = Total), shape=22, fill="white"),
                   geom_errorbarh(height=0.2)
    )
  )
```

```{r Save BE extended level plot}
ggsave(
  paste0("BE_extended_dat_plot",
                    date,
                    ".png"),
  plot = BE_extended_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_main_regressions), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Low weight 
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation
```{r Low weight extended model}
model2 <- glm(NEW_low_weight_pandemic ~ 
                age_category_COVID_baseline +
                sex_binary +
                 minoritised_gender +
                 race_binary +
                 psych_disorder_factor +
                 paid_employment_key_worker +
                 vulnerable_group_member +
                 panworry_factor + 
                 increased_loneliness_during_pandemic + 
                 positive_covid_test_before_LW_final + 
                 lost_someone_before_LW_final + 
                 main_eco_change_before_LW_final + 
                 living_situation_change_before_LW_final,
                 data = dat,
                 family = "binomial")

low_weight_main <- tidy(model2,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model2) %>% 
  length()

# Pseudo R2
DescTools::PseudoR2(model2, which = "McFadden")
DescTools::PseudoR2(model2, which = "McFaddenAdj")
DescTools::PseudoR2(model2, which = "Nagelkerke")
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF low weight}
car::vif(model2)
```

Plot
```{r Low weight extended model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
          "Sex" = "sex_binary",
         "Minoritised_gender" = "minoritised_gender",
         "Race" = "race_binary",
         "New_onset_low_weight" = "NEW_low_weight_pandemic",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_factor",
         "Pandemic_loneliness" = "increased_loneliness_during_pandemic",
         "COVID19_illness_or_positive_test" = "positive_covid_test_before_LW_final",
         "Loss_due_to_COVID19" = "lost_someone_before_LW_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_LW_final",
         "Change_in_living_situation" = "living_situation_change_before_LW_final"
        )
       
# 1. Plot
explanatory <- c("Age",
                 "Sex",
                 "Minoritised_gender",
                 "Race",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "Pandemic_loneliness",
                 "COVID19_illness_or_positive_test",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation"
               )

dependent <- "New_onset_low_weight"

LW_extended_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent,
                    explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.5,
          title_text_size = 15,
          dependent_label = "New onset low weight during pandemic",
          remove_ref = FALSE,
            plot_opts=list(geom_point(aes(size = Total), shape=22, fill="white"),
                   geom_errorbarh(height=0.2)
    )
  )
```

```{r}
f <- dat %>%
  filter(!is.na(age_category_COVID_baseline) &
         !is.na(sex_binary) &
         !is.na(minoritised_gender) &
         !is.na(race_binary) &
         !is.na(NEW_low_weight_pandemic) &
         !is.na(psych_disorder_factor) &
         !is.na(paid_employment_key_worker) &
         !is.na(vulnerable_group_member) &
         !is.na(panworry_total_score) &
         !is.na(increased_loneliness_during_pandemic) &
         !is.na(positive_covid_test_before_LW_final) &
         !is.na(lost_someone_before_LW_final) &
         !is.na(main_eco_change_before_LW_final) &
         !is.na(living_situation_change_before_LW_final)
        )


f %>%
  group_by(NEW_low_weight_pandemic) %>%
  freq(sex_binary)
```







```{r Save LW extended level plot}
ggsave(
  paste0("LW_extended_dat_plot",
                    date,
                    ".png"),
  plot = LW_extended_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_main_regressions), 
   scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Self-harm/suicidal ideation 
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation
```{r Harmful ideation extended model}
model3 <- glm(NEW_harmful_ideation_pandemic ~ age_category_COVID_baseline + 
                   sex_binary +
                 minoritised_gender +
                 race_binary + 
                 psych_disorder_factor + 
                 paid_employment_key_worker + 
                 vulnerable_group_member + 
                 panworry_factor + 
                increased_loneliness_during_pandemic + 
                 positive_covid_test_before_HI_final + 
                 lost_someone_before_HI_final + 
                 main_eco_change_before_HI_final +
                 living_situation_change_before_HI_final,
                 data = dat,
                 family = "binomial")

harmful_ideation_main <- tidy(model3,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model3) %>% 
  length()

# Psuedo R2
DescTools::PseudoR2(model3, which = "McFadden")
DescTools::PseudoR2(model3, which = "McFaddenAdj")
DescTools::PseudoR2(model3, which = "Nagelkerke")
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF low weight}
car::vif(model3)
```

Plot
```{r Harmful ideation extended model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
           "Sex" = "sex_binary",
         "Minoritised_gender" = "minoritised_gender",
         "Race" = "race_binary",
         "New_onset_suicidal_selfharm_ideation" = "NEW_harmful_ideation_pandemic",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_factor",
         "Pandemic_loneliness" = "increased_loneliness_during_pandemic",
         "COVID19_illness_or_positive_test" = "positive_covid_test_before_HI_final",
         "Loss_due_to_COVID19" = "lost_someone_before_HI_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_HI_final",
         "Change_in_living_situation" = "living_situation_change_before_HI_final"
         
        )

# 1. Plot
explanatory <- c("Age",
                 "Sex",
                 "Minoritised_gender",
                 "Race",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "Pandemic_loneliness",
                 "COVID19_illness_or_positive_test",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation")

dependent <- "New_onset_suicidal_selfharm_ideation"

HI_extended_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
           table_text_size = 3.5,
          title_text_size = 13,
          dependent_label = "New onset suicidal and/or self-harm ideation during pandemic",
           remove_ref = FALSE,
          plot_opts=list(geom_point(aes(size = Total), shape=22, fill="white"),
                   geom_errorbarh(height=0.2)
    )
  ) 
```

```{r Save HI extended level plot}
ggsave(
  paste0("HI_extended_dat_plot",
                    date,
                    ".png"),
  plot = HI_extended_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_main_regressions), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Self-harm
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation
```{r Self-harm extended model}
model4 <- glm(NEW_selfharm_pandemic ~ age_category_COVID_baseline + 
                 sex_binary +
                 minoritised_gender +
                 race_binary + 
                 psych_disorder_factor + 
                 paid_employment_key_worker + 
                 vulnerable_group_member + 
                 panworry_factor + 
                 increased_loneliness_during_pandemic + 
                 positive_covid_test_before_SH_final + 
                 lost_someone_before_SH_final + 
                 main_eco_change_before_SH_final +
                 living_situation_change_before_SH_final,
                 data = dat,
                 family = "binomial")

selfharm_main <-  tidy(model4,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model4) %>% 
  length()

# Psuedo R2
DescTools::PseudoR2(model4, which = "McFadden")
DescTools::PseudoR2(model4, which = "McFaddenAdj")
DescTools::PseudoR2(model4, which = "Nagelkerke")
```

Check for Variance inflation factor estimate (VIF) - direct estimate of collinearity in data
```{r check VIF low weight}
car::vif(model4)
```

Plot 
```{r Self-harm extended model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Sex" = "sex_binary",
         "Minoritised_gender" = "minoritised_gender",
         "Race" = "race_binary",
         "New_onset_selfharm" = "NEW_selfharm_pandemic",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_factor",
         "Pandemic_loneliness" = "increased_loneliness_during_pandemic",
         "COVID19_illness_or_positive_test" = "positive_covid_test_before_SH_final",
         "Loss_due_to_COVID19" = "lost_someone_before_SH_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_SH_final",
         "Change_in_living_situation" = "living_situation_change_before_SH_final"
         
        )

#1. Plot
explanatory <- c("Age",
                 "Sex",
                 "Minoritised_gender",
                 "Race",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "Pandemic_loneliness",
                 "COVID19_illness_or_positive_test",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation")

dependent <- "New_onset_selfharm"

SH_extended_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.5,
          title_text_size = 13,
          dependent_label = "New onset self-harm during pandemic",
          remove_ref = FALSE,
          plot_opts=list(geom_point(aes(size = Total), shape=22, fill="white"),
                   geom_errorbarh(height=0.2)
    )
  )
```

```{r Save SH extended level plot}
ggsave(
  paste0("SH_extended_dat_plot",
                    date,
                    ".png"),
  plot = SH_extended_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_main_regressions), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Save environment
Need this to run correlations with OR of other sensitivity analysis (i.e., exposure ONLY before outcome and not in same phase)
```{r save environment}
save.image(file='COVID_main_analysis_regressions.RData')
```

