---
title: 'Sensitivity analysis: Regressions'
author: "Helena Davies"
date: "21/12/2021"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/sens_dat_no_baseline2022-04-28.rds")
dim(dat)
   colnames(dat)
```

### Re-ordering variables / converting to factors
First, re-order all variables to get desired reference category for plotting - put largest category as reference
Age
```{r Re-order age levels}
dat <- dat %>%
  mutate(age_category_COVID_baseline = factor(age_category_COVID_baseline,
                       levels = c("56-65", # Largest category
                                  "16-25",
                                  "26-35",
                                  "36-45",
                                  "46-55",
                                   "66-70",
                                   "71+")
                       )
         )

# Check
dat %>%
  freq(age_category_COVID_baseline)
```

Race
```{r Re-order race levels}
dat <- dat %>%
  mutate(race_binary = factor(race_binary,
                       levels = c("White", # Largest category
                                  "Racially minoritised"
                                  )))
dat %>%
  freq(race_binary)
```

Psychiatric disorder
```{r  Re-order psych disorder levels}
# First recode to "Yes" and "No"
dat <- dat %>%
  mutate(psych_disorder_factor =
           case_when(
            mental_health_diagnosis == "Psychiatric disorder" ~ "Yes", 
            mental_health_diagnosis == "No psychiatric disorder" ~ "No")
  )

# Check 
dat %>%
  freq(psych_disorder_factor)

# Then change order
dat <- dat %>%
  mutate(psych_disorder_factor = factor(psych_disorder_factor,
                       levels = c( "No", # Ref category
                                  "Yes"
                                  )))

# Check again
dat %>%
  freq(psych_disorder_factor)
```

Employment
```{r Re-order employment levels}
dat <- dat%>%
  mutate(paid_employment_key_worker = factor(paid_employment_key_worker,
                       levels = c("Paid employment",  
                                  "Key worker",
                                  "Not paid employment",
                                  "Retired",
                                  "Student"
                                  )
                       )
         )

# Check
dat %>%
  freq(paid_employment_key_worker)
```

# MAIN ANALYSIS MODELS
Adding: Key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, lonelieness, change in main eco activity, change in living situation

## Binge eating
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation

Pandemic worry: If you include a continuous predictor in your logistic regression, the exponentiated coefficient represents the odds ratio for one unit change in the predictor. Often, one unit isn't meaningful and you want the odds ratio for, say, 10 units. To calculate this, just exponentiate the coefficient multiplied by 10: 𝑂𝑅10=exp(𝛽⋅10). 
```{r Binge eating ExpBeforeOut model}
model1 <- glm(sens2_NEW_binge_eating_pandemic ~  
                 age_category_COVID_baseline +
                 gender_cleaned +
                 race_binary +
                 highest_education +
                 psych_disorder_factor +
                 paid_employment_key_worker +
                 vulnerable_group_member +
                 panworry_total_score + 
                 positive_covid_test_before_BE_final +
                 lost_someone_before_BE_final +
                 main_eco_change_before_BE_final +
                 living_situation_change_before_BE_final,
                 data = dat,
                 family = "binomial"
              )

binge_eating_sens2 <- tidy(model1,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model1) %>% 
  length()

# Pseudo R2
DescTools::PseudoR2(model1, which = "McFadden")
DescTools::PseudoR2(model1, which = "McFaddenAdj")
DescTools::PseudoR2(model1, which = "Nagelkerke")
```

Plot
```{r Binge eating ExpBeforeOut model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "race_binary",
         "New_onset_binge_eating" = "sens2_NEW_binge_eating_pandemic",
         "Education" = "highest_education",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_total_score",
         "COVID19_infection" = "positive_covid_test_before_BE_final", 
         "Loss_due_to_COVID19" = "lost_someone_before_BE_final", 
         "Change_in_main_eco_activity" = "main_eco_change_before_BE_final", 
         "Change_in_living_situation" = "living_situation_change_before_BE_final" 
        )


# 1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "COVID19_infection",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation"
               )

dependent <- "New_onset_binge_eating"

BE_ExpBeforeOut_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent,
                    explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.5,
          title_text_size = 15,
          dependent_label = "Sensitivity analysis (exposure before outcome): New onset binge eating during pandemic",
          remove_ref = FALSE) 
```

```{r Save BE ExpBeforeOut level plot}
ggsave(
  paste0("BE_ExpBeforeOut_dat_plot",
                    date,
                    ".png"),
  plot = BE_ExpBeforeOut_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_sensitivity_ExpBeforeOut), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Low weight 
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation, OCD symptoms
```{r Low weight ExpBeforeOut model}
model2 <- glm(sens2_NEW_low_weight_pandemic ~ age_category_COVID_baseline +
                 gender_cleaned +
                 race_binary +
                 highest_education +
                 psych_disorder_factor +
                 paid_employment_key_worker +
                 vulnerable_group_member +
                 panworry_total_score + 
                 positive_covid_test_before_LW_final + 
                 lost_someone_before_LW_final + 
                 main_eco_change_before_LW_final + 
                 living_situation_change_before_LW_final +
                 OCD_symptoms,
                 data = dat,
                 family = "binomial")

low_weight_sens2 <- tidy(model2,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model2) %>% 
  length()

# Pseudo R2
DescTools::PseudoR2(model2, which = "McFadden")
DescTools::PseudoR2(model2, which = "McFaddenAdj")
DescTools::PseudoR2(model2, which = "Nagelkerke")
```

Plot
```{r Low weight ExpBeforeOut model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "race_binary",
         "New_onset_low_weight" = "sens2_NEW_low_weight_pandemic",
         "Education" = "highest_education",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_total_score",
         "COVID19_infection" = "positive_covid_test_before_LW_final",
         "Loss_due_to_COVID19" = "lost_someone_before_LW_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_LW_final",
         "Change_in_living_situation" = "living_situation_change_before_LW_final",
         "OCD_symptoms"
        )
       
# 1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "COVID19_infection",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation",
                 "OCD_symptoms")

dependent <- "New_onset_low_weight"

LW_ExpBeforeOut_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent,
                    explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.5,
          title_text_size = 15,
          dependent_label = "Sensitivity analysis (exposure before outcome): New onset low weight during pandemic",
          remove_ref = FALSE) 
```

```{r Save LW ExpBeforeOut level plot}
ggsave(
  paste0("LW_ExpBeforeOut_dat_plot",
                    date,
                    ".png"),
  plot = LW_ExpBeforeOut_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_sensitivity_ExpBeforeOut), 
   scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Self-harm/suicidal ideation 
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation
```{r Harmful ideation ExpBeforeOut model}
model3 <- glm(sens2_NEW_harmful_ideation_pandemic ~ age_category_COVID_baseline + 
                 gender_cleaned + 
                 race_binary + 
                 highest_education + 
                 psych_disorder_factor + 
                 paid_employment_key_worker + 
                 vulnerable_group_member + 
                 panworry_total_score + 
                 positive_covid_test_before_HI_final + 
                 lost_someone_before_HI_final + 
                 main_eco_change_before_HI_final +
                 living_situation_change_before_HI_final,
                 data = dat,
                 family = "binomial")

harmful_ideation_sens2 <- tidy(model3,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model3) %>% 
  length()

# Psuedo R2
DescTools::PseudoR2(model3, which = "McFadden")
DescTools::PseudoR2(model3, which = "McFaddenAdj")
DescTools::PseudoR2(model3, which = "Nagelkerke")
```

Plot
```{r Harmful ideation ExpBeforeOut model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "race_binary",
         "New_onset_suicidal_selfharm_ideation" = "sens2_NEW_harmful_ideation_pandemic",
         "Education" = "highest_education",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_total_score",
         "COVID19_infection" = "positive_covid_test_before_HI_final",
         "Loss_due_to_COVID19" = "lost_someone_before_HI_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_HI_final",
         "Change_in_living_situation" = "living_situation_change_before_HI_final"
         
        )

# 1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "COVID19_infection",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation")

dependent <- "New_onset_suicidal_selfharm_ideation"

HI_ExpBeforeOut_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
           table_text_size = 3.5,
          title_text_size = 13,
          dependent_label = "Sensitivity analysis (exposure before outcome): New onset suicidal and/or self-harm ideation during pandemic",
           remove_ref = FALSE) 
```

```{r Save HI ExpBeforeOut level plot}
ggsave(
  paste0("HI_ExpBeforeOut_dat_plot",
                    date,
                    ".png"),
  plot = HI_ExpBeforeOut_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_sensitivity_ExpBeforeOut), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Self-harm
Age, gender, race, education, psych disorder, key worker/employment status, vulnerable group member, pandemic worry, positive COVID test, loss of loved one, change in main eco activity, change in living situation
```{r Self-harm ExpBeforeOut model}
model4 <- glm(sens2_NEW_selfharm_pandemic ~ age_category_COVID_baseline + 
                 gender_cleaned + 
                 race_binary + 
                 highest_education + 
                 psych_disorder_factor + 
                 paid_employment_key_worker + 
                 vulnerable_group_member + 
                 panworry_total_score + 
                 positive_covid_test_before_SH_final + 
                 lost_someone_before_SH_final + 
                 main_eco_change_before_SH_final +
                 living_situation_change_before_SH_final,
                 data = dat,
                 family = "binomial")

selfharm_sens2 <-  tidy(model4,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model4) %>% 
  length()

# Psuedo R2
DescTools::PseudoR2(model4, which = "McFadden")
DescTools::PseudoR2(model4, which = "McFaddenAdj")
DescTools::PseudoR2(model4, which = "Nagelkerke")
```

Plot 
```{r Self-harm ExpBeforeOut model plot}
dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "race_binary",
         "New_onset_selfharm" = "sens2_NEW_selfharm_pandemic",
         "Education" = "highest_education",
         "Psychiatric_disorder" = "psych_disorder_factor",
         "Employment_status" = "paid_employment_key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member",
         "Pandemic_worry_score" = "panworry_total_score",
         "COVID19_infection" = "positive_covid_test_before_SH_final",
         "Loss_due_to_COVID19" = "lost_someone_before_SH_final",
         "Change_in_main_eco_activity" = "main_eco_change_before_SH_final",
         "Change_in_living_situation" = "living_situation_change_before_SH_final"
         
        )

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Psychiatric_disorder",
                 "Employment_status",
                 "Vulnerable_group_member",
                 "Pandemic_worry_score",
                 "COVID19_infection",
                 "Loss_due_to_COVID19",
                 "Change_in_main_eco_activity",
                 "Change_in_living_situation")

dependent <- "New_onset_selfharm"

SH_ExpBeforeOut_dat_plot <- dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.5,
          title_text_size = 13,
          dependent_label = "Sensitivity analysis (exposure before outcome): New onset self-harm during pandemic",
          remove_ref = FALSE)
```

```{r Save SH ExpBeforeOut level plot}
ggsave(
  paste0("SH_ExpBeforeOut_dat_plot",
                    date,
                    ".png"),
  plot = SH_ExpBeforeOut_dat_plot,
  device = "png", 
  path = paste0(filepath_plots_sensitivity_ExpBeforeOut), 
  scale = 1,
  width = 25,
  height = 25,
  units = "cm"
  )
```

# Calculate correlation between effect sizes of main and sensitivity analysis (3 no's)
## Load main analysis environment
```{r load main analysis env}
load(file='COVID_main_analysis_regressions.RData')
```

## Low weight
```{r Calculate correlation between effect sizes low weight}
# Extract columns from model - sens analysis
low_weight_sens_extracted <- low_weight_sens2 %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_sens = estimate,
         conf.high_sens = conf.high,
         conf.low_sens = conf.low,
         Exposure = term)

# Check
low_weight_sens_extracted

# Extract columns from model - main analysis
low_weight_extracted <- low_weight_main %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_main = estimate,
         conf.high_main = conf.high,
         conf.low_main = conf.low,
         Exposure = term)

# Check
low_weight_extracted

# Join
low_weight_joined <- merge(x = low_weight_sens_extracted,
                         y = low_weight_extracted,
                         by = "Exposure")


# Check
low_weight_joined

# Summarise ORs
summary(low_weight_joined$estimate_main)
summary(low_weight_joined$estimate_sens)

# Correlation
low_weight_cor <- psych::corr.test(low_weight_joined$estimate_main,
          low_weight_joined$estimate_sens,
          ci = TRUE)

low_weight_cor$r

print(low_weight_cor,
      short=F)
low_weight_joined
```

```{r plot OR correlation low weight}
# Delete intercept row
low_weight_joined <- low_weight_joined[-1, ]

# Rename exposures for plotting
low_weight_joined[1,1] <- "16-25 years (vs. 56-65 years)"
low_weight_joined[2,1] <- "26-35 years (vs. 56-65 years)"
low_weight_joined[3,1] <- "36-45 years (vs. 56-65 years)"
low_weight_joined[4,1] <- "46-55 years (vs. 56-65 years)"
low_weight_joined[5,1] <- "66-70 years (vs. 56-65 years)"
low_weight_joined[6,1] <- "71+ years (vs. 56-65 years)"
low_weight_joined[7,1] <- "Minoritised gender (vs. man)"
low_weight_joined[8,1] <- "Woman (vs. man)"
low_weight_joined[9,1] <- "Highest education: A-levels (vs. no formal education)"
low_weight_joined[10,1] <- "Highest education: GCSE/CSE (vs. no formal education)"
low_weight_joined[11,1] <- "Highest education: NVQ (vs. no formal education)"
low_weight_joined[12,1] <- "Highest education: Uni/Other professional quals (vs. no formal education)"
low_weight_joined[13,1] <- "Change in living situation (vs. not)"
low_weight_joined[14,1] <- "Lost someone due to COVID-19 (vs. not)"
low_weight_joined[15,1] <-"Change in main economic activity (vs. not)"
low_weight_joined[16,1] <-  "OCD symptoms"
low_weight_joined[17,1] <- "Key worker (vs. paid employment)"
low_weight_joined[18,1] <-  "Not in paid employment (vs. paid employment)"
low_weight_joined[19,1] <- "Retired (vs. paid employment)"
low_weight_joined[20,1] <- "Student (vs. paid employment)"
low_weight_joined[21,1] <- "Pandemic worry total score"
low_weight_joined[22,1] <- "COVID-19 infection (vs. not)"
low_weight_joined[23,1] <- "Psychiatric disorder (vs. not)" 
low_weight_joined[24,1] <- "Racially minoritised (vs. white)"
low_weight_joined[25,1] <- "Vulnerable group member (vs. not)"

# Plot
cor_ORs_low_weight_ExpBeforeOut <- ggplot(data = low_weight_joined,
       mapping = aes(
         x = estimate_sens,
         y = estimate_main,
         colour = Exposure
         )) +
  ggplot2::labs(
    y = "OR main analysis",
    x = "OR sensitivity analysis: Exposure before outcome",
    title = "Correlation of Odds Ratio in low weight regression models") +
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_vline(xintercept = 1) +
  theme_minimal() +
  # Add perfect correlation line
  geom_abline(intercept = 0,
              slope = 1,
              color="black", 
              size=0.5) 
  
cor_ORs_low_weight_ExpBeforeOut<- cor_ORs_low_weight_ExpBeforeOut + 
  coord_cartesian(
  xlim = c(0.3, 2.1),
  ylim = c(0.3, 2),
  expand = TRUE,
  default = FALSE,
  clip = "on"
) +
  # Add error bars (both main and sens)
  geom_errorbar(aes(ymin = conf.low_sens, ymax = conf.high_sens)) +
  geom_errorbarh(aes(xmin = conf.low_main, xmax = conf.high_main)) 

# Save
ggsave(
  paste0("cor_ORs_low_weight_ExpBeforeOut",
                    date,
                    ".jpeg"),
  plot = cor_ORs_low_weight_ExpBeforeOut,
  device = "jpeg", 
  path = paste0(filepath_plots_sensitivity_ExpBeforeOut), 
  scale = 1,
  width = 50,
  height = 20,
  units = "cm"
  )
```

## Binge eating
```{r Calculate correlation between effect sizes Binge eating}
# Extract columns from model - sens analysis
binge_eating_sens_extracted <- binge_eating_sens2 %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_sens = estimate,
         conf.high_sens = conf.high,
         conf.low_sens = conf.low,
         Exposure = term)

# Check
binge_eating_sens_extracted

# Extract columns from model - main analysis
binge_eating_extracted <- binge_eating_main %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_main = estimate,
         conf.high_main = conf.high,
         conf.low_main = conf.low,
         Exposure = term)

# Check
binge_eating_extracted

# Join
binge_eating_joined <- merge(x = binge_eating_sens_extracted,
                         y = binge_eating_extracted,
                         by = "Exposure")


# Check
binge_eating_joined

# Summarise ORs
summary(binge_eating_joined$estimate_main)
summary(binge_eating_joined$estimate_sens)

# Correlation
binge_eating_cor <- psych::corr.test(binge_eating_joined$estimate_main,
          binge_eating_joined$estimate_sens,
          ci = TRUE)

binge_eating_cor$r

print(binge_eating_cor,
      short=F)
binge_eating_joined
```

```{r plot OR correlation Binge eating}
# Delete intercept row
binge_eating_joined <- binge_eating_joined[-1, ]

# Rename exposures for plotting
binge_eating_joined[1,1] <- "16-25 years (vs. 56-65 years)"
binge_eating_joined[2,1] <- "26-35 years (vs. 56-65 years)"
binge_eating_joined[3,1] <- "36-45 years (vs. 56-65 years)"
binge_eating_joined[4,1] <- "46-55 years (vs. 56-65 years)"
binge_eating_joined[5,1] <- "66-70 years (vs. 56-65 years)"
binge_eating_joined[6,1] <- "71+ years (vs. 56-65 years)"
binge_eating_joined[7,1] <- "Minoritised gender (vs. man)"
binge_eating_joined[8,1] <- "Woman (vs. man)"
binge_eating_joined[9,1] <- "Highest education: A-levels (vs. no formal education)"
binge_eating_joined[10,1] <- "Highest education: GCSE/CSE (vs. no formal education)"
binge_eating_joined[11,1] <- "Highest education: NVQ (vs. no formal education)"
binge_eating_joined[12,1] <- "Highest education: Uni/Other professional quals (vs. no formal education)"
binge_eating_joined[13,1] <- "Change in living situation (vs. not)"
binge_eating_joined[14,1] <- "Lost someone due to COVID-19 (vs. not)"
binge_eating_joined[15,1] <- "Change in main economic activity (vs. not)"
binge_eating_joined[16,1] <- "Key worker (vs. paid employment)"
binge_eating_joined[17,1] <- "Not in paid employment (vs. paid employment)"
binge_eating_joined[18,1] <- "Retired (vs. paid employment)"
binge_eating_joined[19,1] <- "Student (vs. key worker)"
binge_eating_joined[20,1] <- "Pandemic worry total score"
binge_eating_joined[21,1] <- "COVID-19 infection (vs. not)"
binge_eating_joined[22,1] <- "Psychiatric disorder (vs. not)"
binge_eating_joined[23,1] <- "Racially minoritised (vs. white)"
binge_eating_joined[24,1] <- "Vulnerable group member (vs. not)"

cor_ORs_binge_eating_ExpBeforeOut <- ggplot(data = binge_eating_joined,
       mapping = aes(
         x = estimate_sens,
         y = estimate_main,
         colour = Exposure
         )) +
  ggplot2::labs(
    y = "OR main analysis",
    x = "OR sensitivity analysis: Exposure before outcome",
    title = "Correlation of Odds Ratio in binge eating regression models") +
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_vline(xintercept = 1) +
  theme_minimal() +
  # Add perfect correlation line
  geom_abline(intercept = 0,
              slope = 1,
              color="black", 
              size=0.5) 
  
cor_ORs_binge_eating_ExpBeforeOut <- cor_ORs_binge_eating_ExpBeforeOut + 
  coord_cartesian(
  xlim = c(0.2, 2),
  ylim = c(0.2, 2),
  expand = TRUE,
  default = FALSE,
  clip = "on"
) +
  # Add error bars (both main and sens)
  geom_errorbar(aes(ymin = conf.low_sens, ymax = conf.high_sens)) +
  geom_errorbarh(aes(xmin = conf.low_main, xmax = conf.high_main)) 

# Save
ggsave(
  paste0("cor_ORs_binge_eating_ExpBeforeOut",
                    date,
                    ".jpeg"),
  plot = cor_ORs_binge_eating_ExpBeforeOut,
  device = "jpeg", 
  path = filepath_plots_sensitivity_ExpBeforeOut, 
  scale = 1,
  width = 50,
  height = 20,
  units = "cm"
  )
```

## Harmful ideation
```{r Calculate correlation between effect sizes harmful ideation}
# Extract columns from model - sens analysis
harmful_ideation_sens_extracted <- harmful_ideation_sens2 %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_sens = estimate,
         conf.high_sens = conf.high,
         conf.low_sens = conf.low,
         Exposure = term)

# Check
harmful_ideation_sens_extracted

# Extract columns from model - main analysis
harmful_ideation_extracted <- harmful_ideation_main %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_main = estimate,
         conf.high_main = conf.high,
         conf.low_main = conf.low,
         Exposure = term)

# Check
harmful_ideation_extracted

# Join
harmful_ideation_joined <- merge(x = harmful_ideation_sens_extracted,
                         y = harmful_ideation_extracted,
                         by = "Exposure")


# Check
harmful_ideation_joined

# Summarise ORs
summary(harmful_ideation_joined$estimate_main)
summary(harmful_ideation_joined$estimate_sens)

# Correlation
harmful_ideation_cor <- psych::corr.test(harmful_ideation_joined$estimate_main,
          harmful_ideation_joined$estimate_sens,
          ci = TRUE)

harmful_ideation_cor$r

print(harmful_ideation_cor,
      short=F)
harmful_ideation_joined
```

```{r plot OR correlation harmful ideation}
# Delete intercept row
harmful_ideation_joined <- harmful_ideation_joined[-1, ]

# Rename exposures for plotting
harmful_ideation_joined[1,1] <- "16-25 years (vs. 56-65 years)"
harmful_ideation_joined[2,1] <- "26-35 years (vs. 56-65 years)"
harmful_ideation_joined[3,1] <- "36-45 years (vs. 56-65 years)"
harmful_ideation_joined[4,1] <- "46-55 years (vs. 56-65 years)"
harmful_ideation_joined[5,1] <- "66-70 years (vs. 56-65 years)"
harmful_ideation_joined[6,1] <- "71+ years (vs. 56-65 years)"
harmful_ideation_joined[7,1] <- "Minoritised gender (vs. man)"
harmful_ideation_joined[8,1] <- "Woman (vs. man)"
harmful_ideation_joined[9,1] <- "Highest education: A-levels (vs. no formal education)"
harmful_ideation_joined[10,1] <- "Highest education: GCSE/CSE (vs. no formal education)"
harmful_ideation_joined[11,1] <- "Highest education: NVQ (vs. no formal education)"
harmful_ideation_joined[12,1] <- "Highest education: Uni/Other professional quals (vs. no formal education)"
harmful_ideation_joined[13,1] <- "Change in living situation (vs. not)"
harmful_ideation_joined[14,1] <- "Lost someone due to COVID-19 (vs. not)"
harmful_ideation_joined[15,1] <- "Change in main economic activity (vs. not)"
harmful_ideation_joined[16,1] <- "Key worker (vs. paid employment)"
harmful_ideation_joined[17,1] <- "Not in paid employment (vs. paid employment)"
harmful_ideation_joined[18,1] <- "Retired (vs. paid employment)"
harmful_ideation_joined[19,1] <- "Student (vs. paid employment)"
harmful_ideation_joined[20,1] <- "Pandemic worry total score"
harmful_ideation_joined[21,1] <- "COVID-19 infection (vs. not)"
harmful_ideation_joined[22,1] <- "Psychiatric disorder (vs. not)"
harmful_ideation_joined[23,1] <- "Racially minoritised (vs. white)"
harmful_ideation_joined[24,1] <- "Vulnerable group member (vs. not)"

cor_ORs_harmful_ideation_ExpBeforeOut <- ggplot(data = harmful_ideation_joined,
       mapping = aes(
         x = estimate_sens,
         y = estimate_main,
         colour = Exposure
         )) +
  ggplot2::labs(
    y = "OR main analysis",
    x = "OR sensitivity analysis: Exposure before outcome",
    title = "Correlation of Odds Ratio in suicidal and/or self-harm regression models") +
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_vline(xintercept = 1) +
  theme_minimal() +
  # Add perfect correlation line
  geom_abline(intercept = 0,
              slope = 1,
              color="black", 
              size=0.5) 
  
cor_ORs_harmful_ideation_ExpBeforeOut <- cor_ORs_harmful_ideation_ExpBeforeOut + 
  coord_cartesian(
  xlim = c(0.4, 5.5), 
  ylim = c(0.4, 5.5),
  expand = TRUE,
  default = FALSE,
  clip = "on"
) +
  # Add error bars (both main and sens)
  geom_errorbar(aes(ymin = conf.low_sens, ymax = conf.high_sens)) +
  geom_errorbarh(aes(xmin = conf.low_main, xmax = conf.high_main)) 


# Save
ggsave(
  paste0("cor_ORs_harmful_ideation_ExpBeforeOut",
                    date,
                    ".jpeg"),
  plot = cor_ORs_harmful_ideation_ExpBeforeOut,
  device = "jpeg", 
  path = filepath_plots_sensitivity_ExpBeforeOut, 
  scale = 1,
  width = 50,
  height = 20,
  units = "cm"
  )
```

## Self-harm
```{r Calculate correlation between effect sizes self-harm}
# Extract columns from model - sens analysis
selfharm_sens_extracted <- selfharm_sens2 %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_sens = estimate,
         conf.high_sens = conf.high,
         conf.low_sens = conf.low,
         Exposure = term)

# Check
selfharm_sens_extracted

# Extract columns from model - main analysis
selfharm_extracted <- selfharm_main %>%
  select(term,
         estimate,
         conf.high,
         conf.low) %>%
  rename(estimate_main = estimate,
         conf.high_main = conf.high,
         conf.low_main = conf.low,
         Exposure = term)

# Check
selfharm_extracted

# Join
selfharm_joined <- merge(x = selfharm_sens_extracted,
                         y = selfharm_extracted,
                         by = "Exposure")


# Check
selfharm_joined

# Summarise ORs
summary(selfharm_joined$estimate_main)
summary(selfharm_joined$estimate_sens)

# Correlation
selfharm_cor <- psych::corr.test(selfharm_joined$estimate_main,
          selfharm_joined$estimate_sens,
          ci = TRUE)

selfharm_cor$r

print(selfharm_cor,
      short=F)

selfharm_joined
```

```{r plot OR correlation self-harm}
# Delete intercept row
selfharm_joined <- selfharm_joined[-1, ]

# Rename exposures for plotting
selfharm_joined[1,1] <- "16-25 years (vs. 56-65 years)"
selfharm_joined[2,1] <- "26-35 years (vs. 56-65 years)"
selfharm_joined[3,1] <- "36-45 years (vs. 56-65 years)"
selfharm_joined[4,1] <- "46-55 years (vs. 56-65 years)"
selfharm_joined[5,1] <- "66-70 years (vs. 56-65 years)"
selfharm_joined[6,1] <- "71+ years (vs. 56-65 years)"
selfharm_joined[7,1] <- "Minoritised gender (vs. man)"
selfharm_joined[8,1] <- "Woman (vs. man)"
selfharm_joined[9,1] <- "Highest education: A-levels (vs. no formal education)"
selfharm_joined[10,1] <- "Highest education: GCSE/CSE (vs. no formal education)"
selfharm_joined[11,1] <- "Highest education: NVQ (vs. no formal education)"
selfharm_joined[12,1] <- "Highest education: Uni/Other professional quals (vs. no formal education)"
selfharm_joined[13,1] <- "Change in living situation (vs. not)"
selfharm_joined[14,1] <- "Lost someone due to COVID-19 (vs. not)"
selfharm_joined[15,1] <- "Change in main economic activity (vs. not)"
selfharm_joined[16,1] <- "Key worker (vs. paid employment)"
selfharm_joined[17,1] <- "Not in paid employment (vs. paid employment)"
selfharm_joined[18,1] <- "Retired (vs. paid employment)"
selfharm_joined[19,1] <- "Student (vs. paid employment)"
selfharm_joined[20,1] <- "Pandemic worry total score"
selfharm_joined[21,1] <- "COVID-19 infection (vs. not)"
selfharm_joined[22,1] <- "Psychiatric disorder (vs. not)"
selfharm_joined[23,1] <- "Racially minoritised (vs. white)"
selfharm_joined[24,1] <- "Vulnerable group member (vs. not)"

cor_ORs_selfharm_ExpBeforeOut <- ggplot(data = selfharm_joined,
       mapping = aes(
         x = estimate_sens,
         y = estimate_main,
         colour = Exposure
         )) +
  ggplot2::labs(
    y = "OR main analysis",
    x = "OR sensitivity analysis: Exposure before outcome",
    title = "Correlation of Odds Ratio in self-harm regression models") +
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_vline(xintercept = 1) +
  theme_minimal() +
  # Add perfect correlation line
  geom_abline(intercept = 0,
              slope = 1,
              color="black", 
              size=0.5) 
  
cor_ORs_selfharm_ExpBeforeOut <- cor_ORs_selfharm_ExpBeforeOut + 
  coord_cartesian(
  xlim = c(0.4, 5.2),
  ylim = c(0.4, 4.5),
  expand = TRUE,
  default = FALSE,
  clip = "on"
  ) +
  # Add error bars (both main and sens)
  geom_errorbar(aes(ymin = conf.low_sens, ymax = conf.high_sens)) +
  geom_errorbarh(aes(xmin = conf.low_main, xmax = conf.high_main))  

# Save
ggsave(
  paste0("cor_ORs_selfharm_ExpBeforeOut",
                    date,
                    ".jpeg"),
  plot = cor_ORs_selfharm_ExpBeforeOut,
  device = "jpeg", 
  path = filepath_plots_sensitivity_ExpBeforeOut, 
  scale = 1,
  width = 50,
  height = 20,
  units = "cm"
  )
```