---
title: "Additional analysis: with education included but not people aged 16-25"
author: "Helena Davies"
date: "12/05/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-10-04.rds")
dim(dat)
colnames(dat)
```

# Exclude people aged 16-25
```{r exclude people aged 16-26}
dat <- dat %>%
  filter(age_category_COVID_baseline != "16-25")

# Check
dat %>%
  freq(age_category_COVID_baseline)

33529-36715
```

```{r change panworry to factor}
dat <- dat %>%
  mutate(panworry_factor =
           case_when(panworry_total_score > -1 &
                       panworry_total_score <= 20 ~ "0-20",
             
                     panworry_total_score > 20 &
                       panworry_total_score <= 40 ~ "21-40",
                     
                     panworry_total_score > 40 &
                      panworry_total_score <= 60 ~ "41-60",
                     
                      panworry_total_score > 60 &
                      panworry_total_score <= 80 ~ "61-80"
                     )
         )
```

### Re-ordering variables / converting to factors
First, re-order all variables to get desired reference category for plotting - put largest category as reference
Age
```{r Re-order age levels}
dat <- dat %>%
  mutate(age_category_COVID_baseline = factor(age_category_COVID_baseline,
                       levels = c("46-55",
                          # Mid-life
                                  #"16-25",
                                  "26-35",
                                  "36-45",
                                  "56-65", 
                                   "66-70",
                                   "71+")
                       )
         )

# Check
dat %>%
  freq(age_category_COVID_baseline)
```

Race
```{r Re-order race levels}
dat <- dat %>%
  mutate(race_binary = factor(race_binary,
                       levels = c("White", # Largest category
                                  "Racially minoritised"
                                  )))
dat %>%
  freq(race_binary)
```

Psychiatric disorder
```{r  Re-order psych disorder levels}
# First recode to "Yes" and "No"
dat <- dat %>%
  mutate(psych_disorder_factor =
           case_when(
            mental_health_diagnosis == "Psychiatric disorder" ~ "Yes", 
            mental_health_diagnosis == "No psychiatric disorder" ~ "No")
  )

# Check 
dat %>%
  freq(psych_disorder_factor)

# Then change order
dat <- dat %>%
  mutate(psych_disorder_factor = factor(psych_disorder_factor,
                       levels = c( "No", # Ref category
                                  "Yes"
                                  )))

# Check again
dat %>%
  freq(psych_disorder_factor)
```

Employment
```{r Re-order employment levels}
dat <- dat%>%
  mutate(paid_employment_key_worker = factor(paid_employment_key_worker,
                       levels = c("Paid employment",  
                                  "Key worker",
                                  "Not paid employment",
                                  "Retired",
                                  "Student"
                                  )
                       )
         )

# Check
dat %>%
  freq(paid_employment_key_worker)
```

# REGRESSION MODELS
## Binge eating
```{r Binge eating education model}
# Reference category
dat <- within(dat,
              highest_education <- relevel(highest_education,
                                                     ref = "No formal qualifications"))

model_edu <- glm(NEW_binge_eating_pandemic ~  
                 highest_education +
                   age_category_COVID_baseline +
                   sex_binary + 
                   race_binary +
                   psych_disorder_factor,
                 data = dat,
                 family = "binomial"
              )

binge_eating_edu <- tidy(model_edu,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_edu) %>% 
  length()

binge_eating_edu
```

## Low weight
```{r Low weight education model}
model_edu <- glm(NEW_low_weight_pandemic ~  
                 highest_education +
                   age_category_COVID_baseline +
                   sex_binary + 
                   race_binary +
                   psych_disorder_factor,
                 data = dat,
                 family = "binomial"
              )

low_weight_edu <- tidy(model_edu,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_edu) %>% 
  length()

low_weight_edu
```

## Suicidal and/or self=harm ideation
```{r Harmful ideation education model}
model_edu <- glm(NEW_harmful_ideation_pandemic ~  
                 highest_education +
                   age_category_COVID_baseline +
                   sex_binary + 
                   race_binary +
                   psych_disorder_factor,
                 data = dat,
                 family = "binomial"
              )

harmful_ideation_edu <- tidy(model_edu,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_edu) %>% 
  length()

harmful_ideation_edu
```

## Self-harm
```{r self-harm education model}
model_edu <- glm(NEW_selfharm_pandemic ~  
                 highest_education +
                   age_category_COVID_baseline +
                   sex_binary + 
                   race_binary +
                   psych_disorder_factor,
                 data = dat,
                 family = "binomial"
              )

selfharm_edu <- tidy(model_edu,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_edu) %>% 
  length()

selfharm_edu
```




