---
title: 'Additional analysis: Age stratified by sex'
author: "Helena Davies"
date: "05/10/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-10-04.rds")
dim(dat)
colnames(dat)
```

## Stratify by age
```{r stratify by age}
dat_1625 <- dat %>%
  filter(age_category_COVID_baseline == "16-25")

dat_2635 <- dat %>%
  filter(age_category_COVID_baseline == "26-35")

dat_3645 <- dat %>%
  filter(age_category_COVID_baseline == "36-45")

dat_4655 <- dat %>%
  filter(age_category_COVID_baseline == "46-55")

dat_5665 <- dat %>%
  filter(age_category_COVID_baseline == "56-65")

dat_6670 <- dat %>%
  filter(age_category_COVID_baseline == "66-70")

dat_71plus <- dat %>%
  filter(age_category_COVID_baseline == "71+")
```

# Binge eating
```{r Binge eating sex 16-25 model}
# Reference category
dat_1625 <- within(dat_1625,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_1625,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```

```{r Binge eating sex 26-35 model}
# Reference category
dat_2635 <- within(dat_2635,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_2635,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```

```{r Binge eating sex 36-45 model}
# Reference category
dat_3645 <- within(dat_3645,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_3645,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```

```{r Binge eating sex 46-55 model}
# Reference category
dat_4655 <- within(dat_4655,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_4655,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```


```{r Binge eating sex 56-65 model}
# Reference category
dat_5665 <- within(dat_5665,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_5665,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```

```{r Binge eating sex 66-70 model}
# Reference category
dat_6670 <- within(dat_6670,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_6670,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```

```{r Binge eating sex 71+ model}
# Reference category
dat_71plus <- within(dat_71plus,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_binge_eating_pandemic ~  
                 sex_binary,
                 data = dat_71plus,
                 family = "binomial"
              )

binge_eating_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

binge_eating_sex
```


# Low weight 
```{r Low weight sex 16-25 model}
# Reference category
dat_1625 <- within(dat_1625,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_1625,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

```{r Low weight sex 26-35 model}
# Reference category
dat_2635 <- within(dat_2635,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_2635,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

```{r Low weight sex 36-45 model}
# Reference category
dat_3645 <- within(dat_3645,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_3645,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

```{r Low weight sex 46-55 model}
# Reference category
dat_4655 <- within(dat_4655,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_4655,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```


```{r Low weight sex 56-65 model}
# Reference category
dat_5665 <- within(dat_5665,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_5665,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

```{r Low weight sex 66-70 model}
# Reference category
dat_6670 <- within(dat_6670,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_6670,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

```{r Low weight sex 71+ model}
# Reference category
dat_71plus <- within(dat_71plus,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_low_weight_pandemic ~  
                 sex_binary,
                 data = dat_71plus,
                 family = "binomial"
              )

low_weight_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

low_weight_sex
```

# Harmful ideation 
```{r Harmful ideation sex 16-25 model}
# Reference category
dat_1625 <- within(dat_1625,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_1625,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

```{r Harmful ideation sex 26-35 model}
# Reference category
dat_2635 <- within(dat_2635,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_2635,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

```{r Harmful ideation sex 36-45 model}
# Reference category
dat_3645 <- within(dat_3645,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_3645,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

```{r Harmful ideation sex 46-55 model}
# Reference category
dat_4655 <- within(dat_4655,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_4655,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```


```{r Harmful ideation sex 56-65 model}
# Reference category
dat_5665 <- within(dat_5665,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_5665,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

```{r Harmful ideation sex 66-70 model}
# Reference category
dat_6670 <- within(dat_6670,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_6670,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

```{r Harmful ideation sex 71+ model}
# Reference category
dat_71plus <- within(dat_71plus,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_harmful_ideation_pandemic ~  
                 sex_binary,
                 data = dat_71plus,
                 family = "binomial"
              )

harmful_ideation_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

harmful_ideation_sex
```

# Self-harm 
```{r Self-harm sex 16-25 model}
# Reference category
dat_1625 <- within(dat_1625,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_1625,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```

```{r Self-harm sex 26-35 model}
# Reference category
dat_2635 <- within(dat_2635,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_2635,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```

```{r Self-harm sex 36-45 model}
# Reference category
dat_3645 <- within(dat_3645,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_3645,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```

```{r Self-harm sex 46-55 model}
# Reference category
dat_4655 <- within(dat_4655,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_4655,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```


```{r Self-harm sex 56-65 model}
# Reference category
dat_5665 <- within(dat_5665,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_5665,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```

```{r Self-harm sex 66-70 model}
# Reference category
dat_6670 <- within(dat_6670,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_6670,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```

```{r Self-harm sex 71+ model}
# Reference category
dat_71plus <- within(dat_71plus,
              sex_binary <- relevel(factor(sex_binary),
                                    ref = "Male"))

model_sex <- glm(NEW_selfharm_pandemic ~  
                 sex_binary,
                 data = dat_71plus,
                 family = "binomial"
              )

selfharm_sex <- tidy(model_sex,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model_sex) %>% 
  length()

selfharm_sex
```