---
title: "OCD screener"
author: "Helena Davies"
date: "05/08/2021"
output: html_document
---

# Set up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

Install packages
```{r Install packages}
#install.packages("summarytools")
#install.packages("sjlabelled")
#install.packages("psych")
#install.packages("tidyverse")
```

Load packages from library 
NB: load tidyverse last!
```{r Load packages from library}
library(summarytools)
library(sjlabelled)
library (psych)
library(tidyverse)
```

Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date = Sys.Date()
date
```

Add the add_numeric function - used to convert character variables into numeric variables and sumscore function
```{r Read in functions}
source("./functions.R")
```

# Read in the data: OCD screener 

## GLAD data
```{r GLAD read in data}
glad_dat <- readRDS(file = "/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_raw/glad/ocd_coping_glad_optional.rds")
  
# Check
glad_dat %>%
  colnames()
glad_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r GLAD select}
exclude_cols_dem <- c("ID",
                  "sample")
glad_dat.id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  add_column(sample = "GLAD", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample,
         ocd.strong_urges_urges_dirt,
         ocd.feeling_driven_mental_acts
  ) %>%
  add_numeric(exclude = exclude_cols_dem) 
# Inspect colnames
colnames(glad_dat.id)

glad_dat.id %>%
  dim()
```

## EDGI data
```{r edgi read in data}
edgi_dat <- readRDS(file = "/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_raw/edgi/ocd_coping_edgi_optional.rds")
  
# Check
edgi_dat %>%
  colnames()
edgi_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r edgi select}
exclude_cols_dem <- c("ID",
                  "sample")
edgi_dat.id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  add_column(sample = "EDGI", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample,
         ocd.strong_urges_urges_dirt,
         ocd.feeling_driven_mental_acts
  ) %>%
  add_numeric(exclude = exclude_cols_dem) 
# Inspect colnames
colnames(edgi_dat.id)

edgi_dat.id %>%
  dim()
```

## NBR data
```{r NBR read in data}
nbr_dat <- readRDS(file = "/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_raw/nbr/ocd_coping_nbr_optional.rds")
  
# Check
nbr_dat %>%
  colnames()
nbr_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r NBR select}
exclude_cols_dem <- c("ID",
                  "sample")
nbr_dat.id <- nbr_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  add_column(sample = "NBR", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample,
         ocd.strong_urges_urges_dirt,
         ocd.feeling_driven_mental_acts
  ) %>%
  add_numeric(exclude = exclude_cols_dem) 
# Inspect colnames
colnames(nbr_dat.id)

nbr_dat.id %>%
  dim()
```

## RAMP data
```{r RAMP read in data}
ramp_dat <- readRDS(file = "/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_raw/ramp/ocd_ramp.rds")
  
# Check
ramp_dat %>%
  colnames()
ramp_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r RAMP select}
exclude_cols_dem <- c("ID",
                  "sample")
ramp_dat.id <- ramp_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% 
  add_column(sample = "RAMP", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample,
         ocd.strong_urges_urges_dirt,
         ocd.feeling_driven_mental_acts
  ) %>%
  add_numeric(exclude = exclude_cols_dem) 
# Inspect colnames
colnames(ramp_dat.id)

ramp_dat.id %>%
  dim()
```

# Merge data
```{r}
dat <- nbr_dat.id %>%
  rbind(glad_dat.id,
        edgi_dat.id, 
        ramp_dat.id)

# Check
dat %>%
  colnames()

dat %>%
  nrow()
```

# Recoding variables

## Unpleasant thoughts, urges, images in mind
Q: Over the past two weeks, how often have you been bothered by unpleasant thoughts, urges, or images that repeatedly enter your mind?e.g. thoughts about dirt or germs, thoughts about harm coming to yourself or others, strong urges for things to be ordered or symmetrical)
```{r Freq}

dat %>%
  freq(ocd.strong_urges_urges_dirt)

dat <- dat %>%
  mutate(ocd.repetitive_unpleasant_thoughts_binary =
           case_when(
             ocd.strong_urges_urges_dirt == "Seen but not answered" |
               is.na(ocd.strong_urges_urges_dirt) ~ NA_character_,
             
             ocd.strong_urges_urges_dirt == "Not at all" ~ "No",
             
             TRUE ~ "Yes"
             
           ))

# Check new binary variable
dat %>%
  freq(ocd.repetitive_unpleasant_thoughts_binary)
```

## Compulsive behaviour or mental act
Q: Over the past two weeks, how often have you been bothered by feeling driven to perform certain behaviours or mental acts over and over again?
```{r Freq}

dat %>%
  freq(ocd.feeling_driven_mental_acts)

dat <- dat %>%
  mutate(ocd.compulsive_beh_mental_act_binary =
           case_when(
             ocd.feeling_driven_mental_acts == "Seen but not answered" |
               is.na(ocd.feeling_driven_mental_acts) ~ NA_character_,
             
             ocd.feeling_driven_mental_acts == "Not at all" ~ "No",
             
             TRUE ~ "Yes"
             
           ))

# Check new binary variable
dat %>%
  freq(ocd.compulsive_beh_mental_act_binary)

```
# Select variables for final dataset
```{r Select columns to save}
dat_final <- dat %>%
  select(ID,
         sample,
         ocd.strong_urges_urges_dirt,
         ocd.feeling_driven_mental_acts,
         ocd.repetitive_unpleasant_thoughts_binary,
         ocd.compulsive_beh_mental_act_binary,
  )
```

# Save dataset
```{r Save dataset}
saveRDS(object = dat_final, file = paste0("/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_cleaned/OCD_screener", date, ".rds"))

```

