---
title: "Merging data"
author: "Helena Davies"
date: "06/05/2021"
output: html_document
---

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

Load packages
```{r}
library(tidyverse)
library(skimr)
```

# Import baseline data
```{r export data}
glad_baseline <- readRDS(file = "../data_cleaned/NEW_baseline_glad.rds")
dim(glad_baseline)

edgi_baseline <- readRDS(file = "../data_cleaned/NEW_baseline_edgi.rds")
dim(edgi_baseline)

nbr_baseline <- readRDS(file = "../data_cleaned/NEW_baseline_nbr.rds")
dim(nbr_baseline)

ramp_baseline <- readRDS(file = "../data_cleaned/NEW_baseline_ramp.rds")
dim(ramp_baseline)

```
##Make list of edeq baseline columns only in RAMP
```{r}
edeq_baseline_columnNames <- c("edeq.deliberately_limit_amount_influence_baseline",                     
                               "edeq.calories_made_body_shape_baseline",                               
                               "edeq.weight_influenced_person_baseline",                                
                               "edeq.dissatisfied_shape_weight_baseline",                              
                               "edeq.nibbled_picked_snacks_grazed_baseline",                            
                               "edeq.felt_anxious_blue_bored_baseline",                                
                               "edeq.felt_anxious_blue_bored.1_baseline",                              
                               "edeq.eating_behaviours_concerns_distressed_baseline",                  
                               "edeq.deliberately_limit_amount_influence.1_baseline",                   
                               "edeq.calories_made_body_shape.1_baseline",                              
                               "edeq.weight_influenced_person.1_baseline",                              
                               "edeq.dissatisfied_shape_weight.1_baseline",                            
                               "edeq.eating_behaviours_concerns_distressed.1_baseline",                 
                               "edeq.feelings_pandemic_felt_baseline",                                  
                               "edeq.actively_been_monitoring_your_shape_or_weight_baseline",           
                               "edeq.regard_lost_control_eaten_baseline",                               
                               "edeq.sick_means_made_shape_baseline",                                   
                               "edeq.diuretics_laxatives_means_shape_baseline",                         
                               "edeq.compulsive_driven_burn_calories_baseline",                         
                               "edeq.nibbled_picked_snacks_grazed.1_baseline",                         
                               "edeq.felt_anxious_blue_bored.2_baseline",                               
                               "edeq.felt_anxious_blue_bored.3_baseline",                               
                               "edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline",        
                               "edeq.regard_lost_control_eaten.1_baseline",                             
                               "edeq.sick_means_made_shape.1_baseline",                                 
                               "edeq.diuretics_laxatives_means_shape.1_baseline",                       
                               "edeq.compulsive_driven_burn_calories.1_baseline",                       
                               "edeq.deliberately_limit_amount_influence_baseline_numeric",             
                               "edeq.calories_made_body_shape_baseline_numeric",                        
                               "edeq.weight_influenced_person_baseline_numeric",                        
                               "edeq.dissatisfied_shape_weight_baseline_numeric",                       
                               "edeq.nibbled_picked_snacks_grazed_baseline_numeric",                    
                               "edeq.felt_anxious_blue_bored_baseline_numeric",                         
                               "edeq.felt_anxious_blue_bored.1_baseline_numeric",                       
                               "edeq.eating_behaviours_concerns_distressed_baseline_numeric",           
                               "edeq.deliberately_limit_amount_influence.1_baseline_numeric",           
                               "edeq.calories_made_body_shape.1_baseline_numeric",                      
                               "edeq.weight_influenced_person.1_baseline_numeric",                      
                               "edeq.dissatisfied_shape_weight.1_baseline_numeric",                     
                               "edeq.eating_behaviours_concerns_distressed.1_baseline_numeric",         
                               "edeq.feelings_pandemic_felt_baseline_numeric",                          
                               "edeq.actively_been_monitoring_your_shape_or_weight_baseline_numeric",   
                               "edeq.regard_lost_control_eaten_baseline_numeric",                       
                               "edeq.sick_means_made_shape_baseline_numeric",                           
                               "edeq.diuretics_laxatives_means_shape_baseline_numeric",
                               "edeq.compulsive_driven_burn_calories_baseline_numeric",                 
                               "edeq.nibbled_picked_snacks_grazed.1_baseline_numeric",                  
                               "edeq.felt_anxious_blue_bored.2_baseline_numeric",                       
                               "edeq.felt_anxious_blue_bored.3_baseline_numeric",                       
                               "edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline_numeric",
                               "edeq.regard_lost_control_eaten.1_baseline_numeric",                     
                               "edeq.sick_means_made_shape.1_baseline_numeric",                         
                               "edeq.diuretics_laxatives_means_shape.1_baseline_numeric",               
                               "edeq.compulsive_driven_burn_calories.1_baseline_numeric") 
                               
```

##EDEQ baseline only in RAMP, so add all above columns as NA in nbr, edgi + glad
```{r}
nbr_baseline[edeq_baseline_columnNames] <- NA

glad_baseline[edeq_baseline_columnNames] <- NA

edgi_baseline[edeq_baseline_columnNames] <- NA
```
                                                          
##Need same columns across all datasets in order to merge
```{r}
#sex & age_category_numeric not in RAMP
ramp_baseline$sex <- NA
ramp_baseline$age_category_numeric <- NA

#age called "age_unc" in RAMP
  ramp_baseline <- ramp_baseline %>% 
  rename(
    age_category = age_unc,
    )
  
  
#highest_education_prepan/numeric not in ramp or nbr
ramp_baseline$highest_education_prepan <- NA
ramp_baseline$highest_education_prepan_numeric <- NA
nbr_baseline$highest_education_prepan <- NA
nbr_baseline$highest_education_prepan_numeric <- NA
```

##Merge all baseline data
```{r glad/edgi/nbr/ramp data frame list}

#bind all baseline data
dat <- bind_rows(
  glad_baseline,
  edgi_baseline,
  nbr_baseline,
  ramp_baseline
)

##check col names
colnames(dat)
nrow(dat)
```
##For now, set: age_category, age_category_numeric and sex to NA as these are in the ED grouping dataset
```{r}

dat$age_category <-NULL

dat$age_category_numeric <- NULL

dat$sex <- NULL
```


#Import follow up data
```{r}

taf_ramp <- readRDS(file = "../data_cleaned/NEW_taf_ramp.rds")
dim(taf_ramp)

taf_coping <- readRDS(file = "../data_cleaned/NEW_taf_coping.rds")
dim(taf_coping)

edeq_coping_screener <- readRDS(file = "../data_cleaned/NEW_edeq_screener_coping.rds")
dim(edeq_coping_screener)


edeq_ramp_screener <- readRDS(file = "../data_cleaned/NEW_edeq_screener_ramp.rds")
dim(edeq_ramp_screener)

```
##Create empty wave 1a and 1bs in COPING to merge with RAMP 

```{r}
edeq_coping_screener$ed_scid5.regular_episodes_eating_binges_.Wave_1a <- NULL 
edeq_coping_screener$ed_scid5.regular_episodes_eating_binges_.Wave_1b <- NULL 
edeq_coping_screener$ed_scid5.weigh_weighed_past_month_.Wave_1a <- NULL 
edeq_coping_screener$ed_scid5.weigh_weighed_past_month_.Wave_1b <- NULL 

```

#Bind coping and ramp's edeq and taf TOGETHER
```{r}

#bind all edeq data

EDEQ <- bind_rows(edeq_ramp_screener,
                 edeq_coping_screener)


#check col names edeq
colnames(EDEQ)

#check no of participants edeq
nrow(EDEQ)

#bind all taf data
TAF <- bind_rows(taf_ramp,
                 taf_coping)

#check col names taf
colnames(TAF)

#check no of participants
nrow(TAF)


##Merge TAF and EDEQ
taf_edeq <- merge(TAF,
                  EDEQ,
                  by = "ID"
  
  )

#check col names 
colnames(taf_edeq)

#check no of participants
nrow(taf_edeq)

```


#Bind edeq_taf with baseline data
```{r}

data.merged <- merge(dat,
                  taf_edeq,
                  by = "ID")

#check col names 
colnames(data.merged)

#check no of participants
nrow(data.merged)


```

### Read in ED group data
```{r}

##COPING (GLAD, EDGI, NBR) and RAMP
baseline_ED_groups_data <- readRDS(file = "../data_cleaned/baseline_groups2021-05-06.rds")

# Inspect dimensions
dim(baseline_ED_groups_data)
# Inspect colnames
colnames(baseline_ED_groups_data)

nrow(baseline_ED_groups_data)


```

#Merge merged data with grouping ED data
```{r}

data.merged.with.ED.groups <- merge(baseline_ED_groups_data,
                  data.merged,
                  by = "ID")

dim(data.merged.with.ED.groups)

```

#Remove duplicate IDs 
```{r}

##Remove dupilcate IDs (as each wave is now a column, there should be NO dup IDs)
data.final  <- data.merged.with.ED.groups  %>%
  filter(., !duplicated(ID)) 

##Check number of rows
nrow(data.final)

```

#Skim final data
```{r Skim taf + baseline data}
#look at the data
skimr::skim(data.final)
```

#Save final dataset
##Save dataset
```{r}
saveRDS(object = data.final,
        file = paste0("/Users/helenadavies/King's College London/MT-Translational Neuropsychiatric Genomics - Helena_Davies_PhD - Helena_Davies_PhD/EDBeh_SelfHarm/data_cleaned/data.final.with.ED.groups", date, ".rds"))

```



