---
title: "Regressions2"
author: "Helena Davies"
date: "24/05/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```


#Retrieve the recent date
```{r Recent date}
date = Sys.Date()
date
```

#### R functions

```{r call in function library functions}
# source all functions in the function folder
source("./functions.R")
```

# Read in data
```{r}
dat <- readRDS(file = "../data_cleaned/test_dat2021-05-24.rds")
dim(dat)
colnames(dat)
```
## CORRELATION MATRICES ##
```{r}

#Categorical variables for dummy coding

descriptives.columns.dummy <- c(
"gender_cleaned",
  "age_category_COVID_baseline",
  "ethnicity_binary",
  "highest_education",
  "control_factor",
  "key_worker",
"vulnerable_group_member",
"PREPANDEMIC_selfharm_ideation",
"PREPANDEMIC_passive_suicidal_ideation",
"PREPANDEMIC_selfharm"
)

```

#Dummy coding for categorical variables
```{r descriptives data frame}
dat_dummy <- fastDummies::dummy_cols(dat,
                                              select_columns = descriptives.columns.dummy)

colnames(dat_dummy)

```

# EATING DISORDER CORR MATRIX
```{r}
#Make binary variables numeric 

# Select items for correlation matrix
dat.corr.mat <- dat_dummy %>%
  select("Male" = "gender_cleaned_Male",
   "Female" = "gender_cleaned_Female",
   "Minoritised_gender" = "gender_cleaned_Minoritised gender",
   "16-25" = "age_category_COVID_baseline_16-25",
   "26-35" = "age_category_COVID_baseline_26-35",
   "36-45" = "age_category_COVID_baseline_36-45",
   "46-55" = "age_category_COVID_baseline_46-55",
   "56-65" = "age_category_COVID_baseline_56-65",
   "66-70" =  "age_category_COVID_baseline_66-70",
   "71-75" = "age_category_COVID_baseline_71-75",
   "75+" = "age_category_COVID_baseline_75+",
   "Racially_minoritised" = "ethnicity_binary_Racially minoritised",
   "White" = "ethnicity_binary_White", 
   "No_formal_education" = "highest_education_No formal qualifications",
  "GCSE/CSE"="highest_education_GCSE/CSE",
  "NVQ" = "highest_education_NVQ",
  "A-Levels" = "highest_education_A-levels",
  "Uni/Prof_qual" = "highest_education_University/Other professional qualifications",
  "Control" = "control_factor_Control",
  "Not_control" ="control_factor_Not a control",
  "Not_key_worker" = "key_worker_No key worker",
  "Key_worker"="key_worker_Key worker",
  "Not_vulnerable_group" = "vulnerable_group_member_I am not a member of a vulnerable group",
  "Vulnerable_group" = "vulnerable_group_member_Not I am not a member of a vulnerable group"
) %>%
  polycor::hetcor(use = "pairwise.complete.obs") #Remember to specify "pairwise.complete.obs"!


# Save the correlations from the correlation matrix in an object
dat.corr.matrix <- as.matrix(dat.corr.mat)

# Save the p values from the correlation matrix in an object
dat.p.matrix <- as.matrix(dat.corr.mat$tests)
```

# 16. Create the correlation matrix plot using the corrplot package
```{r Correlation matrix at t1 plot, fig.height=7}

dat.corr.matrix %>%
  corrplot::corrplot(method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         number.cex = 0.75,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4",
                                "white",
                                "firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = dat.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank") # Nonsignificant correlations have no colour
         

         
```

#SELF-HARM CORR MATRIX
[53] "vulnerable_group_member_NA"                                          "PREPANDEMIC_selfharm_ideation_0"                                    
[55] "PREPANDEMIC_selfharm_ideation_1"                                     "PREPANDEMIC_selfharm_ideation_NA"                                   
[57] "PREPANDEMIC_passive_suicidal_ideation_0"                             "PREPANDEMIC_passive_suicidal_ideation_1"                            
[59] "PREPANDEMIC_passive_suicidal_ideation_NA"                            "PREPANDEMIC_selfharm_0"                                             
[61] "PREPANDEMIC_selfharm_1"                                              "PREPANDEMIC_selfharm_NA"     
```{r}
#Make binary variables numeric 

# Select items for correlation matrix
dat.corr.mat <- dat_dummy %>%
  select("Male" = "gender_cleaned_Male",
   "Female" = "gender_cleaned_Female",
   "Minoritised_gender" = "gender_cleaned_Minoritised gender",
   "16-25" = "age_category_COVID_baseline_16-25",
   "26-35" = "age_category_COVID_baseline_26-35",
   "36-45" = "age_category_COVID_baseline_36-45",
   "46-55" = "age_category_COVID_baseline_46-55",
   "56-65" = "age_category_COVID_baseline_56-65",
   "66-70" =  "age_category_COVID_baseline_66-70",
   "71-75" = "age_category_COVID_baseline_71-75",
   "75+" = "age_category_COVID_baseline_75+",
   "Racially_minoritised" = "ethnicity_binary_Racially minoritised",
   "White" = "ethnicity_binary_White", 
   "No_formal_education" = "highest_education_No formal qualifications",
  "GCSE/CSE"="highest_education_GCSE/CSE",
  "NVQ" = "highest_education_NVQ",
  "A-Levels" = "highest_education_A-levels",
  "Uni/Prof_qual" = "highest_education_University/Other professional qualifications",
  "Control" = "control_factor_Control",
  "Not_control" ="control_factor_Not a control",
  "Not_key_worker" = "key_worker_No key worker",
  "Key_worker"= "key_worker_Key worker",
  "Not_vulnerable_group" = "vulnerable_group_member_I am not a member of a vulnerable group",
  "Vulnerable_group" = "vulnerable_group_member_Not I am not a member of a vulnerable group",
  "Prepan_suicidal_ideation" = "PREPANDEMIC_passive_suicidal_ideation_1",
  "Prepan_selfharm_ideation" = "PREPANDEMIC_selfharm_ideation_1",
  "Prepan_selfharm" = "PREPANDEMIC_selfharm_1"
) %>%
  polycor::hetcor(use = "pairwise.complete.obs") #Remember to specify "pairwise.complete.obs"!


# Save the correlations from the correlation matrix in an object
dat.corr.matrix <- as.matrix(dat.corr.mat)

# Save the p values from the correlation matrix in an object
dat.p.matrix <- as.matrix(dat.corr.mat$tests)
```

# 16. Create the correlation matrix plot using the corrplot package
```{r Correlation matrix at t1 plot, fig.height=7}

dat.corr.matrix %>%
  corrplot::corrplot(method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         number.cex = 0.75,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4",
                                "white",
                                "firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = dat.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank") # Nonsignificant correlations have no colour
         

         
```

### BASIC MODELS ###

```{r}
#Rename education labels
dat <- dat %>%
  mutate(highest_education_renamed =
           case_when(highest_education == "No formal qualifications" ~ "No formal qualifications",
                     highest_education == "GCSE/CSE" ~ "GCSE/CSE",
                     highest_education == "NVQ" ~ "NVQ",
                       highest_education == "A-levels" ~"A-levels",
                       highest_education == "University/Other professional qualifications" ~ "Uni/Prof qual"
             
           ))


#Reorder education 
#Change order
dat$highest_education_renamed_ordered <- ordered(dat$highest_education_renamed,
                                         levels = c("No formal qualifications",
                                                    "GCSE/CSE",
                                                    "NVQ",
                                                    "A-levels",
                                                    "Uni/Prof qual"))

#Change back to character
dat$highest_education_renamed <- as.character(dat$highest_education_renamed_ordered)

```


# Age + gender + ethnicity + highest education- Binge eating
```{r}
# Age and gender and ethnicity 
model1 <- glm(NEW_binge_eating_pandemic ~ gender_cleaned +age_category_COVID_baseline +  ethnicity_binary + highest_education,
               data = dat,
               family = "binomial")

tidy(model1,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model1) %>% 
  length()

```

#Plot! Age + gender + ethnicity + highest_education- Binge eating
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_binge_eating" = "NEW_binge_eating_pandemic",
         "Education" = "highest_education_renamed")


#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education")


dependent <- "Pandemic_binge_eating"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 15,
          dependent_label = "New experience of binge eating during pandemic",
          remove_ref = TRUE)


```


# Age + gender + ethnicity + highest_education- Low weight
```{r}
# Age and gender and ethnicity 
model2 <- glm(NEW_low_weight_pandemic ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary+ highest_education,
               data = dat,
               family = "binomial")

tidy(model2,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model2) %>% 
  length()
```

#Plot! Age + gender + ethnicity + highest_education- Low weight
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_low_weight" = "NEW_low_weight_pandemic",
         "Education" = "highest_education_renamed")


#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education")


dependent <- "Pandemic_low_weight"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 15,
          dependent_label = "New experience of low weight during pandemic",
          remove_ref = TRUE)


```
# Age + gender + ethnicity + highest_education- Passive suicial ideation
```{r}
#Recode to factor
dat <- dat %>%
  mutate(PREPANDEMIC_passive_suicidal_ideation_factor = 
           case_when(PREPANDEMIC_passive_suicidal_ideation == 1 ~ "Yes",
                     PREPANDEMIC_passive_suicidal_ideation == 0 ~ "No")
         )


dat %>%
  freq(PREPANDEMIC_passive_suicidal_ideation)

# Age and gender and ethnicity and pre-pan exp
model3 <- glm(passive_suicidal_ideation_PANDEMIC ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary+ highest_education + PREPANDEMIC_passive_suicidal_ideation_factor,
               data = dat,
               family = "binomial")

tidy(model3,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model3) %>% 
  length() 

```

#Plot! Age + gender + ethnicity + highest_education + prepan experience - Passive suicial ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_passive_suicidal_ideation" = "passive_suicidal_ideation_PANDEMIC",
         "Education" = "highest_education_renamed",
         "Prepan_experience" = "PREPANDEMIC_passive_suicidal_ideation_factor")


#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Prepan_experience")


dependent <- "Pandemic_passive_suicidal_ideation"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 13,
          dependent_label = "Passive suicidal ideation during pandemic",
          remove_ref = TRUE)


```


# Age + gender + ethnicity + highest_education + prepandemic experience - Self harm ideation
```{r}
#Recode to factor
dat <- dat %>%
  mutate(PREPANDEMIC_selfharm_ideation_factor = 
           case_when(PREPANDEMIC_selfharm_ideation == 1 ~ "Yes",
                     PREPANDEMIC_selfharm_ideation == 0 ~ "No")
         )


dat %>%
  freq(PREPANDEMIC_selfharm_ideation_factor)


# Age and gender and ethnicity 
model4 <- glm(selfharm_ideation_PANDEMIC ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary+ highest_education + PREPANDEMIC_selfharm_ideation_factor,
               data = dat,
               family = "binomial")

tidy(model4,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model4) %>% 
  length()
```

#Plot! Age + gender + ethnicity+ highest_education - Self harm ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_selfharm_ideation" = "selfharm_ideation_PANDEMIC",
         "Education" = "highest_education_renamed",
         "Prepan_experience" = "PREPANDEMIC_selfharm_ideation_factor")


#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Prepan_experience")


dependent <- "Pandemic_selfharm_ideation"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 13,
          dependent_label = "Self-harm ideation during pandemic",
          remove_ref = TRUE)


```

# Age + gender + ethnicity + highest_education + prepan experience- Self harm 
```{r}

#Recode to factor
dat <- dat %>%
  mutate(PREPANDEMIC_selfharm_factor = 
           case_when(PREPANDEMIC_selfharm == 1 ~ "Yes",
                     PREPANDEMIC_selfharm == 0 ~ "No")
         )


dat %>%
  freq(PREPANDEMIC_selfharm_factor)


# Age and gender and ethnicity 
model5 <- glm(selfharm_PANDEMIC ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary + highest_education + PREPANDEMIC_selfharm,
               data = dat,
               family = "binomial")

tidy(model5,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model5) %>% 
  length()


```

#Plot! Age + gender + ethnicity + highest_education - Self harm ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_selfharm" = "selfharm_PANDEMIC",
         "Education" = "highest_education_renamed",
         "Prepan_experience" = "PREPANDEMIC_selfharm_factor")


#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Education",
                 "Prepan_experience")


dependent <- "Pandemic_selfharm"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 15,
          dependent_label = "Self-harm during pandemic",
          remove_ref = TRUE)


```
         


#### ADDING CONTROL STATUS + KEY WORKER + VULNERABLE GROUP ####

# Age + gender + ethnicity + highest_education +  control + vulnerable group + key worker status - Binge eating

```{r}


#  Age + gender + ethnicity + highest education + control _
model6 <- glm(NEW_binge_eating_pandemic ~  age_category_COVID_baseline + gender_cleaned + ethnicity_binary + highest_education + control_factor + key_worker + vulnerable_group_member,
               data = dat,
               family = "binomial")

tidy(model6,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model6) %>% 
  length()

```

#Plot! AAge + gender + ethnicity + highest education +  control + vulnerable group + key worker status - Binge eating
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_binge_eating" = "NEW_binge_eating_pandemic",
         "Highest_education" = "highest_education",
         "Control_status" = "control_factor",
         "Key_worker_status" = "key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member" 
)

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Highest_education",
                 "Control_status",
                 "Key_worker_status",
                 "Vulnerable_group_member")


dependent <- "Pandemic_binge_eating"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 15,
          dependent_label = "New experience of binge eating during pandemic",
          remove_ref = TRUE)


```
#  Age + gender + ethnicity + highest education + comorbidities  - Low weight
```{r}
#  Age + gender + ethnicity + highest education + comorbidities 
model7 <- glm(NEW_low_weight_pandemic ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary+ highest_education + comorbidities + comorbidities_count,
               data = dat,
               family = "binomial")

tidy(model7,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model7) %>% 
  length()
```
#Plot! AAge + gender + ethnicity + highest education +  control + vulnerable group + key worker status - Low weight
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_low_weight" = "NEW_low_weight_pandemic",
         "Highest_education" = "highest_education",
         "Control_status" = "control_factor",
         "Key_worker_status" = "key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member" 
)

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Highest_education",
                 "Control_status",
                 "Key_worker_status",
                 "Vulnerable_group_member")


dependent <- "Pandemic_low_weight"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 15,
          dependent_label = "New experience of low weight during pandemic",
          remove_ref = TRUE)
```


#  Age + gender + ethnicity + highest education + comorbidities  - Passive suicial ideation
```{r}

#  Age + gender + ethnicity + highest education + comorbidities 
model8 <- glm(NEW_passive_suicidal_ideation_pandemic ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary + highest_education + comorbidities + comorbidities_count,
               data = dat,
               family = "binomial")

tidy(model8,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model8) %>% 
  length()

```

#Plot! AAge + gender + ethnicity + highest education +  control + vulnerable group + key worker status - Passive suicial ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_suicidal_ideation" = "NEW_passive_suicidal_ideation_pandemic",
         "Highest_education" = "highest_education",
         "Control_status" = "control_factor",
         "Key_worker_status" = "key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member" 
)

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Highest_education",
                 "Control_status",
                 "Key_worker_status",
                 "Vulnerable_group_member")


dependent <- "Pandemic_suicidal_ideation"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 13,
          dependent_label = "New experience of passive suicidal ideation during pandemic",
          remove_ref = TRUE)
```

#  Age + gender + ethnicity  + comorbidities  - Self harm ideation
```{r}

#  Age + gender + ethnicity + highest education + comorbidities 
model9 <- glm(NEW_selfharm_ideation_pandemic ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary + highest_education + comorbidities + comorbidities_count,
               data = dat,
               family = "binomial")

tidy(model9,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model9) %>% 
  length()
```

#Plot! Age + gender + ethnicity + highest education +  control + vulnerable group + key worker status - Self harm ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_selfharm_ideation" = "NEW_selfharm_ideation_pandemic",
         "Highest_education" = "highest_education",
         "Control_status" = "control_factor",
         "Key_worker_status" = "key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member" 
)

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Highest_education",
                 "Control_status",
                 "Key_worker_status",
                 "Vulnerable_group_member")


dependent <- "Pandemic_selfharm_ideation"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 13,
          dependent_label = "New experience of self-harm ideation during pandemic",
          remove_ref = TRUE)
```

#  Age + gender + ethnicity + highest education + comorbidities  - Self harm 
```{r}

#  Age + gender + ethnicity + highest education + comorbidities 
model10 <- glm(NEW_selfharm_pandemic ~ age_category_COVID_baseline + gender_cleaned + ethnicity_binary + highest_education + comorbidities + comorbidities_count,
               data = dat,
               family = "binomial")

tidy(model10,
     conf.int=TRUE,
     exponentiate=TRUE)

fitted(model10) %>% 
  length()


```

#Plot! Age + gender + ethnicity + highest education +  control + vulnerable group + key worker status - Self harm ideation
```{r}

dat_plot <- dat %>%
  select("Age" = "age_category_COVID_baseline",
         "Gender" = "gender_cleaned",
         "Race" = "ethnicity_binary",
         "Pandemic_selfharm" = "NEW_selfharm_pandemic",
         "Highest_education" = "highest_education",
         "Control_status" = "control_factor",
         "Key_worker_status" = "key_worker",
         "Vulnerable_group_member" ="vulnerable_group_member" 
)

#1. Plot
explanatory <- c("Age",
                 "Gender",
                 "Race",
                 "Highest_education",
                 "Control_status",
                 "Key_worker_status",
                 "Vulnerable_group_member")


dependent <- "Pandemic_selfharm"


dat_plot %>%
  finalfit::or_plot(dependent, explanatory, 
          breaks = c(0.5, 1, 5, 10, 20, 30),
          table_text_size = 3.0,
          title_text_size = 13,
          dependent_label = "New experience of self-harm during pandemic",
          remove_ref = TRUE)
```