---
title: 'Merging: Derived variables'
author: "Helena Davies"
date: "21/02/2022"
output: html_document
---

This script merges all the derived variables ready for regression analyses.
Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in dataset}
# Exposures
dat_BE <- readRDS(paste0(filepath_saved_data, "exposures_all_models2022-04-21.rds"))

# Outcome: Binge eating (& outcome-specific variables)
dat_BE <- readRDS(paste0(filepath_saved_data, "final_dat_BE2022-03-24.rds"))

# Outcome:Low weight (& outcome-specific variables)
dat_LW <- readRDS(paste0(filepath_saved_data, "final_dat_LW2022-03-24.rds"))

# Outcome:Harmful ideation (& outcome-specific variables)
dat_HI <- readRDS(paste0(filepath_saved_data, "final_dat_HI2022-03-24.rds"))

# Outcome: Self-harm (& outcome-specific variables)
dat_SH <- readRDS(paste0(filepath_saved_data, "final_dat_SH2022-03-24.rds"))
```

# Merge data
```{r merge all data}
dat_BE_LW <- dplyr::left_join(dat_BE,
                              dat_LW,
                              by = c("ID")
)


dat_BE_LW_HI <- dplyr::left_join(dat_BE_LW,
                              dat_HI,
                              by = c("ID",
                                     "sample"
                                     )
)


dat_BE_LW_HI_SH <- dplyr::left_join(dat_BE_LW_HI,
                              dat_SH,
                              by = c("ID",
                                     "sample"
                                     )
)
```

# Check data
```{r check data}
dat_BE_LW_HI_SH %>%
  nrow()

dat_BE_LW_HI_SH %>%
  colnames()
```

# Save
```{r save data}
saveRDS(object = dat_BE_LW_HI_SH,
        file = paste0(filepath_saved_data, "final_dat_merged_", date, ".rds"))
```

