---
title: "Exclusions"
author: "Helena Davies"
date: "21/04/2022"
output: html_document
---

This script merges all the derived variables ready for regression analyses.
Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r read in data}
dat_raw <- readRDS(paste0(filepath_saved_data, "final_dat_merged_2022-10-04.rds"))

dat_raw %>%
  colnames()
```

# Incomplete surveys
Some participants are included in the dataset whose surveys expired and they didn't actually complete the questionnaire. Filter these out based on NAs in age and the first CIDID variable (For EDGI and NBR). These numbers will not be reported in the paper.

GLAD and RAMP participants were not given the CIDI. Therefore, for GLAD participants, I will use age, sex, and change in living situation (dem2.living_situation_change_pandemic). For RAMP participants, I will use gender (they weren't asked sex).
```{r read in CIDID data for EDGI and NBR participants}
# EDGI
cidid_edgi <- readRDS(paste0(filepath_raw_latest_freeze, "coping_edgi/cidid_coping_edgi.rds"))

cidid_edgi <- cidid_edgi %>%
  select(ID =  externalDataReference,
         cidid.felt_sad_blue_row)

# NBR
cidid_nbr <- readRDS(paste0(filepath_raw_latest_freeze, "coping_nbr/cidid_coping_nbr.rds"))

cidid_nbr <- cidid_nbr %>%
  select(ID =  subjectid,
         cidid.felt_sad_blue_row)

cidid_edgi_nbr <- cidid_edgi %>%
  bind_rows(cidid_nbr)
  
# Merge
dat_raw2 <- dplyr::left_join(dat_raw,
                            cidid_edgi_nbr,
                            by = "ID")
```

```{r read in living situation variable for RAMP and GLAD participants}
# GLAD
glad_living_situation <- readRDS(paste0(filepath_raw_latest_freeze, "coping_glad/dem2_coping_glad.rds"))

glad_living_situation <- glad_living_situation %>%
  select(ID =  externalDataReference,
         dem2.living_situation_change_pandemic)

# RAMP 
ramp_living_situation <- readRDS(paste0(filepath_raw_latest_freeze, "ramp/dem_ramp.rds"))

ramp_living_situation <- ramp_living_situation %>%
  select(ID =  `Login ID`,
         dem2.living_situation_change_pandemic)

living_sit_glad_ramp <- glad_living_situation %>%
  bind_rows(ramp_living_situation)

# Merge
dat_raw3 <- dplyr::left_join(dat_raw2,
                            living_sit_glad_ramp,
                            by = "ID")
```

```{r filter out unfinished participants}
dat_edgi_nbr <- dat_raw3 %>%
  filter((sample == "EDGI" |
           sample == "NBR") &
#  !is.na(age_category_COVID_baseline) &
  !is.na(sex_binary) &
   !is.na(cidid.felt_sad_blue_row))

dat_glad <- dat_raw3 %>%
  filter((sample == "GLAD") &
  !is.na(age_category_COVID_baseline) &
  !is.na(sex_binary) &
   !is.na(dem2.living_situation_change_pandemic))

dat_ramp <- dat_raw3 %>%
  filter((sample == "RAMP") &
           !is.na(minoritised_gender))

dat_ramp_glad <- dat_glad %>%
  bind_rows(dat_ramp)

# Bind rows
dat_completed <- dat_edgi_nbr %>%
  bind_rows(dat_ramp_glad)
```

# Read in data (again)
```{r read in data}
dat_raw <- readRDS(paste0(filepath_saved_data, "final_dat_merged_2022-10-04.rds"))

# Keep only those with completed COPING or RAMP data
dat <- dat_raw %>%
  filter(ID %in% dat_completed$ID)

# Check where participants are from
dat %>%
  freq(sample)
```

# Exclude people counted twice (in NBR and EDGI and/or GLAD)
```{r check NBR cohort information}
cohort_info_detailed <- read_csv(paste0(filepath_PhD, "/COPING_cohorts_28.03.2022_hash.csv"))

cohort_info_detailed <- cohort_info_detailed %>%
  select(ID = hash_id,
         cohort_detailed = panel
         )

dat <- dplyr::left_join(dat,
                        cohort_info_detailed)


# Check where people in NBR are from 
dat %>%
  filter(sample =="NBR") %>%
  freq(cohort_detailed)

# Create variable of EDGI and GLAD
dat <- dat %>%
  mutate(GLAD_EDGI_NBR_exclude =
           case_when(
             (str_detect(cohort_detailed, "GLAD") |
             str_detect(cohort_detailed, "EDGI")) ~ 1,
         
         TRUE ~ 0))

# Check
dat %>%
  freq(GLAD_EDGI_NBR_exclude)

# Drop these participants
dat <- dat %>%
  filter(GLAD_EDGI_NBR_exclude == 0)
```

# Check where participants are from before exclusion criteria applied
```{r cohort info less detail}
cohort_info <- read_csv(paste0(filepath_nbr_additional_info, "DEPRECATED_coping_participants_export_20200730_hashed.csv"))

cohort_info <- cohort_info %>%
  select(ID = "NBR ID",
         cohort 
         )

dat <- dplyr::left_join(dat,
                        cohort_info)

# Check overall sample
dat %>%
  freq(sample)

# Check RAMP
dat %>%
  filter(sample == "RAMP") %>%
  nrow()

# Check cohorts within NBR sample
dat %>%
  filter(sample == "NBR") %>%
  freq(cohort)

# Check N of total NBR
dat %>%
  filter(sample == "GLAD" |
         sample == "EDGI" |
           sample == "NBR") %>%
  nrow()
```
# EXCLUDE NAFLD (too small)
```{r exclude NAFLD}
dat <- dat %>%
  filter((sample == "GLAD" |
         sample == "EDGI" |
           sample == "RAMP") |
         cohort != "NAFLD")
```

# Save for comparing with complete data
```{r}
dat %>%
  saveRDS(paste0(filepath_saved_data, "final_dat_merged_FIRST_exclusions_", date, ".rds"))
```

# Create groups with data on outcome
```{r binge eating group}
dat_BE_possible <- dat %>%
  filter(lifetime_binge_eating_baseline_numeric == 0) # Those who reported no pre-pandemic binge eating make up our possible binge eating sample

dat_BE <- dat %>%
  filter(!is.na(NEW_binge_eating_pandemic))

nrow(dat_BE)-nrow(dat)
```
Of those who had no pre-pandemic binge eating (30,818), 6607 people were missing for new onset binge eating during the pandemic.

```{r low weight group}
dat_LW_possible <- dat %>%
  filter(lifetime_low_weight_baseline_numeric == 0) # Those who reported no pre-pandemic low weight make up our possible binge eating sample

dat_LW <- dat_LW_possible %>%
  filter(!is.na(NEW_low_weight_pandemic
              ))

nrow(dat_LW)-nrow(dat_LW_possible)
```
Of those who had no pre-pandemic low weight (31,216), 6,852 people were missing for new onset low weight during the pandemic.

```{r suicidal and/or self-harm ideation group}
dat_HI_possible <- dat %>%
  filter(PREPANDEMIC_passive_suicidal_ideation == 0 &
           PREPANDEMIC_selfharm_ideation == 0) # Those who reported no pre-pandemic low weight make up our possible binge eating sample

dat_HI <- dat_HI_possible %>%
  filter(!is.na(NEW_harmful_ideation_pandemic
              ))

nrow(dat_HI)-nrow(dat_HI_possible)
```
Of those who had no pre-pandemic harmful ideation (18,040), none were missing for new onset harmful ideation during the pandemic.

```{r self-harm ideation group}
dat_SH_possible <- dat %>%
  filter(PREPANDEMIC_selfharm == 0) # Those who reported no pre-pandemic low weight make up our possible binge eating sample

dat_SH <- dat_SH_possible %>%
  filter(!is.na(NEW_selfharm_pandemic
              ))

nrow(dat_SH)-nrow(dat_SH_possible)
```
Of those who had no pre-pandemic self-harm (30,016), 68 were missing for new onset self-harm during the pandemic.


# First, for each outcome, exclude people for missing data on ALL exposures
## BINGE EATING
i.e., keep people who have data on at least one exposure AND at least one outcome
```{r binge eating at least one exposure}
dat_BE_no_NA_exp <- dat_BE %>%
  filter(
    ( !is.na(minoritised_gender) |
        !is.na(age_category_COVID_baseline) |
        !is.na(race_binary) |
         !is.na(mental_health_diagnosis) |
         !is.na(paid_employment_key_worker) |
         !is.na(sex_binary) |
         !is.na(vulnerable_group_member) |
         !is.na(panworry_total_score)|
         !is.na(increased_loneliness_during_pandemic) |
           
         !is.na(positive_covid_test_before_BE_final) |
         !is.na(lost_someone_before_BE_final) |
         !is.na(main_eco_change_before_BE_final) |
         !is.na(living_situation_change_before_BE_final)
         )
    )

nrow(dat_BE_no_NA_exp)-nrow(dat_BE)
```
# Report n missing for exposure in the binge eating group
```{r age missing binge eating}
dat_BE_no_NA_exp_age <- dat_BE_no_NA_exp %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_BE_no_NA_exp_age)-nrow(dat_BE_no_NA_exp)
```

```{r sex missing binge eating}
dat_BE_no_NA_exp_sex <- dat_BE_no_NA_exp %>%
  drop_na(sex_binary)
nrow(dat_BE_no_NA_exp_sex)-nrow(dat_BE_no_NA_exp)
```

```{r gender missing binge eating}
dat_BE_no_NA_exp_gender <- dat_BE_no_NA_exp %>%
  drop_na(minoritised_gender)
nrow(dat_BE_no_NA_exp_gender)-nrow(dat_BE_no_NA_exp)
```
36 people missing for minoritised gender.

```{r race missing binge eating}
dat_BE_no_NA_exp_race <- dat_BE_no_NA_exp %>%
  drop_na(race_binary)
nrow(dat_BE_no_NA_exp_race)-nrow(dat_BE_no_NA_exp)
```
514 missing for race.

```{r psych disorder missing binge eating}
dat_BE_no_NA_exp_psych <- dat_BE_no_NA_exp %>%
  drop_na(mental_health_diagnosis)
nrow(dat_BE_no_NA_exp_psych)-nrow(dat_BE_no_NA_exp)
```
304 missing for psych disorder.        

```{r employment missing binge eating}
dat_BE_no_NA_exp_employ <- dat_BE_no_NA_exp %>%
  drop_na(paid_employment_key_worker)
nrow(dat_BE_no_NA_exp_employ)-nrow(dat_BE_no_NA_exp)
```        
44 missing for employment.

```{r vulnerable group member missing binge eating}
dat_BE_no_NA_exp_vuln <- dat_BE_no_NA_exp %>%
  drop_na(vulnerable_group_member)
nrow(dat_BE_no_NA_exp_vuln)-nrow(dat_BE_no_NA_exp)
```  
188 missing for vulnerable group member.

```{r pandemic worry missing binge eating}
dat_BE_no_NA_exp_panworry <- dat_BE_no_NA_exp %>%
  drop_na(panworry_total_score)
nrow(dat_BE_no_NA_exp_panworry)-nrow(dat_BE_no_NA_exp)
``` 
158 missing for pandemic worry.

```{r loneliness missing binge eating}
dat_BE_no_NA_exp_lone <- dat_BE_no_NA_exp %>%
  drop_na(increased_loneliness_during_pandemic)
nrow(dat_BE_no_NA_exp_lone)-nrow(dat_BE_no_NA_exp)
``` 
43 missing for loneliness.

```{r covid missing binge eating}
dat_BE_no_NA_exp_covid <- dat_BE_no_NA_exp %>%
  drop_na(positive_covid_test_before_BE_final)
nrow(dat_BE_no_NA_exp_covid)-nrow(dat_BE_no_NA_exp)
``` 
338 missing for COVID-19 illness/positive test.

```{r loss missing binge eating}
dat_BE_no_NA_exp_loss <- dat_BE_no_NA_exp %>%
  drop_na(lost_someone_before_BE_final)
nrow(dat_BE_no_NA_exp_loss)-nrow(dat_BE_no_NA_exp)
``` 
321 missing for losing someone due to COVID-19.

```{r main eco change missing binge eating}
dat_BE_no_NA_exp_eco <- dat_BE_no_NA_exp %>%
  drop_na(main_eco_change_before_BE_final)
nrow(dat_BE_no_NA_exp_eco)-nrow(dat_BE_no_NA_exp)
``` 
488 missing for main eco change.

```{r living situation change missing binge eating}
dat_BE_no_NA_exp_living <- dat_BE_no_NA_exp %>%
  drop_na(living_situation_change_before_BE_final)
nrow(dat_BE_no_NA_exp_living)-nrow(dat_BE_no_NA_exp)
``` 
451 missing for living situation change.

## LOW WEIGHT
i.e., keep people who have data on at least one exposure AND at least one outcome
```{r low weight at least one exposure}
dat_LW_no_NA_exp <- dat_LW %>%
  filter(
    ( !is.na(minoritised_gender) |
        !is.na(age_category_COVID_baseline) |
        !is.na(race_binary) |
         !is.na(mental_health_diagnosis) |
         !is.na(paid_employment_key_worker) |
         !is.na(sex_binary) |
         !is.na(vulnerable_group_member) |
         !is.na(panworry_total_score)|
         !is.na(increased_loneliness_during_pandemic) |
           
         !is.na(positive_covid_test_before_LW_final) |
         !is.na(lost_someone_before_LW_final) |
         !is.na(main_eco_change_before_LW_final) |
         !is.na(living_situation_change_before_LW_final)
         )
    )

nrow(dat_LW_no_NA_exp)-nrow(dat_LW)
```

# Report n missing for exposure in the low weight group
```{r age missing low weight}
dat_LW_no_NA_exp_age <- dat_LW_no_NA_exp %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_LW_no_NA_exp_age)-nrow(dat_LW_no_NA_exp)
```

```{r gender missing low weight}
dat_LW_no_NA_exp_gender <- dat_LW_no_NA_exp %>%
  drop_na(minoritised_gender)
nrow(dat_LW_no_NA_exp_gender)-nrow(dat_LW_no_NA_exp)
```
39 people missing for minoritised gender.

```{r race missing low weight}
dat_LW_no_NA_exp_race <- dat_LW_no_NA_exp %>%
  drop_na(race_binary)
nrow(dat_LW_no_NA_exp_race)-nrow(dat_LW_no_NA_exp)
```
502 missing for race.

```{r psych disorder missing low weight}
dat_LW_no_NA_exp_psych <- dat_LW_no_NA_exp %>%
  drop_na(mental_health_diagnosis)
nrow(dat_LW_no_NA_exp_psych)-nrow(dat_LW_no_NA_exp)
```
287 missing for psych disorder.        

```{r employment missing low weight}
dat_LW_no_NA_exp_employ <- dat_LW_no_NA_exp %>%
  drop_na(paid_employment_key_worker)
nrow(dat_LW_no_NA_exp_employ)-nrow(dat_LW_no_NA_exp)
```        
43 missing for employment.

```{r sex missing low weight}
dat_LW_no_NA_exp_sex <- dat_LW_no_NA_exp %>%
  drop_na(sex_binary)
nrow(dat_LW_no_NA_exp_sex)-nrow(dat_LW_no_NA_exp)
```  
93 missing for sex.

```{r vulnerable group member missing low weight}
dat_LW_no_NA_exp_vuln <- dat_LW_no_NA_exp %>%
  drop_na(vulnerable_group_member)
nrow(dat_LW_no_NA_exp_vuln)-nrow(dat_LW_no_NA_exp)
```  
192 missing for vulnerable group member.

```{r pandemic worry missing low weight}
dat_LW_no_NA_exp_panworry <- dat_LW_no_NA_exp %>%
  drop_na(panworry_total_score)
nrow(dat_LW_no_NA_exp_panworry)-nrow(dat_LW_no_NA_exp)
``` 
153 missing for pandemic worry.

```{r loneliness missing low weight}
dat_LW_no_NA_exp_lone <- dat_LW_no_NA_exp %>%
  drop_na(increased_loneliness_during_pandemic)
nrow(dat_LW_no_NA_exp_lone)-nrow(dat_LW_no_NA_exp)
``` 
46 missing for loneliness.

```{r covid missing low weight}
dat_LW_no_NA_exp_covid <- dat_LW_no_NA_exp %>%
  drop_na(positive_covid_test_before_LW_final)
nrow(dat_LW_no_NA_exp_covid)-nrow(dat_LW_no_NA_exp)
``` 
211 missing for COVID-19 illness/positive test.

```{r loss missing low weight}
dat_LW_no_NA_exp_loss <- dat_LW_no_NA_exp %>%
  drop_na(lost_someone_before_LW_final)
nrow(dat_LW_no_NA_exp_loss)-nrow(dat_LW_no_NA_exp)
``` 
222 missing for losing someone due to COVID-19.

```{r main eco change missing low weight}
dat_LW_no_NA_exp_eco <- dat_LW_no_NA_exp %>%
  drop_na(main_eco_change_before_LW_final)
nrow(dat_LW_no_NA_exp_eco)-nrow(dat_LW_no_NA_exp)
``` 
328 missing for main eco change.

```{r living situation change missing low weight}
dat_LW_no_NA_exp_living <- dat_LW_no_NA_exp %>%
  drop_na(living_situation_change_before_LW_final)
nrow(dat_LW_no_NA_exp_living)-nrow(dat_LW_no_NA_exp)
``` 
243 missing for living situation.

## HARMFUL IDEATION
i.e., keep people who have data on at least one exposure AND at least one outcome
```{r harmful ideation at least one exposure}
dat_HI_no_NA_exp <- dat_HI %>%
  filter(
    ( !is.na(minoritised_gender) |
        !is.na(age_category_COVID_baseline) |
        !is.na(race_binary) |
         !is.na(mental_health_diagnosis) |
         !is.na(paid_employment_key_worker) |
         !is.na(sex_binary) |
         !is.na(vulnerable_group_member) |
         !is.na(panworry_total_score)|
         !is.na(increased_loneliness_during_pandemic) |
           
         !is.na(positive_covid_test_before_HI_final) |
         !is.na(lost_someone_before_HI_final) |
         !is.na(main_eco_change_before_HI_final) |
         !is.na(living_situation_change_before_HI_final)
         )
    )

nrow(dat_HI_no_NA_exp)-nrow(dat_HI)
```

# Report n missing for exposure in the harmful ideation group
```{r age missing harmful ideation}
dat_HI_no_NA_exp_age <- dat_HI_no_NA_exp %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_HI_no_NA_exp_age)-nrow(dat_HI_no_NA_exp)
```

```{r gender missing harmful ideation}
dat_HI_no_NA_exp_gender <- dat_HI_no_NA_exp %>%
  drop_na(minoritised_gender)
nrow(dat_HI_no_NA_exp_gender)-nrow(dat_HI_no_NA_exp)
```
14 people missing for minoritised gender.

```{r race missing harmful ideation}
dat_HI_no_NA_exp_race <- dat_HI_no_NA_exp %>%
  drop_na(race_binary)
nrow(dat_HI_no_NA_exp_race)-nrow(dat_HI_no_NA_exp)
```
472 missing for race.

```{r psych disorder missing harmful ideation}
dat_HI_no_NA_exp_psych <- dat_HI_no_NA_exp %>%
  drop_na(mental_health_diagnosis)
nrow(dat_HI_no_NA_exp_psych)-nrow(dat_HI_no_NA_exp)
```
336 missing for psych disorder.        

```{r employment missing harmful ideation}
dat_HI_no_NA_exp_employ <- dat_HI_no_NA_exp %>%
  drop_na(paid_employment_key_worker)
nrow(dat_HI_no_NA_exp_employ)-nrow(dat_HI_no_NA_exp)
```        
29 missing for employment.

```{r sex missing harmful ideation}
dat_HI_no_NA_exp_sex <- dat_HI_no_NA_exp %>%
  drop_na(sex_binary)
nrow(dat_HI_no_NA_exp_sex)-nrow(dat_HI_no_NA_exp)
```  
25 missing for sex.

```{r vulnerable group member missing harmful ideation}
dat_HI_no_NA_exp_vuln <- dat_HI_no_NA_exp %>%
  drop_na(vulnerable_group_member)
nrow(dat_HI_no_NA_exp_vuln)-nrow(dat_HI_no_NA_exp)
```  
159 missing for vulnerable group member.

```{r pandemic worry missing harmful ideation}
dat_HI_no_NA_exp_panworry <- dat_HI_no_NA_exp %>%
  drop_na(panworry_total_score)
nrow(dat_HI_no_NA_exp_panworry)-nrow(dat_HI_no_NA_exp)
``` 
556 missing for pandemic worry.

```{r loneliness missing harmful ideation}
dat_HI_no_NA_exp_lone <- dat_HI_no_NA_exp %>%
  drop_na(increased_loneliness_during_pandemic)
nrow(dat_HI_no_NA_exp_lone)-nrow(dat_HI_no_NA_exp)
``` 
524 missing for loneliness.

```{r covid missing harmful ideation}
dat_HI_no_NA_exp_covid <- dat_HI_no_NA_exp %>%
  drop_na(positive_covid_test_before_HI_final)
nrow(dat_HI_no_NA_exp_covid)-nrow(dat_HI_no_NA_exp)
``` 
1074 missing for COVID-19 illness/positive test.

```{r loss missing harmful ideation}
dat_HI_no_NA_exp_loss <- dat_HI_no_NA_exp %>%
  drop_na(lost_someone_before_HI_final)
nrow(dat_HI_no_NA_exp_loss)-nrow(dat_HI_no_NA_exp)
``` 
1058 missing for losing someone due to COVID-19.

```{r main eco change missing harmful ideation}
dat_HI_no_NA_exp_eco <- dat_HI_no_NA_exp %>%
  drop_na(main_eco_change_before_HI_final)
nrow(dat_HI_no_NA_exp_eco)-nrow(dat_HI_no_NA_exp)
``` 
996 missing for main eco change.

```{r living situation change missing harmful ideation}
dat_HI_no_NA_exp_living <- dat_HI_no_NA_exp %>%
  drop_na(living_situation_change_before_HI_final)
nrow(dat_HI_no_NA_exp_living)-nrow(dat_HI_no_NA_exp)
``` 
502 missing for living situation.

## SELF-HARM
i.e., keep people who have data on at least one exposure AND at least one outcome
```{r self-harm at least one exposure}
dat_SH_no_NA_exp <- dat_SH %>%
  filter(
    ( !is.na(minoritised_gender) |
        !is.na(age_category_COVID_baseline) |
        !is.na(race_binary) |
         !is.na(mental_health_diagnosis) |
         !is.na(paid_employment_key_worker) |
         !is.na(sex_binary) |
         !is.na(vulnerable_group_member) |
         !is.na(panworry_total_score)|
         !is.na(increased_loneliness_during_pandemic) |
           
         !is.na(positive_covid_test_before_SH_final) |
         !is.na(lost_someone_before_SH_final) |
         !is.na(main_eco_change_before_SH_final) |
         !is.na(living_situation_change_before_SH_final)
         )
    )

nrow(dat_SH_no_NA_exp)-nrow(dat_SH)
```
# Report n missing for exposure in the self-harm group
```{r age missing self-harm}
dat_SH_no_NA_exp_age <- dat_SH_no_NA_exp %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_SH_no_NA_exp_age)-nrow(dat_SH_no_NA_exp)
```
2 missing for age.

```{r gender missing self-harm}
dat_SH_no_NA_exp_gender <- dat_SH_no_NA_exp %>%
  drop_na(minoritised_gender)
nrow(dat_SH_no_NA_exp_gender)-nrow(dat_SH_no_NA_exp)
```
35 people missing for minoritised gender.

```{r race missing self-harm}
dat_SH_no_NA_exp_race <- dat_SH_no_NA_exp %>%
  drop_na(race_binary)
nrow(dat_SH_no_NA_exp_race)-nrow(dat_SH_no_NA_exp)
```
657 missing for race.

```{r psych disorder missing self-harm}
dat_SH_no_NA_exp_psych <- dat_SH_no_NA_exp %>%
  drop_na(mental_health_diagnosis)
nrow(dat_SH_no_NA_exp_psych)-nrow(dat_SH_no_NA_exp)
```
544 missing for psych disorder.        

```{r employment missing self-harm}
dat_SH_no_NA_exp_employ <- dat_SH_no_NA_exp %>%
  drop_na(paid_employment_key_worker)
nrow(dat_SH_no_NA_exp_employ)-nrow(dat_SH_no_NA_exp)
```        
61 missing for employment.

```{r sex missing self-harm}
dat_SH_no_NA_exp_sex <- dat_SH_no_NA_exp %>%
  drop_na(sex_binary)
nrow(dat_SH_no_NA_exp_sex)-nrow(dat_SH_no_NA_exp)
```  
61 missing for sex.

```{r vulnerable group member missing self-harm}
dat_SH_no_NA_exp_vuln <- dat_SH_no_NA_exp %>%
  drop_na(vulnerable_group_member)
nrow(dat_SH_no_NA_exp_vuln)-nrow(dat_SH_no_NA_exp)
```  
266 missing for vulnerable group member.

```{r pandemic worry missing self-harm}
dat_SH_no_NA_exp_panworry <- dat_SH_no_NA_exp %>%
  drop_na(panworry_total_score)
nrow(dat_SH_no_NA_exp_panworry)-nrow(dat_SH_no_NA_exp)
``` 
1055 missing for pandemic worry.

```{r loneliness missing self-harm}
dat_SH_no_NA_exp_lone <- dat_SH_no_NA_exp %>%
  drop_na(increased_loneliness_during_pandemic)
nrow(dat_SH_no_NA_exp_lone)-nrow(dat_SH_no_NA_exp)
``` 
1034 missing for loneliness.

```{r covid missing self-harm}
dat_SH_no_NA_exp_covid <- dat_SH_no_NA_exp %>%
  drop_na(positive_covid_test_before_SH_final)
nrow(dat_SH_no_NA_exp_covid)-nrow(dat_SH_no_NA_exp)
``` 
1739 missing for COVID-19 illness/positive test.

```{r loss missing self-harm}
dat_SH_no_NA_exp_loss <- dat_SH_no_NA_exp %>%
  drop_na(lost_someone_before_SH_final)
nrow(dat_SH_no_NA_exp_loss)-nrow(dat_SH_no_NA_exp)
``` 
1724 missing for losing someone due to COVID-19.

```{r main eco change missing self-harm}
dat_SH_no_NA_exp_eco <- dat_SH_no_NA_exp %>%
  drop_na(main_eco_change_before_SH_final)
nrow(dat_SH_no_NA_exp_eco)-nrow(dat_SH_no_NA_exp)
``` 
1009 missing for main eco change.

```{r living situation change missing self-harm}
dat_SH_no_NA_exp_living <- dat_SH_no_NA_exp %>%
  drop_na(living_situation_change_before_SH_final)
nrow(dat_SH_no_NA_exp_living)-nrow(dat_SH_no_NA_exp)
``` 
89 missing for living situation.


# Now, exclude in final dataset
```{r exclude exposure-specific variables in dataset}
# Binge eating
dat <- dat %>%
  mutate(BE_data_for_model = 
           case_when(
             (ID %in% dat_BE_no_NA_exp$ID) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat %>%
  freq(BE_data_for_model)


# Low weight
dat <- dat %>%
  mutate(LW_data_for_model = 
           case_when(
             (ID %in% dat_LW_no_NA_exp$ID) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat %>%
  freq(LW_data_for_model)


# Harmful ideation
dat <- dat %>%
  mutate(HI_data_for_model = 
           case_when(
             (ID %in% dat_HI_no_NA_exp$ID) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat %>%
  freq(HI_data_for_model)


# Self-harm
dat <- dat %>%
  mutate(SH_data_for_model = 
           case_when(
             (ID %in% dat_SH_no_NA_exp$ID) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat %>%
  freq(SH_data_for_model)
```

# Keep people only included in at least one model
```{r keep those in at least one model}
dat_final <- dat %>%
  filter(BE_data_for_model == 1 |
         LW_data_for_model == 1 |
         HI_data_for_model == 1 |
         SH_data_for_model == 1)
```

# TOTAL EXCLUDED
```{r}
nrow(dat)-nrow(dat_final)
```
8356 excluded in total.

# Final dataset - cohort info
```{r dat_final cohort info}
dat_final %>%
  freq(sample)

dat_final %>%
  filter(sample == "NBR") %>%
  freq(cohort)
```

# Save
```{r save data}
dat_final %>%
  saveRDS(paste0(filepath_saved_data, "final_dat_merged_exclusions_", date, ".rds"))
```