---
title: "Comparing those excluded"
author: "Helena Davies"
date: "30/09/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r read in data with missing}
dat_NA <- readRDS(paste0(filepath_saved_data, "final_dat_merged_FIRST_exclusions_2022-09-30.rds"))

dat_NA %>%
  colnames()
```

```{r Read in data complete}
dat_complete <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-09-27.rds")
dim(dat_complete)
colnames(dat_complete)

dat_complete <- dat_complete %>%
  select(ID,
         sample,
         BE_data_for_model,
         LW_data_for_model,
         SH_data_for_model,
         HI_data_for_model)
```

## More refined education data
```{r more refined education data}
edu_dat <- readRDS(file = paste(filepath_saved_data, "highest_education_refined.rds"))

edu_dat <- edu_dat %>%
  select(ID,
         sample,
         merged_highest_education)
# Check
dim(edu_dat)
```

### Merge complete data with refined education data
```{r merge complete data with refined education data}
# Merge complete with education
dat_complete_edu <- dplyr::left_join(dat_complete,
                   edu_dat,
                   by = c("ID",
                          "sample"))


# Check
dim(dat_complete_edu)
colnames(dat_complete_edu)

# Merge complete + edu with missing data
dat <- dplyr::left_join(dat_NA,
                   dat_complete_edu,
                   by = c("ID",
                          "sample"))

# Check
dim(dat)
colnames(dat)
```

## BMI data
### BMI (at time of assessment) 
Merged: GLAD sign-up, EDGI sign-up, NBR COPING (not assessed in RAMP)
Read in data
```{r Read in data bmi}
# GLAD & EDGI
bmi_edgi_glad_signup <- readRDS(file =paste0(filepath_cleaned_latest_freeze, "glad_edgi/demographics/signup_bmi_height_weight_glad_edgi_clean.rds"))

bmi_edgi_glad_signup %>%
  colnames()

bmi_edgi_glad_signup %>%
  dim()

bmi_edgi_glad_signup <- bmi_edgi_glad_signup %>%
  select(ID,
         sample, 
         dem.bmi_signup
         )

# GLAD COPING, EDGI COPING, & NBR
bmi_coping <- readRDS(file =paste0(filepath_cleaned_latest_freeze, "coping_glad_edgi_nbr/demographics/signup_bmi_height_weight_coping_glad_edgi_nbr_clean.rds"))

bmi_coping %>%
  colnames()

bmi_coping %>%
  dim()

bmi_coping <- bmi_coping %>%
  select(ID,
         sample, 
         dem.bmi_signup_cop
         )

# Merge GLAD COPING, EDGI COPING, & NBR with GLAD & EDGI
bmi_at_assessment <- dplyr::full_join(bmi_coping,
                          bmi_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
bmi_at_assessment %>%
  dim()

# Check
bmi_at_assessment %>%
  nrow()

# Set BMIs of less than 0 (e.g., -666) to NA
bmi_at_assessment <- bmi_at_assessment %>%
  mutate(dem.bmi_signup_cop =
           case_when(dem.bmi_signup_cop < 0 ~ NA_real_,
                     TRUE ~ as.numeric(dem.bmi_signup_cop)
                     )
         )
```

```{r merge data with BMI data}
dat <- dplyr::left_join(dat,
                         bmi_at_assessment,
                         by = c("ID",
                                "sample")
)

# Check
dim(dat)
colnames(dat)
```

# Create variable for included vs not included
```{r included vs not included}
dat <- dat %>% 
  mutate(included =
           case_when(BE_data_for_model == 1 |
                       LW_data_for_model == 1 |
                       HI_data_for_model == 1 |
                       SH_data_for_model == 1  ~ "Yes",
                     
                     TRUE ~ "No"
                    ))

# Check
dat %>%
  freq(included)
```

# Compare: Categorical variables 
```{r list categorical dummy variables symptom}
descriptives.columns <- c(
  "included",
  "sex_binary",
  "minoritised_gender",
         "age_category_COVID_baseline",
         "race_binary",
         "A_Levels_higher"
)

descriptives.columns.dummy <- c(
        "sex_binary",
  "minoritised_gender",
         "age_category_COVID_baseline",
         "race_binary",
         "A_Levels_higher"
)
```

Dummy coding for categorical variables
```{r dummy coding categorical variables}
# Create dataset
descriptives_df <- dat %>%
  select(descriptives.columns)

# Dummy coding
descriptives_dummy <- fastDummies::dummy_cols(descriptives_df,
                                              select_columns = descriptives.columns.dummy
                                              )
# Check
colnames(descriptives_dummy)
```

## Age
```{r chi-squared age}
# Aged 16-25 years
dat %>%
  group_by(included) %>%
  freq(age_category_COVID_baseline)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_16-25` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 26-35 years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_26-35` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 36-45 years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_36-45` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 46-55 years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_46-55` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 56-65 years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_56-65` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 66-70 years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_66-70` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value

# Aged 71+ years
test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`age_category_COVID_baseline_71+` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value
```
## Female
```{r chi-squared female}
dat %>%
  group_by(included) %>%
  freq(sex_binary)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`sex_binary_Female` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value
```
## Racially minoritised
```{r chi-squared racially minoritised}
dat %>%
  group_by(included) %>%
  freq(race_binary)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`race_binary_Racially minoritised` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value
```

## Minoritised gender
```{r chi-squared minoritised gender}
dat %>%
  group_by(included) %>%
  freq(minoritised_gender)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`minoritised_gender_Yes` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value
```

## Highest education
```{r chi-squared A levels higher}
dat <- dat %>%
  mutate(A_Levels_higher =
           case_when(A_Levels_higher == "Yes" ~ "Yes",
                     TRUE ~ "No"
                     )
  )

dat %>%
  group_by(included) %>%
  freq(A_Levels_higher)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$`A_Levels_higher_Yes` ~ descriptives_dummy$included ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")
test$p.value
```
# Continous variables
## Table: Comparison of BMI
```{r table compare continuous variables symptom}
# Create table
numeric_table <- dat %>% 
  group_by(included) %>%
  summarise_at(vars(dem.bmi_signup_cop),
    .funs =
      list(
        ~IQR(., na.rm=T),
        ~median(., na.rm = T)
      )
  )

numeric_table
```

Both assumptions violated; so performed the non-parametric equivalent of t-test: Mann-Whitney
```{r independent 2-group Mann-Whitney U test bmi}
bmi_wilcox <- wilcox.test(dat$dem.bmi_signup_cop ~ dat$included
                          ,
            correct = FALSE,
            exact = FALSE,
            p.adjust.methods = "fdr")

bmi_wilcox$p.value
print(age_wilcox)
```