---
title: "Exclusions"
author: "Helena Davies"
date: "21/04/2022"
output: html_document
---

This script merges all the derived variables ready for regression analyses.
Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r read in data}
dat_raw <- readRDS(paste0(filepath_saved_data, "final_dat_merged_2022-04-21.rds"))
```

# Filter out by people who either answered the COPING survey or are a RAMP participant ++ need to work on this- is there another wya to assess participation in COPING?
```{r}
dat_not_cop <- dat_raw %>%
  filter((sample == "GLAD" |
           sample == "EDGI") &
  is.na(age_category_COVID_baseline))
  
dat <- dat_raw %>%
  filter(ID %!in% dat_not_cop$ID)

dat %>%
  filter(sample != "RAMP") %>%
  nrow()
```

# Exclude people counted twice (in NBR and EDGI and/or GLAD)
```{r check NBR cohort information}
cohort_info_detailed <- read_csv(paste0(filepath_PhD, "/COPING_cohorts_28.03.2022_hash.csv"))

cohort_info_detailed <- cohort_info_detailed %>%
  select(ID = hash_id,
         cohort_detailed = panel
         )

cohort_info_detailed %>%
  freq(cohort_detailed)

dat <- dplyr::full_join(dat,
                        cohort_info_detailed)


dat %>%
  filter(sample =="NBR") %>%
  freq(cohort_detailed)

# Create variable of EDGI and GLAD
dat <- dat %>%
  mutate(GLAD_EDGI_NBR_exclude =
           case_when(
             (str_detect(cohort_detailed, "GLAD") |
             str_detect(cohort_detailed, "EDGI")) ~ 1,
         
         TRUE ~ 0))

# Check
dat %>%
  freq(GLAD_EDGI_NBR_exclude)

# Drop these participants
dat <- dat %>%
  filter(GLAD_EDGI_NBR_exclude == 0)
```

# Check where participants are from before exclusion criteria applied
```{r cohort info less detail}
cohort_info <- read_csv(paste0(filepath_nbr_additional_info, "DEPRECATED_coping_participants_export_20200730_hashed.csv"))

cohort_info <- cohort_info %>%
  select(ID = "NBR ID",
         cohort 
         )

dat <- dplyr::left_join(dat,
                        cohort_info)

# Check overall sample
dat %>%
  freq(sample)

# Check cohorts within NBR sample
dat %>%
  filter(sample == "NBR") %>%
  freq(cohort)

# Check N of total NBR
dat %>%
  filter(sample != "RAMP") %>%
  nrow()
```

# Exclude for missing data on ANY exposure
## Gender
Exclude participants with missing gender
```{r gender missing diagnosis data}
dim(dat)
dat_excl_gen <- dat %>%
  drop_na(gender_cleaned)
nrow(dat_excl_gen)-nrow(dat)
```
17,414 participants did not report their gender

## Age
Exclude participants with missing age
```{r age missing diagnosis data}
dat_excl_gen_age <- dat_excl_gen %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_excl_gen_age)-nrow(dat_excl_gen)

dat_excl_age <- dat %>%
  drop_na(age_category_COVID_baseline)
nrow(dat_excl_age)-nrow(dat)
```
14,001 did not report their age

## Race
Exclude participants with missing race
```{r race missing diagnosis data}
dat_excl_gen_age_race <- dat_excl_gen_age %>%
  drop_na(race_binary)
nrow(dat_excl_gen_age_race)-nrow(dat_excl_gen_age)

dat_excl_race <- dat %>%
  drop_na(race_binary)
nrow(dat_excl_race)-nrow(dat)
```
15,500 did not report their race

## Education level
Exclude participants with missing education level
```{r education missing diagnosis data}
dat_excl_gen_age_race_edu <- dat_excl_gen_age_race %>%
  drop_na(highest_education)
nrow(dat_excl_gen_age_race_edu)-nrow(dat_excl_gen_age_race)

dat_excl_edu <- dat %>%
  drop_na(highest_education)
nrow(dat_excl_edu)-nrow(dat)
```
18,288 did not report their education level

## Mental health diagnosis
Exclude participants with missing education level
```{r mental health diagnosis missing diagnosis data}
dat_excl_gen_age_race_edu_psych <- dat_excl_gen_age_race_edu %>%
  drop_na(mental_health_diagnosis)
nrow(dat_excl_gen_age_race_edu_psych)-nrow(dat_excl_gen_age_race_edu)

dat_excl_psych <- dat %>%
  drop_na(mental_health_diagnosis)
nrow(dat_excl_psych)-nrow(dat)
```
15,822 did not report their mental health diagnosis

## Employment status
Exclude participants with missing employment level
```{r employment missing diagnosis data}
dat_excl_gen_age_race_edu_psych_emp <- dat_excl_gen_age_race_edu_psych %>%
  drop_na(paid_employment_key_worker)
nrow(dat_excl_gen_age_race_edu_psych_emp)-nrow(dat_excl_gen_age_race_edu_psych)

dat_excl_emp <- dat %>%
  drop_na(paid_employment_key_worker)
nrow(dat_excl_emp)-nrow(dat)
```
18,386 did not report their employment status

## Being a vulnerable group member
Exclude participants with missing vulnerable member data
```{r vulnerable member missing diagnosis data}
dat_excl_gen_age_race_edu_psych_emp_vuln <- dat_excl_gen_age_race_edu_psych_emp %>%
  drop_na(vulnerable_group_member)
nrow(dat_excl_gen_age_race_edu_psych_emp_vuln)-nrow(dat_excl_gen_age_race_edu_psych)

dat_excl_vuln <- dat %>%
  drop_na(vulnerable_group_member)
nrow(dat_excl_vuln)-nrow(dat)
```
18,723 did not report being a vulnerable group member

## Pandemic worry score
Exclude participants with missing pandemic worry
```{r pandemic worry missing diagnosis data}
dat_excl_gen_age_race_edu_psych_emp_vuln_pan <- dat_excl_gen_age_race_edu_psych_emp_vuln %>%
  drop_na(panworry_total_score)
nrow(dat_excl_gen_age_race_edu_psych_emp_vuln_pan)-nrow(dat_excl_gen_age_race_edu_psych_emp_vuln)

dat_excl_pan <- dat %>%
  drop_na(panworry_total_score)
nrow(dat_excl_pan)-nrow(dat)
```
34,652 did not report a pandemic worry score at baseline

### How many excluded so far?
```{r excluded so far}
nrow(dat_excl_gen_age_race_edu_psych_emp_vuln_pan)-nrow(dat)
```
# The remaining variables are specific to each outcome variable.
As long as someone has all the exposure variables for ONE of the outcome variables AND the relevant outcome variable, then we would like to 'keep' them.
```{r}
# Binge eating
dat_excl_gen_age_race_edu_psych_emp_vuln_pan <- dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  mutate(BE_data_for_model = 
           case_when(
             (!is.na(positive_covid_test_before_BE_final) &
                 !is.na(lost_someone_before_BE_final) &
                 !is.na(main_eco_change_before_BE_final) &
                 !is.na(living_situation_change_before_BE_final) &
                 !is.na(NEW_binge_eating_pandemic)) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  freq(BE_data_for_model)

# Low weight
dat_excl_gen_age_race_edu_psych_emp_vuln_pan <- dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  mutate(LW_data_for_model = 
           case_when(
             (!is.na(positive_covid_test_before_LW_final) &
                 !is.na(lost_someone_before_LW_final) &
                 !is.na(main_eco_change_before_LW_final) &
                 !is.na(living_situation_change_before_LW_final) &
                 !is.na(NEW_low_weight_pandemic) &
                 !is.na(ocd.compulsive_beh_mental_act_binary) &
                 !is.na(ocd.repetitive_unpleasant_thoughts_binary)
                ) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  freq(LW_data_for_model)


# Suicidal and/or self-harm ideation
dat_excl_gen_age_race_edu_psych_emp_vuln_pan <- dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  mutate(HI_data_for_model = 
           case_when(
             (!is.na(positive_covid_test_before_HI_final) &
                 !is.na(lost_someone_before_HI_final) &
                 !is.na(main_eco_change_before_HI_final) &
                 !is.na(living_situation_change_before_HI_final) &
                 !is.na(NEW_harmful_ideation_pandemic)) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  freq(HI_data_for_model)

# Self-harm
dat_excl_gen_age_race_edu_psych_emp_vuln_pan <- dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  mutate(SH_data_for_model = 
           case_when(
             (!is.na(positive_covid_test_before_SH_final) &
                 !is.na(lost_someone_before_SH_final) &
                 !is.na(main_eco_change_before_SH_final) &
                 !is.na(living_situation_change_before_SH_final) &
                 !is.na(NEW_selfharm_pandemic)) ~ 1,
         
                TRUE ~ 0)
  )

# Check
dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  freq(SH_data_for_model)

# How many have NO full data for ANY of the models?
dat_final <- dat_excl_gen_age_race_edu_psych_emp_vuln_pan %>%
  filter(SH_data_for_model == 1 |
         HI_data_for_model== 1 |
           LW_data_for_model == 1 |
           BE_data_for_model == 1)

nrow(dat_excl_gen_age_race_edu_psych_emp_vuln_pan)-nrow(dat_final)
```

# Double check that all participants are included in at least one of the models
```{r double check}
dat_NA_BE_model <- dat_final %>%
  filter(is.na(NEW_binge_eating_pandemic) |
                 is.na(age_category_COVID_baseline) |
                 is.na(gender_cleaned) |
                 is.na(race_binary) |
                 is.na(highest_education) |
                 is.na(mental_health_diagnosis)|
                 is.na(paid_employment_key_worker) |
                 is.na(vulnerable_group_member) |
                 is.na(panworry_total_score) |
                 is.na(positive_covid_test_before_BE_final) |
                 is.na(lost_someone_before_BE_final) |
                 is.na(main_eco_change_before_BE_final) |
                 is.na(living_situation_change_before_BE_final))
  
dat_NA_LW_model <- dat_NA_BE_model %>%
  filter(is.na(NEW_low_weight_pandemic) |
                 is.na(age_category_COVID_baseline) |
                 is.na(gender_cleaned) |
                 is.na(race_binary) |
                 is.na(highest_education) |
                 is.na(mental_health_diagnosis)|
                 is.na(paid_employment_key_worker) |
                 is.na(vulnerable_group_member) |
                 is.na(panworry_total_score) |
                 is.na(positive_covid_test_before_LW_final) |
                 is.na(lost_someone_before_LW_final) |
                 is.na(main_eco_change_before_LW_final) |
                 is.na(living_situation_change_before_LW_final) |
                 is.na(ocd.compulsive_beh_mental_act_binary) |
                 is.na(ocd.repetitive_unpleasant_thoughts_binary))

dat_NA_HI_model <- dat_NA_LW_model %>%
  filter(is.na(NEW_harmful_ideation_pandemic) |
                 is.na(age_category_COVID_baseline) |
                 is.na(gender_cleaned) |
                 is.na(race_binary) |
                 is.na(highest_education) |
                 is.na(mental_health_diagnosis)|
                 is.na(paid_employment_key_worker) |
                 is.na(vulnerable_group_member) |
                 is.na(panworry_total_score) |
                 is.na(positive_covid_test_before_HI_final) |
                 is.na(lost_someone_before_HI_final) |
                 is.na(main_eco_change_before_HI_final) |
                 is.na(living_situation_change_before_HI_final)) 

# The n of dat_NA_SH_model should be 0 (it is)
dat_NA_SH_model <- dat_NA_HI_model %>%
  filter(is.na(NEW_selfharm_pandemic) |
                 is.na(age_category_COVID_baseline) |
                 is.na(gender_cleaned) |
                 is.na(race_binary) |
                 is.na(highest_education) |
                 is.na(mental_health_diagnosis)|
                 is.na(paid_employment_key_worker) |
                 is.na(vulnerable_group_member) |
                 is.na(panworry_total_score) |
                 is.na(positive_covid_test_before_SH_final) |
                 is.na(lost_someone_before_SH_final) |
                 is.na(main_eco_change_before_SH_final) |
                 is.na(living_situation_change_before_SH_final)) 
```

# Final dataset - cohort info
```{r dat_final cohort info}
dat_final %>%
  freq(sample)

dat_final %>%
  filter(sample == "NBR") %>%
  freq(cohort)
```

# Save
```{r}
dat_final %>%
  saveRDS(paste0(filepath_saved_data, "final_dat_merged_exclusions_", date, ".rds"))
```



