---
title: "Latent class analysis - EDEQ"
author: "Helena Davies"
date: "12/08/2021"
output: html_document
---
# Set up 
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

Call in library script
```{r Source library files}
source("./libraries.R")
```

Retrieve the recent date
```{r Recent date}
date = Sys.Date()
date
```

Call in R functions scripts
```{r Call in function library functions}
source("./functions.R")
```

# Read in EDEQ baseline data
## data.final is generated from the "3.Merging" script
```{r Read in data}
baseline_edeq_raw <- readRDS(file = "../data_raw/ramp/edeq_ramp.rds")

# Check
dim(baseline_edeq_raw)
colnames(baseline_edeq_raw)
```

## Select edeq columns
```{r Select edeq columns from ramp baseline data}

exclude_cols_dem <- c("ID")

baseline_edeq_raw.id <- baseline_edeq_raw %>% #new dataset with ID
  drop_na(`Login ID`) %>% # Drop NAs
  select(
         ID = `Login ID`, # ID
         edeq.deliberately_limit_amount_influence_baseline = edeq.deliberately_limit_amount_influence,              
         edeq.calories_made_body_shape_baseline = edeq.calories_made_body_shape,                    
         edeq.weight_influenced_person_baseline = edeq.weight_influenced_person,                        
         edeq.dissatisfied_shape_weight_baseline = edeq.dissatisfied_shape_weight,                    
         edeq.nibbled_picked_snacks_grazed_baseline = edeq.nibbled_picked_snacks_grazed,                    
         edeq.felt_anxious_blue_bored_baseline = edeq.felt_anxious_blue_bored,                     
         edeq.felt_anxious_blue_bored.1_baseline = edeq.felt_anxious_blue_bored.1,        
         edeq.actively_been_monitoring_your_shape_or_weight__baseline = edeq.actively_been_monitoring_your_shape_or_weight_,
         edeq.regard_lost_control_eaten_baseline = edeq.regard_lost_control_eaten,
         edeq.sick_means_made_shape_baseline = edeq.sick_means_made_shape,
         edeq.diuretics_laxatives_means_shape_baseline = edeq.diuretics_laxatives_means_shape,
         edeq.compulsive_driven_burn_calories_baseline = edeq.compulsive_driven_burn_calories,
         edeq.eating_behaviours_concerns_distressed_baseline = edeq.eating_behaviours_concerns_distressed
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
 #mutate_if(is.numeric, ~na_if(., -99)) %>%
  #mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
 # mutate_if(is.factor, ~na_if(., "Don't know")) %>%
 # mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
 # mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) # Drop empty factor levels
 # mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
 # mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
 # mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
# Inspect dimensions
dim(baseline_edeq_raw.id)
# Inspect colnames
colnames(baseline_edeq_raw.id)
#Differences
dim(baseline_edeq_raw.id)[1]-dim(baseline_edeq_raw)[1]
freq(baseline_edeq_raw.id$edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric)
```

```{r select columns}
ramp_baseline_edeq <- baseline_edeq_raw.id %>%
  select(ID,
     edeq.deliberately_limit_amount_influence_baseline,            
         edeq.calories_made_body_shape_baseline,                   
         edeq.weight_influenced_person_baseline,                       
         edeq.dissatisfied_shape_weight_baseline ,                   
         edeq.nibbled_picked_snacks_grazed_baseline, 
        edeq.eating_behaviours_concerns_distressed_baseline,
         edeq.felt_anxious_blue_bored_baseline,                    
         edeq.felt_anxious_blue_bored.1_baseline,   
         edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric,
         edeq.regard_lost_control_eaten_baseline_numeric,
         edeq.sick_means_made_shape_baseline_numeric,
         edeq.diuretics_laxatives_means_shape_baseline_numeric,
         edeq.compulsive_driven_burn_calories_baseline_numeric
     )

```


# EDEQ follow up B
## COPING
### Read in data
NB: The EDEQ  is only available in follow up B across both RAMP and COPING.
```{r Read in data COPING follow up B EDEQ }
edeq_followup_COPING <- readRDS(file = "../data_raw/coping/edeq_coping_followupb.rds")

# Check
dim(edeq_followup_COPING)
colnames(edeq_followup_COPING)
```

Select variables COPING follow up B EDEQ 
```{r Select variables COPING follow up B EDEQ }

exclude_cols_dem <- c("ID",
                  "startDate_waves",
                  "endDate")

edeq_followup_COPING.id <- edeq_followup_COPING %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  select(
         ID = externalDataReference, # ID
         startDate_waves = startDate,
         edeq.deliberately_limit_amount_influence,
         edeq.calories_made_body_shape,                     
         edeq.weight_influenced_person,                      
         edeq.dissatisfied_shape_weight,                     
         edeq.actively_been_monitoring_your_shape_or_weight_, ### +++ HAL HERE - Change these to numeric 
         edeq.regard_lost_control_eaten,                    
         edeq.sick_means_made_shape,                      
         edeq.diuretics_laxatives_means_shape,               
         edeq.compulsive_driven_burn_calories,              
         edeq.eating_behaviours_distressed_concerns,        
         edeq.nibbled_picked_snacks_grazed,                  
         edeq.felt_anxious_blue_bored,                        
         edeq.felt_anxious_blue_bored.1                  
        # edeq.experiences_pandemic                     
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  #mutate_if(is.numeric, ~na_if(., -99)) %>%
 # mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  #mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  #mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
 # mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) # Drop empty factor levels
  #mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
 # mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  #mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(edeq_followup_COPING.id)
# Inspect colnames
colnames(edeq_followup_COPING.id)
#Differences
dim(edeq_followup_COPING)[1]-dim(edeq_followup_COPING.id)[1]

```

# EDEQ follow up B
## RAMP
### Read in data
```{r Read in data RAMP follow up B EDEQ }

edeq_followup_RAMP <- readRDS(file = "../data_raw/ramp/edeq_ramp_followupb.rds")

# Check
dim(edeq_followup_RAMP)
colnames(edeq_followup_RAMP)

```
Select variables COPING follow up B EDEQ 
```{r Select variables COPING follow up B EDEQ }

exclude_cols_dem <- c("ID",
                  "startDate_waves",
                  "endDate")

edeq_followup_RAMP.id <- edeq_followup_RAMP %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  select(
         ID = externalDataReference, # ID
         startDate_waves = startDate,
         edeq.deliberately_limit_amount_influence,
         edeq.calories_made_body_shape,                     
         edeq.weight_influenced_person,                      
         edeq.dissatisfied_shape_weight,                     
         edeq.actively_been_monitoring_your_shape_or_weight_,
         edeq.regard_lost_control_eaten,                    
         edeq.sick_means_made_shape,                      
         edeq.diuretics_laxatives_means_shape,               
         edeq.compulsive_driven_burn_calories,              
         edeq.eating_behaviours_distressed_concerns,        
         edeq.nibbled_picked_snacks_grazed,                  
         edeq.felt_anxious_blue_bored,                        
         edeq.felt_anxious_blue_bored.1                 
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  #mutate_if(is.numeric, ~na_if(., -99)) %>%
 # mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  #mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  #mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
 # mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) # Drop empty factor levels
  #mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
 # mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  #mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(edeq_followup_RAMP.id)
# Inspect colnames
colnames(edeq_followup_RAMP.id)
#Differences
dim(edeq_followup_RAMP)[1]-dim(edeq_followup_RAMP.id)[1]

```

# TIMEPOINTS / PHASES - RAMP - EDEQ 
Create phase columns in follow up data - RAMP
```{r Identify phases source script RAMP}

# MAY 1 (wave 1b) - FOLLOW UP B
start2 <- as.POSIXct("2020-05-05")
end2 <-  as.POSIXct("2020-05-19")  

# JUNE 1 (wave 2b) - FOLLOW UP B ##COPING STARTS HERE
start4 <- as.POSIXct("2020-06-02")
end4 <-  as.POSIXct("2020-06-16")  

# JULY 1 (wave 3b) - FOLLOW UP B
start6 <- as.POSIXct("2020-06-30")
end6 <-  as.POSIXct("2020-07-14") 

# JULY - AUG (wave 4b) - FOLLOW UP B
start8 <- as.POSIXct("2020-07-28")
end8 <-  as.POSIXct("2020-08-25") 

# SEPT - OCT (wave 6b) - FOLLOW UP B
start10 <- as.POSIXct("2020-09-22")
end10 <-  as.POSIXct("2020-10-20") 

# NOV - DEC (wave 8b) - FOLLOW UP B
start12 <- as.POSIXct("2020-11-17")
end12 <-  as.POSIXct("2020-12-15") 

# JAN - FEB (wave 10b) - FOLLOW UP B
start14 <- as.POSIXct("2021-01-12")
end14 <-  as.POSIXct("2021-02-09") 

# MARCH - APRIL (wave 11a) - FOLLOW UP B
start16 <- as.POSIXct("2021-03-09")
end16 <-  as.POSIXct("2021-06-06") 

edeq_followup_RAMP.id <- edeq_followup_RAMP.id %>%
  mutate(wave_edeq =  case_when(
    startDate_waves >= start2 & startDate_waves < end2 ~ ".Wave_1b",
    startDate_waves >= start4 & startDate_waves < end4 ~ ".Wave_2b",
    startDate_waves >= start6 & startDate_waves < end6 ~ ".Wave_3b",
    startDate_waves >= start8 & startDate_waves < end8 ~ ".Wave_4b",
    startDate_waves >= start10 & startDate_waves < end10 ~ ".Wave_6b",
    startDate_waves >= start12 & startDate_waves < end12 ~ ".Wave_8b",
    startDate_waves >= start14 & startDate_waves < end14 ~ ".Wave_10b",
    startDate_waves >= start16 & startDate_waves < end16 ~ ".Wave_12b"))
```

Check number of entries per wave
```{r Check number of entries per wave RAMP EDEQ }

edeq_followup_RAMP.id %>%
  group_by(wave_edeq) %>%
  count()

```

Idenfity duplicate IDs in a single wave
```{r Idenfity duplicate IDs in a single wave RAMP EDEQ }

# Identify dup IDs in a single wave
edeq_followup_RAMP.id %>%
   group_by(wave_edeq, ID) %>%
   summarize(N = n()) %>%
   filter(N > 1)

```

Want the LATER data entry from people who answered twice within a single wave (again, for now!)
[want ID AND wave to be unique]
```{r Later date entry RAMP EDEQ }
# Confirm number of rows in current dataset 
nrow(edeq_followup_RAMP.id)

# Filter out duplicated IDs AND wave, keeping the LAST entry
edeq_followup_RAMP.id <- edeq_followup_RAMP.id %>% 
    group_by(ID) %>% 
    filter(!duplicated(wave_edeq,
                      fromLast = TRUE)
           )

nrow(edeq_followup_RAMP.id)

```

Change follow up EDEQ RAMP  to wide format

```{r RAMP EDEQ  wide format}
edeq_followup_RAMP.id <- edeq_followup_RAMP.id %>%
  group_by(wave_edeq) %>%
  mutate(row = row_number()) %>%
  tidyr::pivot_wider(id_cols = ID,
    names_from = wave_edeq, 
                     values_from = c(edeq.deliberately_limit_amount_influence,
                                     edeq.calories_made_body_shape,                     
                                     edeq.weight_influenced_person,                      
                                     edeq.dissatisfied_shape_weight,                     
                                     edeq.actively_been_monitoring_your_shape_or_weight__numeric,
                                     edeq.regard_lost_control_eaten_numeric,                    
                                     edeq.sick_means_made_shape_numeric,                      
                                     edeq.diuretics_laxatives_means_shape_numeric,               
                                     edeq.compulsive_driven_burn_calories_numeric,              
                                     edeq.eating_behaviours_distressed_concerns,        
                                     edeq.nibbled_picked_snacks_grazed,                  
                                     edeq.felt_anxious_blue_bored,                        
                                     edeq.felt_anxious_blue_bored.1)) 
  

```

Select variables for dataset EDEQ RAMP 
```{r Select variables for dataset RAMP EDEQ }
edeq_followup_RAMP.id <- edeq_followup_RAMP.id  %>%
  select(ID,
         edeq.deliberately_limit_amount_influence_.Wave_1b,
         edeq.deliberately_limit_amount_influence_.Wave_2b,    
         edeq.deliberately_limit_amount_influence_.Wave_3b,       
         edeq.deliberately_limit_amount_influence_.Wave_4b,
         edeq.deliberately_limit_amount_influence_.Wave_6b,
         edeq.deliberately_limit_amount_influence_.Wave_8b,
         edeq.deliberately_limit_amount_influence_.Wave_10b,
         edeq.deliberately_limit_amount_influence_.Wave_12b,
        
         edeq.calories_made_body_shape_.Wave_1b,
         edeq.calories_made_body_shape_.Wave_2b,    
         edeq.calories_made_body_shape_.Wave_3b,       
         edeq.calories_made_body_shape_.Wave_4b,
         edeq.calories_made_body_shape_.Wave_6b,
         edeq.calories_made_body_shape_.Wave_8b,
         edeq.calories_made_body_shape_.Wave_10b,
         edeq.calories_made_body_shape_.Wave_12b,
        
         edeq.weight_influenced_person_.Wave_1b,
         edeq.weight_influenced_person_.Wave_2b,    
         edeq.weight_influenced_person_.Wave_3b,       
         edeq.weight_influenced_person_.Wave_4b,
         edeq.weight_influenced_person_.Wave_6b,
         edeq.weight_influenced_person_.Wave_8b,
         edeq.weight_influenced_person_.Wave_10b,
         edeq.weight_influenced_person_.Wave_12b,
        
         edeq.dissatisfied_shape_weight_.Wave_1b,
         edeq.dissatisfied_shape_weight_.Wave_2b,    
         edeq.dissatisfied_shape_weight_.Wave_3b,       
         edeq.dissatisfied_shape_weight_.Wave_4b,
         edeq.dissatisfied_shape_weight_.Wave_6b,
         edeq.dissatisfied_shape_weight_.Wave_8b,
         edeq.dissatisfied_shape_weight_.Wave_10b,
         edeq.dissatisfied_shape_weight_.Wave_12b,
         
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b,
         
         edeq.regard_lost_control_eaten_numeric_.Wave_1b,
         edeq.regard_lost_control_eaten_numeric_.Wave_2b,
         edeq.regard_lost_control_eaten_numeric_.Wave_3b,
         edeq.regard_lost_control_eaten_numeric_.Wave_4b,
         edeq.regard_lost_control_eaten_numeric_.Wave_6b,
         edeq.regard_lost_control_eaten_numeric_.Wave_8b,
         edeq.regard_lost_control_eaten_numeric_.Wave_10b,
         edeq.regard_lost_control_eaten_numeric_.Wave_12b,
         
         edeq.sick_means_made_shape_numeric_.Wave_1b,
         edeq.sick_means_made_shape_numeric_.Wave_2b,
         edeq.sick_means_made_shape_numeric_.Wave_3b,
         edeq.sick_means_made_shape_numeric_.Wave_4b,
         edeq.sick_means_made_shape_numeric_.Wave_6b,
         edeq.sick_means_made_shape_numeric_.Wave_8b,
         edeq.sick_means_made_shape_numeric_.Wave_10b,
         edeq.sick_means_made_shape_numeric_.Wave_12b,
         
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b,
         
         edeq.compulsive_driven_burn_calories_numeric_.Wave_1b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_2b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_3b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_4b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_6b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_8b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_10b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_12b,
         
         edeq.eating_behaviours_distressed_concerns_.Wave_1b,
         edeq.eating_behaviours_distressed_concerns_.Wave_2b,
         edeq.eating_behaviours_distressed_concerns_.Wave_3b,
         edeq.eating_behaviours_distressed_concerns_.Wave_4b,
         edeq.eating_behaviours_distressed_concerns_.Wave_6b,
         edeq.eating_behaviours_distressed_concerns_.Wave_8b,
         edeq.eating_behaviours_distressed_concerns_.Wave_10b,
         edeq.eating_behaviours_distressed_concerns_.Wave_12b,
         
         edeq.nibbled_picked_snacks_grazed_.Wave_1b,
         edeq.nibbled_picked_snacks_grazed_.Wave_2b,
         edeq.nibbled_picked_snacks_grazed_.Wave_3b,
         edeq.nibbled_picked_snacks_grazed_.Wave_4b,
         edeq.nibbled_picked_snacks_grazed_.Wave_6b,
         edeq.nibbled_picked_snacks_grazed_.Wave_8b,
         edeq.nibbled_picked_snacks_grazed_.Wave_10b,
         edeq.nibbled_picked_snacks_grazed_.Wave_12b,
         
         edeq.felt_anxious_blue_bored_.Wave_1b,
         edeq.felt_anxious_blue_bored_.Wave_2b,
         edeq.felt_anxious_blue_bored_.Wave_3b,
         edeq.felt_anxious_blue_bored_.Wave_4b,
         edeq.felt_anxious_blue_bored_.Wave_6b,
         edeq.felt_anxious_blue_bored_.Wave_8b,
         edeq.felt_anxious_blue_bored_.Wave_10b,
         edeq.felt_anxious_blue_bored_.Wave_12b,
         
         edeq.felt_anxious_blue_bored.1_.Wave_1b,
         edeq.felt_anxious_blue_bored.1_.Wave_2b,
         edeq.felt_anxious_blue_bored.1_.Wave_3b,
         edeq.felt_anxious_blue_bored.1_.Wave_4b,
         edeq.felt_anxious_blue_bored.1_.Wave_6b,
         edeq.felt_anxious_blue_bored.1_.Wave_8b,
         edeq.felt_anxious_blue_bored.1_.Wave_10b,
         edeq.felt_anxious_blue_bored.1_.Wave_12b)
```

Remove duplicate IDs EDEQ RAMP 
```{r Remove duplicate IDs RAMP EDEQ }

# Check col names
colnames(edeq_followup_RAMP.id)

# Remove dupilcate IDs (as each wave is now a column, there should be NO dup IDs)
edeq_followup_RAMP.id  <- edeq_followup_RAMP.id  %>%
  filter(., !duplicated(ID)) 

# Check number of rows
nrow(edeq_followup_RAMP.id)

```

# TIMEPOINTS / PHASES - COPING - EDEQ 
Create phase columns in follow up data - COPING
```{r Identify phases COPING}

edeq_followup_COPING.id <- edeq_followup_COPING.id %>%
  mutate(wave_edeq =  case_when(
   # startDate_waves >= start2 & startDate_waves < end2 ~ ".Wave_1b",
    startDate_waves >= start4 & startDate_waves < end4 ~ ".Wave_2b",
    startDate_waves >= start6 & startDate_waves < end6 ~ ".Wave_3b",
    startDate_waves >= start8 & startDate_waves < end8 ~ ".Wave_4b",
    startDate_waves >= start10 & startDate_waves < end10 ~ ".Wave_6b",
    startDate_waves >= start12 & startDate_waves < end12 ~ ".Wave_8b",
    startDate_waves >= start14 & startDate_waves < end14 ~ ".Wave_10b",
    startDate_waves >= start16 & startDate_waves < end16 ~ ".Wave_12b"))
```

Check number of entries per wave
```{r Check number of entries per wave COPING EDEQ }

edeq_followup_COPING.id %>%
  group_by(wave_edeq) %>%
  count()

```

Check number of entries per wave
```{r Check number of entries per wave COPING EDEQ }

edeq_followup_COPING.id %>%
  group_by(wave_edeq) %>%
  count()

```

Idenfity duplicate IDs in a single wave
```{r Idenfity duplicate IDs in a single wave COPING EDEQ }

# Identify dup IDs in a single wave
edeq_followup_COPING.id %>%
   group_by(wave_edeq, ID) %>%
   summarize(N = n()) %>%
   filter(N > 1)

```

Want the LATER data entry from people who answered twice within a single wave (again, for now!)
[want ID AND wave to be unique]
```{r Later date entry COPING EDEQ }
# Confirm number of rows in current dataset 
nrow(edeq_followup_COPING.id)

# Filter out duplicated IDs AND wave, keeping the LAST entry
edeq_followup_COPING.id <- edeq_followup_COPING.id %>% 
    group_by(ID) %>% 
    filter(!duplicated(wave_edeq,
                      fromLast = TRUE)
           )

nrow(edeq_followup_COPING.id)

```

Change follow up EDEQ COPING  to wide format

```{r COPING EDEQ  wide format}
edeq_followup_COPING.id <- edeq_followup_COPING.id %>%
  group_by(wave_edeq) %>%
  mutate(row = row_number()) %>%
  tidyr::pivot_wider(id_cols = ID,
    names_from = wave_edeq, 
                     values_from = c(edeq.deliberately_limit_amount_influence,
                                     edeq.calories_made_body_shape,                     
                                     edeq.weight_influenced_person,                      
                                     edeq.dissatisfied_shape_weight,                     
                                     edeq.actively_been_monitoring_your_shape_or_weight__numeric,
                                     edeq.regard_lost_control_eaten_numeric,                    
                                     edeq.sick_means_made_shape_numeric,                      
                                     edeq.diuretics_laxatives_means_shape_numeric,               
                                     edeq.compulsive_driven_burn_calories_numeric,              
                                     edeq.eating_behaviours_distressed_concerns,        
                                     edeq.nibbled_picked_snacks_grazed,                  
                                     edeq.felt_anxious_blue_bored,                        
                                     edeq.felt_anxious_blue_bored.1)) 
  

```

Select variables for dataset EDEQ COPING 

```{r Select variables for dataset COPING EDEQ }
edeq_followup_COPING.id <- edeq_followup_COPING.id  %>%
  select(ID,
         #edeq.deliberately_limit_amount_influence_.Wave_1b,
         edeq.deliberately_limit_amount_influence_.Wave_2b,    
         edeq.deliberately_limit_amount_influence_.Wave_3b,       
         edeq.deliberately_limit_amount_influence_.Wave_4b,
         edeq.deliberately_limit_amount_influence_.Wave_6b,
         edeq.deliberately_limit_amount_influence_.Wave_8b,
         edeq.deliberately_limit_amount_influence_.Wave_10b,
         edeq.deliberately_limit_amount_influence_.Wave_12b,
        
         #edeq.calories_made_body_shape_.Wave_1b,
         edeq.calories_made_body_shape_.Wave_2b,    
         edeq.calories_made_body_shape_.Wave_3b,       
         edeq.calories_made_body_shape_.Wave_4b,
         edeq.calories_made_body_shape_.Wave_6b,
         edeq.calories_made_body_shape_.Wave_8b,
         edeq.calories_made_body_shape_.Wave_10b,
         edeq.calories_made_body_shape_.Wave_12b,
        
         #edeq.weight_influenced_person_.Wave_1b,
         edeq.weight_influenced_person_.Wave_2b,    
         edeq.weight_influenced_person_.Wave_3b,       
         edeq.weight_influenced_person_.Wave_4b,
         edeq.weight_influenced_person_.Wave_6b,
         edeq.weight_influenced_person_.Wave_8b,
         edeq.weight_influenced_person_.Wave_10b,
         edeq.weight_influenced_person_.Wave_12b,
        
        # edeq.dissatisfied_shape_weight_.Wave_1b,
         edeq.dissatisfied_shape_weight_.Wave_2b,    
         edeq.dissatisfied_shape_weight_.Wave_3b,       
         edeq.dissatisfied_shape_weight_.Wave_4b,
         edeq.dissatisfied_shape_weight_.Wave_6b,
         edeq.dissatisfied_shape_weight_.Wave_8b,
         edeq.dissatisfied_shape_weight_.Wave_10b,
         edeq.dissatisfied_shape_weight_.Wave_12b,
         
         #edeq.actively_been_monitoring_your_shape_or_weight__.Wave_1b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b,
         edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b,
         
        # edeq.regard_lost_control_eaten_.Wave_1b,
         edeq.regard_lost_control_eaten_numeric_.Wave_2b,
         edeq.regard_lost_control_eaten_numeric_.Wave_3b,
         edeq.regard_lost_control_eaten_numeric_.Wave_4b,
         edeq.regard_lost_control_eaten_numeric_.Wave_6b,
         edeq.regard_lost_control_eaten_numeric_.Wave_8b,
         edeq.regard_lost_control_eaten_numeric_.Wave_10b,
         edeq.regard_lost_control_eaten_numeric_.Wave_12b,
         
        # edeq.sick_means_made_shape_.Wave_1b,
         edeq.sick_means_made_shape_numeric_.Wave_2b,
         edeq.sick_means_made_shape_numeric_.Wave_3b,
         edeq.sick_means_made_shape_numeric_.Wave_4b,
         edeq.sick_means_made_shape_numeric_.Wave_6b,
         edeq.sick_means_made_shape_numeric_.Wave_8b,
         edeq.sick_means_made_shape_numeric_.Wave_10b,
         edeq.sick_means_made_shape_numeric_.Wave_12b,
         
        # edeq.diuretics_laxatives_means_shape_.Wave_1b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b,
         edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b,
         
        # edeq.compulsive_driven_burn_calories_.Wave_1b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_2b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_3b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_4b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_6b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_8b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_10b,
         edeq.compulsive_driven_burn_calories_numeric_.Wave_12b,
         
       #  edeq.eating_behaviours_distressed_concerns_.Wave_1b,
         edeq.eating_behaviours_distressed_concerns_.Wave_2b,
         edeq.eating_behaviours_distressed_concerns_.Wave_3b,
         edeq.eating_behaviours_distressed_concerns_.Wave_4b,
         edeq.eating_behaviours_distressed_concerns_.Wave_6b,
         edeq.eating_behaviours_distressed_concerns_.Wave_8b,
         edeq.eating_behaviours_distressed_concerns_.Wave_10b,
         edeq.eating_behaviours_distressed_concerns_.Wave_12b,
         
        # edeq.nibbled_picked_snacks_grazed_.Wave_1b,
         edeq.nibbled_picked_snacks_grazed_.Wave_2b,
         edeq.nibbled_picked_snacks_grazed_.Wave_3b,
         edeq.nibbled_picked_snacks_grazed_.Wave_4b,
         edeq.nibbled_picked_snacks_grazed_.Wave_6b,
         edeq.nibbled_picked_snacks_grazed_.Wave_8b,
         edeq.nibbled_picked_snacks_grazed_.Wave_10b,
         edeq.nibbled_picked_snacks_grazed_.Wave_12b,
         
       #  edeq.felt_anxious_blue_bored_.Wave_1b,
         edeq.felt_anxious_blue_bored_.Wave_2b,
         edeq.felt_anxious_blue_bored_.Wave_3b,
         edeq.felt_anxious_blue_bored_.Wave_4b,
         edeq.felt_anxious_blue_bored_.Wave_6b,
         edeq.felt_anxious_blue_bored_.Wave_8b,
         edeq.felt_anxious_blue_bored_.Wave_10b,
         edeq.felt_anxious_blue_bored_.Wave_12b,
         
       #  edeq.felt_anxious_blue_bored.1_.Wave_1b,
         edeq.felt_anxious_blue_bored.1_.Wave_2b,
         edeq.felt_anxious_blue_bored.1_.Wave_3b,
         edeq.felt_anxious_blue_bored.1_.Wave_4b,
         edeq.felt_anxious_blue_bored.1_.Wave_6b,
         edeq.felt_anxious_blue_bored.1_.Wave_8b,
         edeq.felt_anxious_blue_bored.1_.Wave_10b,
         edeq.felt_anxious_blue_bored.1_.Wave_12b
         )
```

Remove duplicate IDs EDEQ COPING 
```{r Remove duplicate IDs COPING EDEQ }

# Check col names
colnames(edeq_followup_COPING.id)

# Remove dupilcate IDs (as each wave is now a column, there should be NO dup IDs)
edeq_followup_COPING.id  <- edeq_followup_COPING.id  %>%
  filter(., !duplicated(ID)) 

# Check number of rows
nrow(edeq_followup_COPING.id)

```

# Merging data
## Merge RAMP baseline with RAMP follow up
```{r merge RAMP baseline and follow up}
RAMP_merged <- merge(ramp_baseline_edeq,
  edeq_followup_RAMP.id,
  by = "ID")

RAMP_merged %>%
  colnames()
```

## Create empty columns in COPING to match those in RAMP

```{r empty columns in COPING to match RAMP}
RAMP_edeq_columns <- c(
"edeq.deliberately_limit_amount_influence_.Wave_1b",
"edeq.calories_made_body_shape_.Wave_1b",
"edeq.weight_influenced_person_.Wave_1b",
"edeq.dissatisfied_shape_weight_.Wave_1b",
"edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b",
"edeq.regard_lost_control_eaten_numeric_.Wave_1b",
"edeq.sick_means_made_shape_numeric_.Wave_1b",
"edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b",
"edeq.compulsive_driven_burn_calories_numeric_.Wave_1b",
"edeq.eating_behaviours_distressed_concerns_.Wave_1b",
"edeq.nibbled_picked_snacks_grazed_.Wave_1b",
"edeq.felt_anxious_blue_bored_.Wave_1b",
"edeq.felt_anxious_blue_bored.1_.Wave_1b",

"edeq.deliberately_limit_amount_influence_baseline", 
"edeq.eating_behaviours_concerns_distressed_baseline",
         "edeq.calories_made_body_shape_baseline",                   
         "edeq.weight_influenced_person_baseline",                       
         "edeq.dissatisfied_shape_weight_baseline",                   
         "edeq.nibbled_picked_snacks_grazed_baseline",                  
         "edeq.felt_anxious_blue_bored_baseline",                    
         "edeq.felt_anxious_blue_bored.1_baseline",   
         "edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric",
         "edeq.regard_lost_control_eaten_baseline_numeric",
         "edeq.sick_means_made_shape_baseline_numeric",
         "edeq.diuretics_laxatives_means_shape_baseline_numeric",
         "edeq.compulsive_driven_burn_calories_baseline_numeric")

edeq_followup_COPING.id[RAMP_edeq_columns] <- NA_real_
```

## Bind data using rbind
```{r rbind RAMP and COPING data}
EDEQ_dat <- edeq_followup_COPING.id %>%
  rbind(RAMP_merged)

# Check
EDEQ_dat %>%
  colnames()

EDEQ_dat %>%
  nrow()
```
# First time filling out EDEQ
```{r first time only, eval=FALSE, include=FALSE}

# On how many of the past 28 days:	Have you been deliberately trying to limit the amount of food you eat to influence your shape or weight ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.deliberate_limit_food =
           case_when(
                    edeq.deliberately_limit_amount_influence_baseline == "No days" ~ "No days",
                    edeq.deliberately_limit_amount_influence_baseline == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_baseline == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_baseline == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_baseline == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_baseline == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_baseline == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "No days" ~ "No days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "No days" ~ "No days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "Every day" ~ "Every day",
                    
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "No days" ~ "No days", 
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "1-4 days" ~ "1-4 days",
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "5-10 days" ~ "5-10 days",
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "11-16 days" ~ "11-16 days",
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "17-22 days" ~ "17-22 days",
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "23-27 days" ~ "23-27 days",
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "Every day" ~ "Every day"
           
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.deliberate_limit_food)

# On how many of the past 28 days:	Has thinking about body shape, weight, food, eating, or calories made it very difficult to concentrate on things you are interested in ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.difficulty_concentrating =
           case_when( 
                    edeq.calories_made_body_shape_baseline == "No days" ~ "No days",
                    edeq.calories_made_body_shape_baseline == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_baseline == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_baseline == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_baseline == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_baseline == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_baseline == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_1b == "No days" ~ "No days",
                    edeq.calories_made_body_shape_.Wave_1b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_1b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_1b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_1b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_1b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_1b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_2b == "No days" ~ "No days",
                    edeq.calories_made_body_shape_.Wave_2b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_2b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_2b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_2b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_2b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_2b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_3b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_3b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_3b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_3b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_3b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_3b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_3b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_4b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_4b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_4b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_4b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_4b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_4b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_4b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_6b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_6b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_6b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_6b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_6b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_6b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_6b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_8b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_8b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_8b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_8b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_8b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_8b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_8b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_10b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_10b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_10b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_10b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_10b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_10b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_10b == "Every day" ~ "Every day",
                    
                    edeq.calories_made_body_shape_.Wave_12b == "No days" ~ "No days", 
                    edeq.calories_made_body_shape_.Wave_12b == "1-4 days" ~ "1-4 days",
                    edeq.calories_made_body_shape_.Wave_12b == "5-10 days" ~ "5-10 days",
                    edeq.calories_made_body_shape_.Wave_12b == "11-16 days" ~ "11-16 days",
                    edeq.calories_made_body_shape_.Wave_12b == "17-22 days" ~ "17-22 days",
                    edeq.calories_made_body_shape_.Wave_12b == "23-27 days" ~ "23-27 days",
                    edeq.calories_made_body_shape_.Wave_12b == "Every day" ~ "Every day"
           
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.difficulty_concentrating)

# Over the past 28 days:	Has your weight influenced how you think about yourself as a person?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.weight_influenced_think_person =
           case_when(
                    edeq.weight_influenced_person_baseline == "0" ~ "0",
                    edeq.weight_influenced_person_baseline == "1" ~ "1",
                    edeq.weight_influenced_person_baseline == "2" ~ "2",
                    edeq.weight_influenced_person_baseline == "3" ~ "3",
                    edeq.weight_influenced_person_baseline == "4" ~ "4",
                    edeq.weight_influenced_person_baseline == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_1b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_1b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_1b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_1b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_1b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_1b == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_2b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_2b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_2b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_2b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_2b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_2b == "5" ~ "5",

                    edeq.weight_influenced_person_.Wave_3b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_3b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_3b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_3b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_3b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_3b == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_4b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_4b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_4b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_4b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_4b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_4b == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_6b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_6b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_6b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_6b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_6b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_6b == "5" ~ "5",
                  
                    edeq.weight_influenced_person_.Wave_8b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_8b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_8b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_8b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_8b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_8b == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_10b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_10b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_10b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_10b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_10b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_10b == "5" ~ "5",
                    
                    edeq.weight_influenced_person_.Wave_12b == "0" ~ "0",
                    edeq.weight_influenced_person_.Wave_12b == "1" ~ "1",
                    edeq.weight_influenced_person_.Wave_12b == "2" ~ "2",
                    edeq.weight_influenced_person_.Wave_12b == "3" ~ "3",
                    edeq.weight_influenced_person_.Wave_12b == "4" ~ "4",
                    edeq.weight_influenced_person_.Wave_12b == "5" ~ "5"
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.weight_influenced_think_person)

# Over the past 28 days:	How dissatisfied have you been with your weight or shape?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.dissatisfied_weight_shape =
           case_when(
                    edeq.dissatisfied_shape_weight_baseline == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_baseline == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_baseline == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_baseline == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_baseline == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_baseline == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_1b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_1b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_1b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_1b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_1b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_1b == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_2b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_2b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_2b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_2b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_2b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_2b == "5" ~ "5",

                    edeq.dissatisfied_shape_weight_.Wave_3b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_3b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_3b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_3b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_3b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_3b == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_4b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_4b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_4b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_4b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_4b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_4b == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_6b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_6b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_6b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_6b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_6b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_6b == "5" ~ "5",
                  
                    edeq.dissatisfied_shape_weight_.Wave_8b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_8b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_8b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_8b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_8b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_8b == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_10b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_10b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_10b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_10b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_10b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_10b == "5" ~ "5",
                    
                    edeq.dissatisfied_shape_weight_.Wave_12b == "0" ~ "0",
                    edeq.dissatisfied_shape_weight_.Wave_12b == "1" ~ "1",
                    edeq.dissatisfied_shape_weight_.Wave_12b == "2" ~ "2",
                    edeq.dissatisfied_shape_weight_.Wave_12b == "3" ~ "3",
                    edeq.dissatisfied_shape_weight_.Wave_12b == "4" ~ "4",
                    edeq.dissatisfied_shape_weight_.Wave_12b == "5" ~ "5"
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.dissatisfied_weight_shape)

# Over the past 28 days, how many times per day have you:	Actively been monitoring your shape or weight ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.actively_monitoring_shape_weight =
           case_when(
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric)  ~ edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.actively_monitoring_shape_weight)


# Over the past 28 days, how many times per day have you:	Eaten what other people would regard as an unusually large amount of food with a sense of having lost control over your eating?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.binge_eating =
           case_when(
                    !is.na(edeq.regard_lost_control_eaten_baseline_numeric)  ~ edeq.regard_lost_control_eaten_baseline_numeric,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_1b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_1b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_2b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_2b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_3b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_3b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_4b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_4b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_6b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_6b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_8b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_8b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_10b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_10b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_12b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.binge_eating)

# Over the past 28 days, how many times per day have you:	Made yourself sick as a means of controlling your shape or weight?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.self_induced_vomiting =
           case_when(
                    !is.na(edeq.sick_means_made_shape_baseline_numeric)  ~ edeq.sick_means_made_shape_baseline_numeric,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_1b)  ~ edeq.sick_means_made_shape_numeric_.Wave_1b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_2b)  ~ edeq.sick_means_made_shape_numeric_.Wave_2b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_3b)  ~ edeq.sick_means_made_shape_numeric_.Wave_3b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_4b)  ~ edeq.sick_means_made_shape_numeric_.Wave_4b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_6b)  ~ edeq.sick_means_made_shape_numeric_.Wave_6b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_8b)  ~ edeq.sick_means_made_shape_numeric_.Wave_8b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_10b)  ~ edeq.sick_means_made_shape_numeric_.Wave_10b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_12b)  ~ edeq.sick_means_made_shape_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.self_induced_vomiting)

# Over the past 28 days, how many times per day have you:	Taken laxatives, diuretics, or diet pills as a means of controlling your shape or weight?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.laxatives_diuretics_diet_pills =
           case_when(
                    !is.na(edeq.diuretics_laxatives_means_shape_baseline_numeric)  ~ edeq.diuretics_laxatives_means_shape_baseline_numeric,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.laxatives_diuretics_diet_pills)

# Over the past 28 days, how many times per day have you:	Exercised in a driven or compulsive way as a means of controlling your weight, shape, or amount of fat, or to burn off calories?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.excessive_exercise =
           case_when(
                    !is.na(edeq.compulsive_driven_burn_calories_baseline_numeric)  ~ edeq.compulsive_driven_burn_calories_baseline_numeric,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_1b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_1b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_2b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_2b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_3b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_3b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_4b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_4b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_6b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_6b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_8b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_8b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_10b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_10b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_12b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.excessive_exercise)

# Over the past 28 days:	How distressed have you been by your eating behaviours, the measures you've taken to control your weight, or concerns about your weight and shape?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.distressed_by_behaviours =
           case_when(
                    edeq.eating_behaviours_concerns_distressed_baseline == "0" ~ "0",
                    edeq.eating_behaviours_concerns_distressed_baseline == "1" ~ "1",
                    edeq.eating_behaviours_concerns_distressed_baseline == "2" ~ "2",
                    edeq.eating_behaviours_concerns_distressed_baseline == "3" ~ "3",
                    edeq.eating_behaviours_concerns_distressed_baseline == "4" ~ "4",
                    edeq.eating_behaviours_concerns_distressed_baseline == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "5" ~ "5",

                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "5" ~ "5",
                  
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "5" ~ "5",
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "0" ~ "0",
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "1" ~ "1",
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "2" ~ "2",
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "3" ~ "3",
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "4" ~ "4",
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "5" ~ "5"
         )
  )
 
 
# Check
EDEQ_dat %>%
  freq(edeq.distressed_by_behaviours)

# Over the past 28 days, on how many days have you:	Picked at, nibbled, or grazed food repeatedly outside of planned meals and snacks?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.repeated_grazing =
           case_when( 
                    edeq.nibbled_picked_snacks_grazed_baseline == "No days" ~ "No days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_baseline == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "No days" ~ "No days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "No days" ~ "No days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "Every day" ~ "Every day",
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "No days" ~ "No days", 
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "1-4 days" ~ "1-4 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "5-10 days" ~ "5-10 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "11-16 days" ~ "11-16 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "17-22 days" ~ "17-22 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "23-27 days" ~ "23-27 days",
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "Every day" ~ "Every day"
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.repeated_grazing)

# Over the past 28 days, on how many days have you:	Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.eaten_more_emotional =
           case_when( 
                    edeq.felt_anxious_blue_bored_baseline == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored_baseline == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_baseline == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_baseline == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_baseline == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_baseline == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_baseline == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_1b == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_1b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_2b == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_2b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_3b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_3b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_3b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_3b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_3b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_3b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_3b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_4b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_4b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_4b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_4b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_4b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_4b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_4b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_6b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_6b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_6b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_6b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_6b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_6b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_6b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_8b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_8b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_8b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_8b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_8b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_8b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_8b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_10b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_10b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_10b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_10b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_10b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_10b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_10b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored_.Wave_12b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored_.Wave_12b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored_.Wave_12b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored_.Wave_12b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored_.Wave_12b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored_.Wave_12b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored_.Wave_12b == "Every day" ~ "Every day"
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.eaten_more_emotional)

# Over the past 28 days, on how many days have you:	Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.eaten_less_emotional =
           case_when( 
                    edeq.felt_anxious_blue_bored.1_baseline == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored.1_baseline == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_baseline == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_baseline == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_baseline == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_baseline == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_baseline == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "No days" ~ "No days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "Every day" ~ "Every day",
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "No days" ~ "No days", 
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "1-4 days" ~ "1-4 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "5-10 days" ~ "5-10 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "11-16 days" ~ "11-16 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "17-22 days" ~ "17-22 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "23-27 days" ~ "23-27 days",
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "Every day" ~ "Every day"
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.eaten_less_emotional)
```


# FOR STATA: First time filling out EDEQ
```{r first time only}

# On how many of the past 28 days:	Have you been deliberately trying to limit the amount of food you eat to influence your shape or weight ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.deliberate_limit_food =
           case_when(
                    edeq.deliberately_limit_amount_influence_baseline == "No days" ~     1,
                    edeq.deliberately_limit_amount_influence_baseline == "1-4 days" ~    2,
                    edeq.deliberately_limit_amount_influence_baseline == "5-10 days" ~   3,
                    edeq.deliberately_limit_amount_influence_baseline == "11-16 days" ~  4,
                    edeq.deliberately_limit_amount_influence_baseline == "17-22 days" ~  5,
                    edeq.deliberately_limit_amount_influence_baseline == "23-27 days" ~  6,
                    edeq.deliberately_limit_amount_influence_baseline == "Every day" ~   7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "No days" ~ 1,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_1b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "No days" ~ 1,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_2b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_3b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_4b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_6b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_8b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_10b == "Every day" ~ 7,
                    
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "No days" ~ 1, 
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "1-4 days" ~ 2,
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "5-10 days" ~ 3,
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "11-16 days" ~ 4,
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "17-22 days" ~ 5,
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "23-27 days" ~ 6,
                    edeq.deliberately_limit_amount_influence_.Wave_12b == "Every day" ~ 7
           
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.deliberate_limit_food)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.deliberate_limit_food_binary = 
           case_when(
             is.na(edeq.deliberate_limit_food) ~ NA_real_,
             edeq.deliberate_limit_food == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.deliberate_limit_food_binary)


# On how many of the past 28 days:	Has thinking about body shape, weight, food, eating, or calories made it very difficult to concentrate on things you are interested in ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.difficulty_concentrating =
           case_when( 
                    edeq.calories_made_body_shape_baseline == "No days" ~ 1,
                    edeq.calories_made_body_shape_baseline == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_baseline == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_baseline == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_baseline == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_baseline == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_baseline == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_1b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_1b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_1b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_1b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_1b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_1b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_1b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_2b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_2b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_2b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_2b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_2b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_2b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_2b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_3b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_3b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_3b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_3b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_3b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_3b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_3b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_4b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_4b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_4b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_4b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_4b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_4b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_4b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_6b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_6b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_6b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_6b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_6b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_6b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_6b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_8b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_8b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_8b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_8b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_8b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_8b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_8b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_10b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_10b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_10b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_10b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_10b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_10b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_10b == "Every day" ~ 7,
                    
                    edeq.calories_made_body_shape_.Wave_12b == "No days" ~ 1,
                    edeq.calories_made_body_shape_.Wave_12b == "1-4 days" ~ 2,
                    edeq.calories_made_body_shape_.Wave_12b == "5-10 days" ~ 3,
                    edeq.calories_made_body_shape_.Wave_12b == "11-16 days" ~ 4,
                    edeq.calories_made_body_shape_.Wave_12b == "17-22 days" ~ 5,
                    edeq.calories_made_body_shape_.Wave_12b == "23-27 days" ~ 6,
                    edeq.calories_made_body_shape_.Wave_12b == "Every day" ~ 7
           
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.difficulty_concentrating)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.difficulty_concentrating_binary = 
           case_when(
             is.na(edeq.difficulty_concentrating) ~ NA_real_,
             edeq.difficulty_concentrating == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.difficulty_concentrating_binary)

# Over the past 28 days:	Has your weight influenced how you think about yourself as a person?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.weight_influenced_think_person =
           case_when(
                    edeq.weight_influenced_person_baseline == "0" ~ 0,
                    edeq.weight_influenced_person_baseline == "1" ~ 1,
                    edeq.weight_influenced_person_baseline == "2" ~ 2,
                    edeq.weight_influenced_person_baseline == "3" ~ 3,
                    edeq.weight_influenced_person_baseline == "4" ~ 4,
                    edeq.weight_influenced_person_baseline == "5" ~ 5,
                    
                    edeq.weight_influenced_person_.Wave_1b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_1b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_1b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_1b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_1b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_1b == "5" ~ 5,
                
                    edeq.weight_influenced_person_.Wave_2b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_2b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_2b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_2b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_2b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_2b == "5" ~ 5,
                    edeq.weight_influenced_person_.Wave_3b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_3b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_3b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_3b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_3b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_3b == "5" ~ 5,
                
                    edeq.weight_influenced_person_.Wave_4b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_4b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_4b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_4b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_4b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_4b == "5" ~ 5,
                
                    edeq.weight_influenced_person_.Wave_6b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_6b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_6b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_6b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_6b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_6b == "5" ~ 5,
              
                    edeq.weight_influenced_person_.Wave_8b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_8b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_8b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_8b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_8b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_8b == "5" ~ 5,
                  
                    edeq.weight_influenced_person_.Wave_10b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_10b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_10b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_10b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_10b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_10b == "5" ~ 5,
                
                    edeq.weight_influenced_person_.Wave_12b == "0" ~ 0,
                    edeq.weight_influenced_person_.Wave_12b == "1" ~ 1,
                    edeq.weight_influenced_person_.Wave_12b == "2" ~ 2,
                    edeq.weight_influenced_person_.Wave_12b == "3" ~ 3,
                    edeq.weight_influenced_person_.Wave_12b == "4" ~ 4,
                    edeq.weight_influenced_person_.Wave_12b == "5" ~ 5
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.weight_influenced_think_person)

# Over the past 28 days:	How dissatisfied have you been with your weight or shape?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.dissatisfied_weight_shape =
           case_when(
                    edeq.dissatisfied_shape_weight_baseline == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_baseline == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_baseline == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_baseline == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_baseline == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_baseline == "5" ~ 5,
                
                    edeq.dissatisfied_shape_weight_.Wave_1b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_1b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_1b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_1b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_1b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_1b == "5" ~ 5,
                
                    edeq.dissatisfied_shape_weight_.Wave_2b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_2b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_2b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_2b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_2b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_2b == "5" ~ 5,
                    
                    edeq.dissatisfied_shape_weight_.Wave_3b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_3b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_3b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_3b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_3b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_3b == "5" ~ 5,
                
                    edeq.dissatisfied_shape_weight_.Wave_4b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_4b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_4b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_4b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_4b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_4b == "5" ~ 5,
                
                    edeq.dissatisfied_shape_weight_.Wave_6b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_6b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_6b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_6b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_6b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_6b == "5" ~ 5,
              
                    edeq.dissatisfied_shape_weight_.Wave_8b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_8b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_8b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_8b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_8b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_8b == "5" ~ 5,
                    
                    edeq.dissatisfied_shape_weight_.Wave_10b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_10b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_10b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_10b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_10b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_10b == "5" ~ 5,
                
                    edeq.dissatisfied_shape_weight_.Wave_12b == "0" ~ 0,
                    edeq.dissatisfied_shape_weight_.Wave_12b == "1" ~ 1,
                    edeq.dissatisfied_shape_weight_.Wave_12b == "2" ~ 2,
                    edeq.dissatisfied_shape_weight_.Wave_12b == "3" ~ 3,
                    edeq.dissatisfied_shape_weight_.Wave_12b == "4" ~ 4,
                    edeq.dissatisfied_shape_weight_.Wave_12b == "5" ~ 5
         )
  )
 
# Check
EDEQ_dat %>%
  freq(edeq.dissatisfied_weight_shape)

# Over the past 28 days, how many times per day have you:	Actively been monitoring your shape or weight ?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.actively_monitoring_shape_weight_cont =
           case_when(
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric)  ~ edeq.actively_been_monitoring_your_shape_or_weight__baseline_numeric,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_1b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_2b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_3b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_4b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_6b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_8b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_10b,
                    !is.na(edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b)  ~ edeq.actively_been_monitoring_your_shape_or_weight__numeric_.Wave_12b
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.actively_monitoring_shape_weight_cont)

EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.actively_monitoring_shape_weight =
           case_when(
                    edeq.actively_monitoring_shape_weight_cont == 0 ~ 1,
                    edeq.actively_monitoring_shape_weight_cont >= 1 &
                      edeq.actively_monitoring_shape_weight_cont <= 4 ~ 2,
                    edeq.actively_monitoring_shape_weight_cont >= 5 &
                      edeq.actively_monitoring_shape_weight_cont <= 10 ~ 3,
                    edeq.actively_monitoring_shape_weight_cont >= 11 &
                      edeq.actively_monitoring_shape_weight_cont <= 16 ~ 4,
                    edeq.actively_monitoring_shape_weight_cont >= 17 &
                      edeq.actively_monitoring_shape_weight_cont <= 22 ~ 5,
                    edeq.actively_monitoring_shape_weight_cont >= 23 &
                      edeq.actively_monitoring_shape_weight_cont <= 27 ~ 6,
                    edeq.actively_monitoring_shape_weight_cont >= 28 ~ 7,
                    
                    
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.actively_monitoring_shape_weight)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.actively_monitoring_shape_weight_binary = 
           case_when(
             is.na(edeq.actively_monitoring_shape_weight) ~ NA_real_,
             edeq.actively_monitoring_shape_weight == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.actively_monitoring_shape_weight_binary)


# Over the past 28 days, how many times per day have you:	Eaten what other people would regard as an unusually large amount of food with a sense of having lost control over your eating?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.binge_eating_cont =
           case_when(
                    !is.na(edeq.regard_lost_control_eaten_baseline_numeric)  ~ edeq.regard_lost_control_eaten_baseline_numeric,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_1b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_1b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_2b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_2b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_3b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_3b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_4b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_4b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_6b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_6b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_8b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_8b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_10b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_10b,
                    !is.na(edeq.regard_lost_control_eaten_numeric_.Wave_12b)  ~ edeq.regard_lost_control_eaten_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.binge_eating_cont)

EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.binge_eating =
           case_when(
                    edeq.binge_eating_cont == 0 ~ 1,
                    edeq.binge_eating_cont >= 1 &
                      edeq.binge_eating_cont <= 4 ~ 2,
                    edeq.binge_eating_cont >= 5 &
                      edeq.binge_eating_cont <= 10 ~ 3,
                    edeq.binge_eating_cont >= 11 &
                      edeq.binge_eating_cont <= 16 ~ 4,
                    edeq.binge_eating_cont >= 17 &
                      edeq.binge_eating_cont <= 22 ~ 5,
                    edeq.binge_eating_cont >= 23 &
                      edeq.binge_eating_cont <= 27 ~ 6,
                    edeq.binge_eating_cont >= 28 ~ 7,
                    
                    
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.binge_eating)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.binge_eating_binary = 
           case_when(
             is.na(edeq.binge_eating) ~ NA_real_,
             edeq.binge_eating == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.binge_eating_binary)

# Over the past 28 days, how many times per day have you:	Made yourself sick as a means of controlling your shape or weight?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.self_induced_vomiting_cont =
           case_when(
                    !is.na(edeq.sick_means_made_shape_baseline_numeric)  ~ edeq.sick_means_made_shape_baseline_numeric,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_1b)  ~ edeq.sick_means_made_shape_numeric_.Wave_1b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_2b)  ~ edeq.sick_means_made_shape_numeric_.Wave_2b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_3b)  ~ edeq.sick_means_made_shape_numeric_.Wave_3b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_4b)  ~ edeq.sick_means_made_shape_numeric_.Wave_4b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_6b)  ~ edeq.sick_means_made_shape_numeric_.Wave_6b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_8b)  ~ edeq.sick_means_made_shape_numeric_.Wave_8b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_10b)  ~ edeq.sick_means_made_shape_numeric_.Wave_10b,
                    !is.na(edeq.sick_means_made_shape_numeric_.Wave_12b)  ~ edeq.sick_means_made_shape_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.self_induced_vomiting_cont)

EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.self_induced_vomiting =
           case_when(
                    edeq.self_induced_vomiting_cont == 0 ~ 1,
                    edeq.self_induced_vomiting_cont >= 1 &
                      edeq.self_induced_vomiting_cont <= 4 ~ 2,
                    edeq.self_induced_vomiting_cont >= 5 &
                      edeq.self_induced_vomiting_cont <= 10 ~ 3,
                    edeq.self_induced_vomiting_cont >= 11 &
                      edeq.self_induced_vomiting_cont <= 16 ~ 4,
                    edeq.self_induced_vomiting_cont >= 17 &
                      edeq.self_induced_vomiting_cont <= 22 ~ 5,
                    edeq.self_induced_vomiting_cont >= 23 &
                      edeq.self_induced_vomiting_cont <= 27 ~ 6,
                    edeq.self_induced_vomiting_cont >= 28 ~ 7,
                    
                    
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.self_induced_vomiting)


# Over the past 28 days, how many times per day have you:	Taken laxatives, diuretics, or diet pills as a means of controlling your shape or weight?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.laxatives_diuretics_diet_pills_cont =
           case_when(
                    !is.na(edeq.diuretics_laxatives_means_shape_baseline_numeric)  ~ edeq.diuretics_laxatives_means_shape_baseline_numeric,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_1b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_2b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_3b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_4b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_6b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_8b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_10b,
                    !is.na(edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b)  ~ edeq.diuretics_laxatives_means_shape_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.laxatives_diuretics_diet_pills_cont)

EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.laxatives_diuretics_diet_pills =
           case_when(
                    edeq.laxatives_diuretics_diet_pills_cont == 0 ~ 1,
                    edeq.laxatives_diuretics_diet_pills_cont >= 1 &
                      edeq.laxatives_diuretics_diet_pills_cont <= 4 ~ 2,
                    edeq.laxatives_diuretics_diet_pills_cont >= 5 &
                      edeq.laxatives_diuretics_diet_pills_cont <= 10 ~ 3,
                    edeq.laxatives_diuretics_diet_pills_cont >= 11 &
                      edeq.laxatives_diuretics_diet_pills_cont <= 16 ~ 4,
                    edeq.laxatives_diuretics_diet_pills_cont >= 17 &
                      edeq.laxatives_diuretics_diet_pills_cont <= 22 ~ 5,
                    edeq.laxatives_diuretics_diet_pills_cont >= 23 &
                      edeq.laxatives_diuretics_diet_pills_cont <= 27 ~ 6,
                    edeq.laxatives_diuretics_diet_pills_cont >= 28 ~ 7,
                    
                    
                    )
         )

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.laxatives_diuretics_diet_pills_binary = 
           case_when(
             is.na(edeq.laxatives_diuretics_diet_pills) ~ NA_real_,
             edeq.laxatives_diuretics_diet_pills == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.laxatives_diuretics_diet_pills_binary)
 
# Check
EDEQ_dat %>%
  freq(edeq.laxatives_diuretics_diet_pills)

# Over the past 28 days, how many times per day have you:	Exercised in a driven or compulsive way as a means of controlling your weight, shape, or amount of fat, or to burn off calories?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.excessive_exercise_cont =
           case_when(
                    !is.na(edeq.compulsive_driven_burn_calories_baseline_numeric)  ~ edeq.compulsive_driven_burn_calories_baseline_numeric,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_1b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_1b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_2b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_2b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_3b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_3b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_4b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_4b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_6b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_6b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_8b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_8b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_10b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_10b,
                    !is.na(edeq.compulsive_driven_burn_calories_numeric_.Wave_12b)  ~ edeq.compulsive_driven_burn_calories_numeric_.Wave_12b
                    )
         )

 
# Check
EDEQ_dat %>%
  freq(edeq.excessive_exercise_cont)


EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.excessive_exercise =
           case_when(
                    edeq.excessive_exercise_cont == 0 ~ 1,
                    edeq.excessive_exercise_cont >= 1 &
                      edeq.excessive_exercise_cont <= 4 ~ 2,
                    edeq.excessive_exercise_cont >= 5 &
                      edeq.excessive_exercise_cont <= 10 ~ 3,
                    edeq.excessive_exercise_cont >= 11 &
                      edeq.excessive_exercise_cont <= 16 ~ 4,
                    edeq.excessive_exercise_cont >= 17 &
                      edeq.excessive_exercise_cont <= 22 ~ 5,
                    edeq.excessive_exercise_cont >= 23 &
                      edeq.excessive_exercise_cont <= 27 ~ 6,
                    edeq.excessive_exercise_cont >= 28 ~ 7,
                    )
         )
 
# Check
EDEQ_dat %>%
  freq(edeq.excessive_exercise)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.excessive_exercise_binary = 
           case_when(
             is.na(edeq.excessive_exercise) ~ NA_real_,
             edeq.excessive_exercise == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.excessive_exercise_binary)

# Over the past 28 days:	How distressed have you been by your eating behaviours, the measures you've taken to control your weight, or concerns about your weight and shape?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.distressed_by_behaviours =
           case_when(
                    edeq.eating_behaviours_concerns_distressed_baseline == "0" ~ 0,
                    edeq.eating_behaviours_concerns_distressed_baseline == "1" ~ 1,
                    edeq.eating_behaviours_concerns_distressed_baseline == "2" ~ 2,
                    edeq.eating_behaviours_concerns_distressed_baseline == "3" ~ 3,
                    edeq.eating_behaviours_concerns_distressed_baseline == "4" ~ 4,
                    edeq.eating_behaviours_concerns_distressed_baseline == "5" ~ 5,
                
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_1b == "5" ~ 5,
                
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_2b == "5" ~ 5,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_3b == "5" ~ 5,
                
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_4b == "5" ~ 5,
                
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_6b == "5" ~ 5,
              
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_8b == "5" ~ 5,
                    
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_10b == "5" ~ 5,
                
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "0" ~ 0,
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "1" ~ 1,
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "2" ~ 2,
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "3" ~ 3,
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "4" ~ 4,
                    edeq.eating_behaviours_distressed_concerns_.Wave_12b == "5" ~ 5
         )
  )
 
 
# Check
EDEQ_dat %>%
  freq(edeq.distressed_by_behaviours)

# Over the past 28 days, on how many days have you:	Picked at, nibbled, or grazed food repeatedly outside of planned meals and snacks?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.repeated_grazing =
           case_when( 
                    edeq.nibbled_picked_snacks_grazed_baseline == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_baseline == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_baseline == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_baseline == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_baseline == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_baseline == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_baseline == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_1b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_2b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_3b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_4b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_6b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_8b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_10b == "Every day" ~ 7,
                    
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "No days" ~ 1,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "1-4 days" ~ 2,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "5-10 days" ~ 3,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "11-16 days" ~ 4,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "17-22 days" ~ 5,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "23-27 days" ~ 6,
                    edeq.nibbled_picked_snacks_grazed_.Wave_12b == "Every day" ~ 7
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.repeated_grazing)

# Over the past 28 days, on how many days have you:	Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.eaten_more_emotional =
           case_when( 
                    edeq.felt_anxious_blue_bored_baseline == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_baseline == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_baseline == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_baseline == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_baseline == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_baseline == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_baseline == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_1b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_1b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_2b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_2b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_3b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_3b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_4b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_4b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_6b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_6b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_8b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_8b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_10b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_10b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored_.Wave_12b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored_.Wave_12b == "Every day" ~ 7
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.eaten_more_emotional)

# Over the past 28 days, on how many days have you:	Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.eaten_less_emotional =
           case_when( 
                    edeq.felt_anxious_blue_bored.1_baseline == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_baseline == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_baseline == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_baseline == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_baseline == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_baseline == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_baseline == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_1b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_2b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_3b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_4b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_6b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_8b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_10b == "Every day" ~ 7,
                    
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "No days" ~ 1,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "1-4 days" ~ 2,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "5-10 days" ~ 3,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "11-16 days" ~ 4,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "17-22 days" ~ 5,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "23-27 days" ~ 6,
                    edeq.felt_anxious_blue_bored.1_.Wave_12b == "Every day" ~ 7
           
         )
  )

 
# Check
EDEQ_dat %>%
  freq(edeq.eaten_less_emotional)

# Change to binary
EDEQ_dat <- EDEQ_dat %>%
  mutate(edeq.eaten_less_emotional_binary = 
           case_when(
             is.na(edeq.eaten_less_emotional) ~ NA_real_,
             edeq.eaten_less_emotional == 1 ~ 0, # No days
             TRUE ~ 1 # At least one day
           ))

EDEQ_dat %>%
  freq(edeq.eaten_less_emotional_binary)
```


# Only want people with NEW experiences of BE or LW
```{r NEW experience of LW or BE}
NEW_exp <- readRDS(file = "../data_cleaned/test_dat2021-08-16.rds")

# Check
dim(NEW_exp)
colnames(NEW_exp)
```

```{r extract needed columns}
# Extract only needed columns
NEW_exp <- NEW_exp %>%
  select(ID,
         cohort_name,
         NEW_binge_eating_pandemic,
         NEW_low_weight_pandemic)
```

```{r merge with other data}
dat <- merge(EDEQ_dat,
             NEW_exp,
             by = "ID")


# Check
dat %>%
  colnames()

dat %>%
  nrow()
```
# Select only those with new experiences
```{r select only those with new experiences}
dat_only_new_exp <- dat %>%
  filter(NEW_binge_eating_pandemic == 1 |
           NEW_low_weight_pandemic == 1)

# Check
dat_only_new_exp %>%
  nrow()
```

# Save dataset ready for analysis
## Select variables
```{r select variables}
EDEQ_dat_final <- dat_only_new_exp %>%
  select(ID,
         cohort_name,
         edeq.deliberate_limit_food_binary,
         edeq.difficulty_concentrating_binary,
         edeq.weight_influenced_think_person,
         edeq.dissatisfied_weight_shape,
         edeq.actively_monitoring_shape_weight_binary,
         edeq.binge_eating_binary,
         edeq.self_induced_vomiting,
         edeq.laxatives_diuretics_diet_pills_binary,
         edeq.excessive_exercise_binary,
         edeq.distressed_by_behaviours,
         edeq.repeated_grazing,
         edeq.eaten_more_emotional,
         edeq.eaten_less_emotional_binary
         )
```

# Change -77 to NA
```{r -77 to NA}
EDEQ_dat_final_NA <- EDEQ_dat_final %>%
  mutate_if(is.numeric, ~na_if(., -77)) 
```

# Clean numeric variables
```{r eval=FALSE, include=FALSE}
# Monitoring weight and shape
EDEQ_dat_final_NA <- EDEQ_dat_final_NA %>%
  filter(edeq.actively_monitoring_shape_weight >= 0 &
           edeq.actively_monitoring_shape_weight <= 28)

# Check
EDEQ_dat_final_NA %>%
  freq(edeq.dissatisfied_weight_shape)

# Binge eating
EDEQ_dat_final_NA <- EDEQ_dat_final_NA %>%
  filter(edeq.binge_eating >= 0 &
           edeq.binge_eating <= 28)

# Check
EDEQ_dat_final_NA %>%
  freq(edeq.binge_eating)

# Self-induced vomiting
EDEQ_dat_final_NA <- EDEQ_dat_final_NA %>%
  filter(edeq.self_induced_vomiting >= 0 &
           edeq.self_induced_vomiting <= 28)

# Check
EDEQ_dat_final_NA %>%
  freq(edeq.self_induced_vomiting)

# Laxative diuretics diet piet pills
EDEQ_dat_final_NA <- EDEQ_dat_final_NA %>%
  filter(edeq.laxatives_diuretics_diet_pills >= 0 &
           edeq.laxatives_diuretics_diet_pills <= 28)

# Check
EDEQ_dat_final_NA %>%
  freq(edeq.laxatives_diuretics_diet_pills)

# Excessive exercise
EDEQ_dat_final_NA <- EDEQ_dat_final_NA %>%
  filter(edeq.excessive_exercise >= 0 &
           edeq.excessive_exercise <= 28)

# Check
EDEQ_dat_final_NA %>%
  freq(edeq.excessive_exercise)
```

```{r distributions of variables}


hist(EDEQ_dat_final_NA$edeq.eaten_more_emotional) 
hist(EDEQ_dat_final_NA$edeq.repeated_grazing) 


hist(EDEQ_dat_final_NA$edeq.distressed_by_behaviours) 
hist(EDEQ_dat_final_NA$edeq.dissatisfied_weight_shape) 

#Binary
hist(EDEQ_dat_final_NA$edeq.deliberate_limit_food_binary) 
hist(EDEQ_dat_final_NA$edeq.eaten_less_emotional_binary)
hist(EDEQ_dat_final_NA$edeq.difficulty_concentrating_binary)
hist(EDEQ_dat_final_NA$edeq.actively_monitoring_shape_weight_binary)
hist(EDEQ_dat_final_NA$edeq.binge_eating_binary)
hist(EDEQ_dat_final_NA$edeq.laxatives_diuretics_diet_pills_binary)
hist(EDEQ_dat_final_NA$edeq.excessive_exercise_binary)

freq(EDEQ_dat_final_NA$edeq.deliberate_limit_food) 
freq(EDEQ_dat_final_NA$edeq.difficulty_concentrating)
freq(EDEQ_dat_final_NA$edeq.dissatisfied_weight_shape) 
freq(EDEQ_dat_final_NA$edeq.eaten_less_emotional)
freq(EDEQ_dat_final_NA$edeq.eaten_more_emotional) 
freq(EDEQ_dat_final_NA$edeq.distressed_by_behaviours) 
freq(EDEQ_dat_final_NA$edeq.repeated_grazing) 
freq(EDEQ_dat_final_NA$edeq.excessive_exercise)
freq(EDEQ_dat_final_NA$edeq.actively_monitoring_shape_weight)
freq(EDEQ_dat_final_NA$edeq.binge_eating)
freq(EDEQ_dat_final_NA$edeq.laxatives_diuretics_diet_pills)
```



```{r save dataset}
# Save as excel spreadsheet ready for stata
#install.packages("openxlsx")
openxlsx::write.xlsx(EDEQ_dat_final_NA,
                     'EDEQ_dat_final_25_08_2021.xlsx')

# Also save as rds file
saveRDS(object = EDEQ_dat_final_NA, file = paste0("/Users/helenadavies/werk/EDBEHSELFHARM2/gitEDBEHSELFHARM/data_cleaned/EDEQ_dat_final_NA", date, ".rds"))
```



# Latent class analysis
The basis of latent class analysis is that each subject is assumed to belong to one of a finite number of classes, with each class described by a set of parameters that define the distribution of outcomes or manifest variables for a subject, and is a form of finite mixture model (McLachlan and Peel 2000). Generally, the number of classes is unknown and must be determined from the data.

When used as a classification algorithm the model does not simply return the most likely class for each subject but returns a probability of class membership, based on the observed outcomes. The posterior probability for a set of given observed outcomes can be obtained from Bayes theorem.

The assumption of latent class models is conditional or local independence, where the outcomes are independent conditional on the latent class. This assumes that subjects within a class are homogeneous. Where this does not apply, that is the true classes are heterogeneous, a consequence of this will be to increase the number of latent classes required in attempting to explain the heterogeneity, with possible consequent difficulty in interpretation. A solution is to incorporate random effects so that the outcomes are independent conditional on the latent class and random effect or effects.

The advantage of randomLCA over the other packages is that it will fit both standard latent class models and those incorporating random effects.

https://maksimrudnev.com/2016/12/28/latent-class-analysis-in-r/
CRAN offers plenty of different ways to get clusters on your data, but most of these packages have a very narrow and specific utility. For example, I found at least 15 packages involving latent class models, of which only six perform latent class analysis in the form of classification based on indicators, and only two of them allow including nominal indicators, and none allows including ordinal indicators.



















