---
title: "Untitled"
author: "Helena Davies"
date: "12/05/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "broom",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-05-11.rds")
dim(dat)
   colnames(dat)
```

# Mental health diagnosis
```{r read in mental health diagnosis cleaned data}
# EDGI
edgi_mhd_dat_id <- readRDS(file = paste0(filepath_cleaned_latest_freeze, "edgi/clinical/mhd_edgi_clean.rds"))

edgi_mhd_dat_id <- edgi_mhd_dat_id %>%
  select(ID,
         sample,
         mhd.personality_disorder_diagnosed_numeric)

# GLAD
mhd_dat_glad <- readRDS(file = paste0(filepath_cleaned_latest_freeze, "glad/clinical/mhd_glad_clean.rds"))

mhd_dat_glad <- mhd_dat_glad %>%
  select(ID,
         sample,
         mhd.personality_disorder_diagnosed_numeric)

## GLAD COPING 
mhd_dat_glad_coping  <- readRDS(file = paste0(filepath_cleaned_latest_freeze, "coping_glad/clinical/mhd_coping_glad_clean.rds"))

mhd_dat_glad_coping <- mhd_dat_glad_coping %>%
  select(ID,
         sample,
         mhd.personality_disorder_diagnosed_cop_numeric)

### Merge
glad_mhd_dat_id <- dplyr::full_join(mhd_dat_glad,
                               mhd_dat_glad_coping,
                               by = c("ID",
                                      "sample"
                                      )
                               )


# NBR
nbr_mhd_dat_id <- readRDS(file = paste0(filepath_cleaned_latest_freeze, "coping_nbr/clinical/mhd_coping_nbr_clean.rds"))

nbr_mhd_dat_id <- nbr_mhd_dat_id %>%
  select(ID,
         sample,
         mhd.personality_disorder_diagnosed_cop_numeric)

# RAMP
ramp_mhd_dat_id <- readRDS(file = paste0(filepath_cleaned_latest_freeze, "ramp/clinical/mhd_ramp_clean.rds"))

ramp_mhd_dat_id <- ramp_mhd_dat_id %>%
  select(ID,
         sample,
         mhd.personality_disorder_diagnosed_cop_numeric)

# Bind
MHD <- edgi_mhd_dat_id %>%
  bind_rows(glad_mhd_dat_id,
            nbr_mhd_dat_id,
            ramp_mhd_dat_id)
```

# Merge MHD and original data
```{r merge MHD with dat}
dat_merged <- dplyr::left_join(dat,
                               MHD,
                               by = c("ID",
                                      "sample"
                                      )
                               )

```

# Check freq of BPD
```{r}
# My sample
dat_merged <- dat_merged %>%
  mutate(personality_disorder =
           case_when(mhd.personality_disorder_diagnosed_numeric == 5 |
                      mhd.personality_disorder_diagnosed_cop_numeric == 5 ~ 1 ))

dat_merged %>%
  freq(personality_disorder)

(553/25451)*100 # 2.2%

# Overall sample
MHD <- MHD %>%
  mutate(personality_disorder =
           case_when(mhd.personality_disorder_diagnosed_numeric == 5 |
                      mhd.personality_disorder_diagnosed_cop_numeric == 5 ~ 1 ))

MHD %>%
  freq(personality_disorder)

(3936/97198)*100 # 4%
```








