---
title: "Cross-tab of "
author: "Helena Davies"
date: "13/05/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  ) 
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "naniar",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
## Final cleaned data
```{r Read in data}
dat <- readRDS(file = "../data_cleaned/final_dat_merged_exclusions_2022-05-11.rds")

# Check
dim(dat)
colnames(dat)

dat <- dat %>%
   mutate(age_category_COVID_baseline =
             case_when(age_category_COVID_baseline == "56-65" ~ "56-65",
                       age_category_COVID_baseline == "16-25" ~ "16-25",
                       age_category_COVID_baseline == "26-35" ~ "26-35",
                       age_category_COVID_baseline == "36-45" ~ "36-45",
                       age_category_COVID_baseline == "46-55" ~ "46-55",
                       age_category_COVID_baseline == "66-70" ~ "66+",
                       age_category_COVID_baseline == "71+" ~ "66+"
                ))
```

# 

```{r}
dat <- dat %>%
  mutate(retired =
           case_when(paid_employment_key_worker == "Retired" ~ "Retired",
                     
                     TRUE ~ "Not retired"))

dat <- dat %>%
  mutate(age =
           case_when(age_category_COVID_baseline == "66+" ~ "66+",
                     
                     TRUE ~ "<66"))




dat %>%
  group_by(age) %>%
  freq(retired)



```





