---
title: "Data_Analysis_EDBeh_SelfHarm"
author: "Helena Davies"
date: "28/01/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```

### Read in TAF data
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

### Read in EDEQ data
```{r}
dat.edeq <- readRDS(file = "../data_cleaned/dat.edeq.rds")
dim(dat.edeq)
colnames(dat.edeq)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")
COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")
COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")
COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98")
COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")
COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB",
                    "#808080")
COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")
COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")
RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b",
                "#b7dee8")
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(),
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

##Demographics - TAF
#cohort
```{r}
freq(dat.taf$cohort_name)
```

#age
```{r}
freq(dat.taf$age_category)
```

#gender
```{r}
freq(dat.taf$gender)
```

#ethnicity
```{r}
freq(dat.taf$ethnicity)
##Lots of missing data from NBR - have checked ethnicity source script and seems that the original dataset contains a lot of NAs...

##Check which cohort missing data is from
x <- dat.taf %>%
  filter(is.na(ethnicity))

freq(x$cohort_name)

```

#highest level of education
```{r}
freq(dat.taf$highest_education)

##Check which cohort missing data is from
x <- dat.taf %>%
  filter(is.na(highest_education))

freq(x$cohort_name)

```

#Self-reported diagnoses
##Depression
```{r}
freq(dat.taf$depressive_disorders_numeric) 

```

##Mania
```{r}
freq(dat.taf$mhd.mania_hypomania_bipolar_or_manicdepression_numeric) 

```

##anxiety
```{r}
  freq(dat.taf$anxiety_disorders_numeric)

```

##eating disorders
```{r}
freq(dat.taf$eating_disorders_numeric)

```

##OCD
```{r}
  freq(dat.taf$obsessive_compulsive_disorders_numeric)

```

##Psychotic disorder
```{r}
  freq(dat.taf$psychotic_disorders_numeric)
```

##PTSD
```{r eval=FALSE, include=FALSE}
  freq(dat.taf$mhd.posttraumatic_stress_disorder_ptsd_numeric
```
##Autism
```{r}
freq(dat.taf$autism_spectrum_disorder_numeric)
```

##ADHD
```{r}
  freq(dat.taf$mhd.attention_deficit_hyperactivity_disorder_numeric)

```


##PLOTS - TAF 


##**RETRO PREPAN - need to rename these the same as baseline / waves

taf.pandemic_felt_.Wavebaseline: Had you felt that way [life not worth living] before the pandemic?
taf.pandemic_felt.1_.Wavebaseline: Had you felt that way [contemplated harm] before the pandemic?
taf.meant_end_life_pandemic_.Wavebaseline: Before the pandemic, had you deliberately harmed yourself, whether or not you meant to end your life?
```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.worth_living_life_people_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline,
   taf.have_you_contemplated_harming_yourself_.Waveretro_prepan = taf.pandemic_felt.1_.Wavebaseline,
   taf.meant_life_end_weeks_.Waveretro_prepan = taf.meant_end_life_pandemic_.Wavebaseline
    )

```


#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```


#2. Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.worth_living_life_people),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.worth_living_life_people_factor <- factor(dat.no.nas$taf.worth_living_life_people)
```

#3. Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                           "1a",
                           "1b",
                           "2a",
                           "2b",
                           "3a",
                           "3b",
                           "4a",
                           "4b",
                           "5",
                           "6",
                           "7",
                           "8"))


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#4. Rename waves to dates
```{r}

##Rename waves
levels(dat.no.nas$wave_factor)[1] <- "test"


```


#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.worth_living_life_people_factor) / sum(table(taf.worth_living_life_people_factor))) %>%
  ungroup() %>%
  mutate(taf.worth_living_life_people_factor = rep(levels(dat.no.nas[["taf.worth_living_life_people_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.worth_living_life_people_factor = fct_relevel(taf.worth_living_life_people_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes, once",
                           "Yes, more than once"))


```


7. PLOT ! [WHAT TO DO WITH "YES" FROM RAMP RETRO PREPAN?]
```{r}
ggplot(dat_plot,
       aes(x = taf.worth_living_life_people_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent)

```


##PLOTS - TAF (LIFE NOT WORTH LIVING, 2 WEEKS)
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```



#2. Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.felt_weeks_past_factor <- factor(dat.no.nas$taf.felt_weeks_past)
```

#3. Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                           "1a",
                           "1b",
                           "2a",
                           "2b",
                           "3a",
                           "3b",
                           "4a",
                           "4b",
                           "5",
                           "6",
                           "7",
                           "8"))


#Check that this worked
str(dat.no.nas$wave_factor)
```

#4. Rename waves to dates
```{r}

##Rename waves
levels(dat.no.nas$wave_factor)[1] <- "test"


```


#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past_factor) / sum(table(taf.felt_weeks_past_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past_factor = fct_relevel(taf.felt_weeks_past_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT ! [WHAT TO DO WITH "YES" FROM RAMP RETRO PREPAN?]
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent)

```









































##EDEQ

##***NEED NUMERIC VERSIONS FOR:
edeq.actively_been_monitoring_your_shape_or_weight_.Wavebaseline_numeric
edeq.regard_lost_control_eaten_.Wavebaseline_numeric
edeq.sick_means_made_shape_.Wavebaseline_numeric
edeq.diuretics_laxatives_means_shape_.Wavebaseline_numeric
edeq.compulsive_driven_burn_calories_.Wavebaseline_numeric

*****
"PRE-PANDEMIC" [retrospective] EDEQ BASELINE-SPECIFIC QUESTIONS (*NB: Baseline questions also asks about "Over the past 28 days...")

1. edeq.deliberately_limit_amount_influence.1_baseline
= On how many of the 28 days BEFORE THE PANDEMIC: Have you been deliberately trying to limit the amount of food you eat to influence your shape or weight ?

2. edeq.calories_made_body_shape.1_baseline
= On how many of the 28 days BEFORE THE PANDEMIC: Has thinking about body shape, weight, food, eating, or calories made it very difficult to concentrate on things you are interested in ?

3. edeq.weight_influenced_person.1_baseline
= Over the 28 days BEFORE THE PANDEMIC: Has your weight influenced how you think about yourself as a person?

4. edeq.dissatisfied_shape_weight.1_baseline
= Over the 28 days BEFORE THE PANDEMIC: How dissatisfied have you been with your weight or shape?

5. edeq.eating_behaviours_concerns_distressed.1_baseline
= Over the 28 days BEFORE THE PANDEMIC: How distressed have you been by your eating behaviours, the measures you've taken to control your weight, or concerns about your weight and shape?

6. edeq.feelings_pandemic_felt_baseline [ONLY ONE NOT ASKED IN FOLLOW UP]
= How different are these feelings to how you felt before the pandemic?

7. edeq.nibbled_picked_snacks_grazed.1_baseline
= On how many of the past 28 days BEFORE THE PANDEMIC: Picked at, nibbled, or grazed food repeatedly outside of planned meals and snacks?

8. edeq.felt_anxious_blue_bored.2_baseline
= On how many of the past 28 days BEFORE THE PANDEMIC: Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
 
9.  edeq.felt_anxious_blue_bored.3_baseline
= On how many of the past 28 days BEFORE THE PANDEMIC: Eaten less than usual because you felt anxious, blue, bored, frustrated or lonely?

10.  edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline
= Over the past 28 days BEFORE PANDEMIC, how many times have you: Actively been monitoring your shape or weight ?

11.  edeq.regard_lost_control_eaten.1_baseline
= Over the past 28 days BEFORE PANDEMIC, how many times have you:Eaten what other people would regard as an unusually large amount of food with a sense of having lost control over your eating?

12.  edeq.sick_means_made_shape.1_baseline =
Over the past 28 days BEFORE PANDEMIC, how many times have you:Made yourself sick as a means of controlling your shape or weight?
 
13. edeq.diuretics_laxatives_means_shape.1_baseline
= Over the past 28 days BEFORE PANDEMIC, how many times have you: Taken laxatives, diuretics, or diet pills as a means of controlling your shape or weight?
 
 14. edeq.compulsive_driven_burn_calories.1_baseline
= Over the past 28 days BEFORE PANDEMIC, how many times have you: Exercised in a “driven” or “compulsive” way as a means of controlling your weight, shape, or amount of fat, or to burn off calories?


*****
BASELINE + WAVES EDEQ QUESTIONS

1. edeq.deliberately_limit_amount_influence_X 
= On how many of the past 28 days: Have you been deliberately trying to limit the amount of food you eat to influence your shape or weight ?

2. edeq.calories_made_body_shape_X 
= On how many of the past 28 days: Has thinking about body shape, weight, food, eating, or calories made it very difficult to concentrate on things you are interested in ?

3. edeq.weight_influenced_person_baseline
= Over the past 28 days: Has your weight influenced how you think about yourself as a person?

4. edeq.dissatisfied_shape_weight_baseline
= Over the past 28 days: How dissatisfied have you been with your weight or shape?

5. edeq.nibbled_picked_snacks_grazed_baseline
= Over the past 28 days, on how many days have you: Picked at, nibbled, or grazed food repeatedly outside of planned meals and snacks?

6. edeq.felt_anxious_blue_bored_baseline
= Over the past 28 days, on how many days have you: Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?

7. edeq.felt_anxious_blue_bored.1_baseline
= Over the past 28 days, on how many days have you: Have you eaten less than usual because you felt anxious, blue, bored, frustrated or lonely?

8. edeq.eating_behaviours_concerns_distressed_baseline
= Over the past 28 days: How distressed have you been by your eating behaviours, the measures you've taken to control your weight, or concerns about your weight and shape?

9. edeq.actively_been_monitoring_your_shape_or_weight_baseline 
= Over the past 28 days, how many times per day have you: Actively been monitoring your shape or weight ?

10. edeq.regard_lost_control_eaten_baseline
= Over the past 28 days, how many times per day have you:Eaten what other people would regard as an unusually large amount of food with a sense of having lost control over your eating?

11. edeq.sick_means_made_shape_baseline
= Over the past 28 days, how many times per day have you: Made yourself sick as a means of controlling your shape or weight?

12. edeq.diuretics_laxatives_means_shape_baseline
= Over the past 28 days, how many times per day have you: Taken laxatives, diuretics, or diet pills as a means of controlling your shape or weight?

13. edeq.compulsive_driven_burn_calories_baseline
= Over the past 28 days, how many times per day have you: Exercised in a “driven” or “compulsive” way as a means of controlling your weight, shape, or amount of fat, or to burn off calories?



****
NB: ONLY RAMP HAS 'RETROSPECTIVE PREPAN' and BASELINE EDEQ
CATEGORIES - distress?
Should split Qs into categories:

1) Restricting

A. deliberately trying to limit the amount of food you eat to influence your shape or weight 
edeq.deliberately_limit_amount_influence.1 (retro prepan)
edeq.deliberately_limit_amount_influence_X (baseline and waves)

B.Eaten less than usual because you felt anxious, blue, bored, frustrated or lonely?
edeq.felt_anxious_blue_bored.3_ (retro prepan)
edeq.felt_anxious_blue_bored.1 (baseline and waves)

2) Compensating
A. Made yourself sick as a means of controlling your shape or weight?
edeq.sick_means_made_shape.1 (retro prepan)
edeq.sick_means_made_shape_X (baseline and waves)

B. Taken laxatives, diuretics, or diet pills as a means of controlling your shape or weight?
edeq.diuretics_laxatives_means_shape.1  (retro prepan)
edeq.diuretics_laxatives_means_shape_x (baseline and waves)

C. Exercised in a “driven” or “compulsive” way as a means of controlling your weight, shape, or amount of fat, or to burn off calories?
edeq.compulsive_driven_burn_calories.1  (retro prepan)
edeq.compulsive_driven_burn_calories_X (baseline and waves)

3) Bingeing behaviour (eating more)

A. Picked at, nibbled, or grazed food repeatedly outside of planned meals and snacks?
edeq.nibbled_picked_snacks_grazed.1 (retro prepan)
edeq.nibbled_picked_snacks_grazed_X (baseline and waves)

B. Eaten more than usual because you felt anxious, blue, bored, frustrated or lonely?
edeq.felt_anxious_blue_bored.2 (retro prepan)
edeq.felt_anxious_blue_bored_X (baseline and waves)

c. Eaten what other people would regard as an unusually large amount of food with a sense of having lost control over your eating?
edeq.regard_lost_control_eaten.1 (retro prepan)
edeq.regard_lost_control_eaten_X  (baseline and waves)

4) Body dissatisfaction / cognitive

A. Has thinking about body shape, weight, food, eating, or calories made it very difficult to concentrate on things you are interested in ?
edeq.calories_made_body_shape.1 (retro prepan)
edeq.calories_made_body_shape_X (baseline and waves)

B. Has your weight influenced how you think about yourself as a person?
edeq.weight_influenced_person.1 (retro prepan)
edeq.weight_influenced_person)X (baseline and waves)

C. How dissatisfied have you been with your weight or shape?
edeq.dissatisfied_shape_weight.1 (retro prepan)
edeq.dissatisfied_shape_weight_X (baseline and waves)

D. Actively been monitoring your shape or weight?
edeq.actively_been_monitoring_your_shape_or_weight_.1 (retro prepan)
edeq.actively_been_monitoring_your_shape_or_weight_X (baseline and waves)


ALSO - DISTRESS

How distressed have you been by your eating behaviours, the measures you've taken to control your weight, or concerns about your weight and shape?
edeq.eating_behaviours_concerns_distressed.1 (retro prepan)
edeq.eating_behaviours_concerns_distressed_X (baseline and waves)

##Rename retro prepandemic variable names in EDEQ

##**need to rename these the same as baseline / waves
```{r}
dat.edeq <- dat.edeq %>% 
  rename(
    edeq.sick_means_made_shape_.Waveretro_prepan = edeq.sick_means_made_shape.1_baseline,
    edeq.felt_anxious_blue_bored.3_.Waveretro_prepan = edeq.felt_anxious_blue_bored.3_baseline,
    edeq.sick_means_made_shape.1_.Waveretro_prepan =  edeq.sick_means_made_shape.1_baseline,
    edeq.diuretics_laxatives_means_shape.1_.Waveretro_prepan= edeq.diuretics_laxatives_means_shape.1_baseline,
    edeq.compulsive_driven_burn_calories.1_.Waveretro_prepan = edeq.compulsive_driven_burn_calories.1_baseline ,
    edeq.nibbled_picked_snacks_grazed.1_.Waveretro_prepan = edeq.nibbled_picked_snacks_grazed.1_baseline,
    edeq.felt_anxious_blue_bored.2_.Waveretro_prepan = edeq.felt_anxious_blue_bored.2_baseline,
    edeq.regard_lost_control_eaten.1_.Waveretro_prepan = edeq.regard_lost_control_eaten.1_baseline,
    edeq.calories_made_body_shape.1_.Waveretro_prepan = edeq.calories_made_body_shape.1_baseline,
    edeq.weight_influenced_person.1_.Waveretro_prepan = edeq.weight_influenced_person.1_baseline,
    edeq.dissatisfied_shape_weight.1_.Waveretro_prepan = edeq.dissatisfied_shape_weight.1_baseline,
    edeq.actively_been_monitoring_your_shape_or_weight_.Waveretro_prepan = edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline,
    edeq.eating_behaviours_concerns_distressed_.Waveretro_prepan = edeq.eating_behaviours_concerns_distressed.1_baseline

    )

```

##PLOTS - EDEQ
1. Need to select variables to use (don't want numeric ones in there as then can't re-structure the data)
```{r}

dat.edeq.long.prep1 <- dat.edeq %>% 
  select(!contains(".Wavebaseline_numeric"))

dat.edeq.long.prep2 <- dat.edeq.long.prep1 %>% 
  select(!contains("baseline_numeric"))

 colnames(dat.edeq.long.prep2) 
 
```

2. Restructure data into long 
```{r eval=FALSE, include=FALSE}
dat.edeq.long <- dat.edeq.long.prep2 %>%
  pivot_longer(
    cols = (starts_with("edeq") &
              contains(".Wave")),
    names_to = "wave_edeq",
    values_to = "value") %>%
  separate(wave_edeq, into = c("edeq", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "edeq",
     values_from = "value")

colnames(dat.edeq.long)

```

















