---
title: "Data_Analysis_EDBeh_SelfHarm"
author: "Helena Davies"
date: "28/01/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```

### Read in TAF data
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```



# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")
COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")
COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")
COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98")
COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")
COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB",
                    "#808080")
COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")
COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")
RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b",
                "#b7dee8")
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(),
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```



##PLOTS - TAF 


##**RETRO PREPAN - need to rename these the same as baseline / waves

taf.pandemic_felt_.Wavebaseline: Had you felt that way [life not worth living] before the pandemic?
taf.pandemic_felt.1_.Wavebaseline: Had you felt that way [contemplated harm] before the pandemic?
taf.meant_end_life_pandemic_.Wavebaseline: Before the pandemic, had you deliberately harmed yourself, whether or not you meant to end your life?
```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.worth_living_life_people_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline,
   taf.have_you_contemplated_harming_yourself_.Waveretro_prepan = taf.pandemic_felt.1_.Wavebaseline,
   taf.meant_life_end_weeks_.Waveretro_prepan = taf.meant_end_life_pandemic_.Wavebaseline
    )

```


#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```


#2. Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.worth_living_life_people),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.worth_living_life_people_factor <- factor(dat.no.nas$taf.worth_living_life_people)
```

#3. Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                           "1a",
                           "1b",
                           "2a",
                           "2b",
                           "3a",
                           "3b",
                           "4a",
                           "4b",
                           "5",
                           "6",
                           "7",
                           "8"))


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#4. Rename waves to dates
```{r}

##Rename waves
levels(dat.no.nas$wave_factor)[1] <- "test"


```


#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.worth_living_life_people_factor) / sum(table(taf.worth_living_life_people_factor))) %>%
  ungroup() %>%
  mutate(taf.worth_living_life_people_factor = rep(levels(dat.no.nas[["taf.worth_living_life_people_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.worth_living_life_people_factor = fct_relevel(taf.worth_living_life_people_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes, once",
                           "Yes, more than once"))


```


7. PLOT ! [WHAT TO DO WITH "YES" FROM RAMP RETRO PREPAN?]
```{r}
ggplot(dat_plot,
       aes(x = taf.worth_living_life_people_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent)

```


##PLOTS - TAF (LIFE NOT WORTH LIVING, 2 WEEKS)
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```



#2. Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.felt_weeks_past_factor <- factor(dat.no.nas$taf.felt_weeks_past)
```

#3. Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                           "1a",
                           "1b",
                           "2a",
                           "2b",
                           "3a",
                           "3b",
                           "4a",
                           "4b",
                           "5",
                           "6",
                           "7",
                           "8"))


#Check that this worked
str(dat.no.nas$wave_factor)
```

#4. Rename waves to dates
```{r}

##Rename waves
levels(dat.no.nas$wave_factor)[1] <- "test"


```


#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past_factor) / sum(table(taf.felt_weeks_past_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past_factor = fct_relevel(taf.felt_weeks_past_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent)

```

































