---
title: "Deriving Variables"
author: "Helena Davies"
date: "04/05/2021"
output: html_document
---


```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```


#Retrieve the recent date
```{r Recent date}
date = Sys.Date()
date
```

#### R functions

```{r call in function library functions}
# source all functions in the function folder
source("./functions.R")
```

# Read in data
```{r}
dat <- readRDS(file = "../data_cleaned/data.final2021-05-04.rds")
dim(dat)
colnames(dat)
```




EXPOSURE: 

•	Eating disorder behaviour: Pre-pandemic eating disorder diagnostic status (self-reported diagnosis and/or algorithm-derived)
    o	Lifetime anorexia nervosa: 1, 0
    o	Lifetime bulimia nervosa:  1, 0
    o	Lifetime binge-eating disorder: 1, 0

#Prepandemic binge-eating disorder
```{r}

  dat <- dat %>%
    mutate(
      BED_prepandemic =
        case_when(COPING_bed_group_numeric == 1 |
                  BED_group_numeric == 1 ~ 1,
                  
                  COPING_bed_group_numeric == 0 |
                    BED_group_numeric == 0 ~ 0,
                  
                  is.na(COPING_bed_group_numeric) &
                    is.na(BED_group_numeric) ~ NA_real_
                
        )
        )
    

#Check
 dat %>%
   freq(BED_prepandemic)

```
#Prepandemic bulimia nervosa
```{r}

  dat <- dat %>%
    mutate(
      BN_prepandemic =
        case_when(COPING_bulimia_group_numeric == 1 |
                  bulimia_group_numeric== 1 ~ 1,
                  
                  COPING_bulimia_group_numeric == 0 |
                    bulimia_group_numeric == 0 ~ 0,
                  
                  is.na(COPING_bulimia_group_numeric) &
                    is.na(bulimia_group_numeric) ~ NA_real_
                
        )
        )
    

#Check
 dat %>%
   freq(BN_prepandemic)

```
#Prepandemic anorexia nervosa
```{r}

  dat <- dat %>%
    mutate(
      AN_prepandemic =
        case_when(COPING_anorexia_group_numeric== 1 |
                  anorexia_group_numeric == 1 ~ 1,
                  
                  COPING_anorexia_group_numeric == 0 |
                    anorexia_group_numeric == 0 ~ 0,
                  
                  is.na(COPING_anorexia_group_numeric) &
                    is.na(anorexia_group_numeric) ~ NA_real_
                
        )
        )
    

#Check
 dat %>%
   freq(AN_prepandemic)

```
OUTCOMES

•	Eating disorder behaviour:
  o	binge eating during the COVID-19 pandemic: binary (1,0)
  o	low weight during the COVID-19 pandemic: binary (1,0)

•	Self-harm thoughts/behaviour:
  o	passive suicidal ideation during COVID-19 pandemic: binary (1,0)
  o	self-harm ideation during the COVID-19 pandemic: binary (1,0)
  o	self-harm during the COVID-19 pandemic: binary (1,0)

o	Cumulative score; 
	scores of 3 indicate someone has experienced all of the above during the pandemic
	scores of 2 indicate someone has experienced two of the above during the pandemic
	scores of 1 indicate someone has experienced one of the above during the pandemic
	scores of 0 indicate someone has experienced none of the above during the pandemic


##ANY Binge eating during the COVID-19 pandemic
```{r}

dat <- dat %>%
  mutate(pandemic_binge_eating =
           case_when(ed_scid5.regular_episodes_eating_binges_.Wave_1b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_2b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_3b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_4b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_6b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_8b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_10b == "Yes" |
                       ed_scid5.regular_episodes_eating_binges_.Wave_12b == "Yes" ~ 1,
                     
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_1b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_2b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_3b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_4b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_6b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_8b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_10b) &
                       is.na(ed_scid5.regular_episodes_eating_binges_.Wave_12b) ~ NA_real_,
                     
                      (ed_scid5.regular_episodes_eating_binges_.Wave_1b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_1b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_2b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_2b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_3b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_3b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_4b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_4b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_6b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_6b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_8b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_8b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_10b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_10b)) &
                       (ed_scid5.regular_episodes_eating_binges_.Wave_12b == "No" | is.na(ed_scid5.regular_episodes_eating_binges_.Wave_12b)) ~ 0
                    
           ))

#Check
dat %>%
  freq(pandemic_binge_eating)

```
##ANY Low weight during the COVID-19 pandemic
```{r}

dat <- dat %>%
  mutate(pandemic_low_weight =
           case_when(ed_scid5.weigh_weighed_past_month_.Wave_1b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_2b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_3b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_4b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_6b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_8b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_10b == "Yes" |
                       ed_scid5.weigh_weighed_past_month_.Wave_12b == "Yes" ~ 1,
                     
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_1b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_2b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_3b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_4b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_6b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_8b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_10b) &
                       is.na(ed_scid5.weigh_weighed_past_month_.Wave_12b) ~ NA_real_,
                     
                       (ed_scid5.weigh_weighed_past_month_.Wave_1b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_1b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_2b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_2b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_3b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_3b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_4b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_4b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_6b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_6b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_8b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_8b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_10b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_10b)) &
                       (ed_scid5.weigh_weighed_past_month_.Wave_12b == "No" | is.na(ed_scid5.weigh_weighed_past_month_.Wave_12b)) ~ 0
                    
           ))

#Check
dat %>%
  freq(pandemic_low_weight)

```


  
#ANY passive suicidal ideation during COVID-19 pandemic
```{r}

dat <- dat %>%
  mutate(pandemic_passive_suicidal_ideation =
           case_when(
                     taf.felt_weeks_past_.Wave_1a == "Yes" |
                       taf.felt_weeks_past_.Wave_1b == "Yes" |
                       taf.felt_weeks_past_.Wave_2a == "Yes" |
                       taf.felt_weeks_past_.Wave_2b == "Yes" |
                       taf.felt_weeks_past_.Wave_3a == "Yes" |
                       taf.felt_weeks_past_.Wave_3b == "Yes" |
                       taf.felt_weeks_past_.Wave_4a == "Yes" |
                       taf.felt_weeks_past_.Wave_4b == "Yes" |
                       taf.felt_weeks_past_.Wave_5a == "Yes" |
                       taf.felt_weeks_past_.Wave_6b == "Yes" |
                       taf.felt_weeks_past_.Wave_7a == "Yes" |
                       taf.felt_weeks_past_.Wave_8b == "Yes" |
                       taf.felt_weeks_past_.Wave_9a == "Yes" |
                       taf.felt_weeks_past_.Wave_10b == "Yes" |
                       taf.felt_weeks_past_.Wave_11a == "Yes" |
                       taf.felt_weeks_past_.Wave_12b == "Yes" ~ 1,
                        
              
                       is.na(taf.felt_weeks_past_.Wave_1a) &
                       is.na(taf.felt_weeks_past_.Wave_1b) &
                       is.na(taf.felt_weeks_past_.Wave_2a) &
                       is.na(taf.felt_weeks_past_.Wave_2b) &
                       is.na(taf.felt_weeks_past_.Wave_3a) &
                       is.na(taf.felt_weeks_past_.Wave_3b) &
                       is.na(taf.felt_weeks_past_.Wave_4a) &
                       is.na(taf.felt_weeks_past_.Wave_4b) &
                       is.na(taf.felt_weeks_past_.Wave_5a) &
                       is.na(taf.felt_weeks_past_.Wave_6b) &
                       is.na(taf.felt_weeks_past_.Wave_7a) &
                       is.na(taf.felt_weeks_past_.Wave_8b) &
                       is.na(taf.felt_weeks_past_.Wave_9a) &
                       is.na(taf.felt_weeks_past_.Wave_10b) &
                       is.na(taf.felt_weeks_past_.Wave_11a) &
                       is.na(taf.felt_weeks_past_.Wave_12b) ~ NA_real_,
                     
                      
                       (taf.felt_weeks_past_.Wave_1a == "No" | is.na(taf.felt_weeks_past_.Wave_1a)) &
                       (taf.felt_weeks_past_.Wave_1b == "No" | is.na(taf.felt_weeks_past_.Wave_1b)) &
                       (taf.felt_weeks_past_.Wave_2a == "No" | is.na(taf.felt_weeks_past_.Wave_2a)) &
                       (taf.felt_weeks_past_.Wave_2b == "No" | is.na(taf.felt_weeks_past_.Wave_2b)) &
                       (taf.felt_weeks_past_.Wave_3a == "No" | is.na(taf.felt_weeks_past_.Wave_3a)) &
                       (taf.felt_weeks_past_.Wave_3b == "No" | is.na(taf.felt_weeks_past_.Wave_3b)) &
                       (taf.felt_weeks_past_.Wave_4a == "No" | is.na(taf.felt_weeks_past_.Wave_4a)) &
                       (taf.felt_weeks_past_.Wave_4b == "No" | is.na(taf.felt_weeks_past_.Wave_4b)) &
                       (taf.felt_weeks_past_.Wave_5a == "No" | is.na(taf.felt_weeks_past_.Wave_5a)) &
                       (taf.felt_weeks_past_.Wave_6b == "No" | is.na(taf.felt_weeks_past_.Wave_6b)) &
                       (taf.felt_weeks_past_.Wave_7a == "No" | is.na(taf.felt_weeks_past_.Wave_7a)) &
                       (taf.felt_weeks_past_.Wave_8b == "No" | is.na(taf.felt_weeks_past_.Wave_8b)) &
                       (taf.felt_weeks_past_.Wave_9a == "No" | is.na(taf.felt_weeks_past_.Wave_9a)) &
                       (taf.felt_weeks_past_.Wave_10b == "No" | is.na(taf.felt_weeks_past_.Wave_10b)) &
                       (taf.felt_weeks_past_.Wave_11a == "No" | is.na(taf.felt_weeks_past_.Wave_11a)) &
                       (taf.felt_weeks_past_.Wave_12b == "No" | is.na(taf.felt_weeks_past_.Wave_12b)) ~ 0
                    
           ))

#Check
dat %>%
  freq(pandemic_passive_suicidal_ideation)

```
#ANY self-harm ideation during the COVID-19 pandemic
```{r}
dat <- dat %>%
  mutate(pandemic_selfharm_ideation =
           case_when(
             taf.felt_weeks_past.1_.Wave_1a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_1b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_2a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_2b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_3a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_3b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_4a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_4b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_5a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_6b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_7a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_8b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_9a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_10b == "Yes" |
                       taf.felt_weeks_past.1_.Wave_11a == "Yes" |
                       taf.felt_weeks_past.1_.Wave_12b == "Yes" ~ 1,
                        
              
                       is.na(taf.felt_weeks_past.1_.Wave_1a) &
                       is.na(taf.felt_weeks_past.1_.Wave_1b) &
                       is.na(taf.felt_weeks_past.1_.Wave_2a) &
                       is.na(taf.felt_weeks_past.1_.Wave_2b) &
                       is.na(taf.felt_weeks_past.1_.Wave_3a) &
                       is.na(taf.felt_weeks_past.1_.Wave_3b) &
                       is.na(taf.felt_weeks_past.1_.Wave_4a) &
                       is.na(taf.felt_weeks_past.1_.Wave_4b) &
                       is.na(taf.felt_weeks_past.1_.Wave_5a) &
                       is.na(taf.felt_weeks_past.1_.Wave_6b) &
                       is.na(taf.felt_weeks_past.1_.Wave_7a) &
                       is.na(taf.felt_weeks_past.1_.Wave_8b) &
                       is.na(taf.felt_weeks_past.1_.Wave_9a) &
                       is.na(taf.felt_weeks_past.1_.Wave_10b) &
                       is.na(taf.felt_weeks_past.1_.Wave_11a) &
                       is.na(taf.felt_weeks_past.1_.Wave_12b) ~ NA_real_,
                     
                      
                       (taf.felt_weeks_past.1_.Wave_1a == "No" | is.na(taf.felt_weeks_past.1_.Wave_1a)) &
                       (taf.felt_weeks_past.1_.Wave_1b == "No" | is.na(taf.felt_weeks_past.1_.Wave_1b)) &
                       (taf.felt_weeks_past.1_.Wave_2a == "No" | is.na(taf.felt_weeks_past.1_.Wave_2a)) &
                       (taf.felt_weeks_past.1_.Wave_2b == "No" | is.na(taf.felt_weeks_past.1_.Wave_2b)) &
                       (taf.felt_weeks_past.1_.Wave_3a == "No" | is.na(taf.felt_weeks_past.1_.Wave_3a)) &
                       (taf.felt_weeks_past.1_.Wave_3b == "No" | is.na(taf.felt_weeks_past.1_.Wave_3b)) &
                       (taf.felt_weeks_past.1_.Wave_4a == "No" | is.na(taf.felt_weeks_past.1_.Wave_4a)) &
                       (taf.felt_weeks_past.1_.Wave_4b == "No" | is.na(taf.felt_weeks_past.1_.Wave_4b)) &
                       (taf.felt_weeks_past.1_.Wave_5a == "No" | is.na(taf.felt_weeks_past.1_.Wave_5a)) &
                       (taf.felt_weeks_past.1_.Wave_6b == "No" | is.na(taf.felt_weeks_past.1_.Wave_6b)) &
                       (taf.felt_weeks_past.1_.Wave_7a == "No" | is.na(taf.felt_weeks_past.1_.Wave_7a)) &
                       (taf.felt_weeks_past.1_.Wave_8b == "No" | is.na(taf.felt_weeks_past.1_.Wave_8b)) &
                       (taf.felt_weeks_past.1_.Wave_9a == "No" | is.na(taf.felt_weeks_past.1_.Wave_9a)) &
                       (taf.felt_weeks_past.1_.Wave_10b == "No" | is.na(taf.felt_weeks_past.1_.Wave_10b)) &
                       (taf.felt_weeks_past.1_.Wave_11a == "No" | is.na(taf.felt_weeks_past.1_.Wave_11a)) &
                       (taf.felt_weeks_past.1_.Wave_12b == "No" | is.na(taf.felt_weeks_past.1_.Wave_12b)) ~ 0
                    
           ))
```


#ANY self-harm during the COVID-19 pandemic
```{r}

dat <- dat %>%
mutate(pandemic_selfharm =
           case_when(
                     taf.meant_life_end_weeks_.Wave_1a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_1b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_2a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_2b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_3a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_3b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_4a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_4b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_5a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_6b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_7a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_8b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_9a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_10b == "Yes" |
                       taf.meant_life_end_weeks_.Wave_11a == "Yes" |
                       taf.meant_life_end_weeks_.Wave_12b == "Yes" ~ 1,
                        
              
                       is.na(taf.meant_life_end_weeks_.Wave_1a) &
                       is.na(taf.meant_life_end_weeks_.Wave_1b) &
                       is.na(taf.meant_life_end_weeks_.Wave_2a) &
                       is.na(taf.meant_life_end_weeks_.Wave_2b) &
                       is.na(taf.meant_life_end_weeks_.Wave_3a) &
                       is.na(taf.meant_life_end_weeks_.Wave_3b) &
                       is.na(taf.meant_life_end_weeks_.Wave_4a) &
                       is.na(taf.meant_life_end_weeks_.Wave_4b) &
                       is.na(taf.meant_life_end_weeks_.Wave_5a) &
                       is.na(taf.meant_life_end_weeks_.Wave_6b) &
                       is.na(taf.meant_life_end_weeks_.Wave_7a) &
                       is.na(taf.meant_life_end_weeks_.Wave_8b) &
                       is.na(taf.meant_life_end_weeks_.Wave_9a) &
                       is.na(taf.meant_life_end_weeks_.Wave_10b) &
                       is.na(taf.meant_life_end_weeks_.Wave_11a) &
                       is.na(taf.meant_life_end_weeks_.Wave_12b) ~ NA_real_,
                     
                      
                       (taf.meant_life_end_weeks_.Wave_1a == "No" | is.na(taf.meant_life_end_weeks_.Wave_1a)) &
                       (taf.meant_life_end_weeks_.Wave_1b == "No" | is.na(taf.meant_life_end_weeks_.Wave_1b)) &
                       (taf.meant_life_end_weeks_.Wave_2a == "No" | is.na(taf.meant_life_end_weeks_.Wave_2a)) &
                       (taf.meant_life_end_weeks_.Wave_2b == "No" | is.na(taf.meant_life_end_weeks_.Wave_2b)) &
                       (taf.meant_life_end_weeks_.Wave_3a == "No" | is.na(taf.meant_life_end_weeks_.Wave_3a)) &
                       (taf.meant_life_end_weeks_.Wave_3b == "No" | is.na(taf.meant_life_end_weeks_.Wave_3b)) &
                       (taf.meant_life_end_weeks_.Wave_4a == "No" | is.na(taf.meant_life_end_weeks_.Wave_4a)) &
                       (taf.meant_life_end_weeks_.Wave_4b == "No" | is.na(taf.meant_life_end_weeks_.Wave_4b)) &
                       (taf.meant_life_end_weeks_.Wave_5a == "No" | is.na(taf.meant_life_end_weeks_.Wave_5a)) &
                       (taf.meant_life_end_weeks_.Wave_6b == "No" | is.na(taf.meant_life_end_weeks_.Wave_6b)) &
                       (taf.meant_life_end_weeks_.Wave_7a == "No" | is.na(taf.meant_life_end_weeks_.Wave_7a)) &
                       (taf.meant_life_end_weeks_.Wave_8b == "No" | is.na(taf.meant_life_end_weeks_.Wave_8b)) &
                       (taf.meant_life_end_weeks_.Wave_9a == "No" | is.na(taf.meant_life_end_weeks_.Wave_9a)) &
                       (taf.meant_life_end_weeks_.Wave_10b == "No" | is.na(taf.meant_life_end_weeks_.Wave_10b)) &
                       (taf.meant_life_end_weeks_.Wave_11a == "No" | is.na(taf.meant_life_end_weeks_.Wave_11a)) &
                       (taf.meant_life_end_weeks_.Wave_12b == "No" | is.na(taf.meant_life_end_weeks_.Wave_12b)) ~ 0
                    
           ))
                    
   
#Check
dat %>%
  freq(pandemic_selfharm)
```


#Covariates
  •	age
  •	sex
  • Current symptoms
  •	Ethnicity 
  •	Education (proxying SES)
  
  o	Sensitivity analysis; Other mental health diagnosis pre-pandemic, i.e., not ED
    	Count
    	Group (Dep, Anx, Dep+Anx, Psychotic, ADHD, ASD, PTSD)

#Age
```{r}

dat %>%
  freq(age_category)

```

#Sex
```{r}

dat %>%
  freq(gender_unc) #***does RAMP have sex?
```

#Ethnicity
```{r}

dat %>%
  freq(ethnicity)

```

#Education
```{r}

dat %>%
  freq(highest_education) #Is this definitely prepandemic?

```

# Current baseline symptoms

```{r}



```

#Sensitivity analysis; Other mental health diagnosis pre-pandemic, i.e., not ED
    1. Count
    2. Group (Dep, Anx, Dep+Anx, Psychotic, ADHD, ASD, PTSD)
```{r}




```



