---
title: "Checking dup IDs"
author: "Helena Davies"
date: "26/03/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```


#Retrieve the recent date
```{r Recent date}
date = Sys.Date()
date
```


IDs that are duplicated in EDEQ RAMP waves AND RAMP baseline
"1125b21bce6837c04a2d25e594f6"
"243ee9773c50486a347ee2f669dc"
"535dc8c1b776fc5451e8d24b922f"
"B9cb44638fc728f7ade0b43419bd" -- not in baseline?
"5842dd2523474a35f849d7105152"
"Fc97d7705ab0ec4bf95fa3eea814"
"0f0965788de87a3fad79aba14085"
"1a47ff6555d71515aa20484e59c4"
"2d6f692405cebd783448d2d3bcdd"
"5842dd2523474a35f849d7105152"
"b5e2e62f0a2c261807caa1ac90b5" 
"d301f9a79573ee7b36d5736eb298"
"fc97d7705ab0ec4bf95fa3eea814"


# Demographics 
## RAMP
### Read in data
```{r ramp dem cols}

ramp.dem.raw <- readRDS(file = "../data_raw/ramp/dem_ramp.rds")
dim(ramp.dem.raw)
colnames(ramp.dem.raw)

```

1. 1125b21bce6837c04a2d25e594f6

Different 1) age, 2) marital status, 3) relationship with people they're living with, 4) whether they live with pets, 5) member of vulnerable group, etc
```{r}

ramp.dem.raw %>%
  filter(`Login ID` == "1125b21bce6837c04a2d25e594f6")


```

2. 243ee9773c50486a347ee2f669dc

Different 1) age, 2) gender, 3) marital status
```{r}

ramp.dem.raw %>%
  filter(`Login ID` == "243ee9773c50486a347ee2f669dc")

```
3. 535dc8c1b776fc5451e8d24b922f

Different 1) age, 2) marital status, 3) member of vulnerable group
```{r}

ramp.dem.raw %>%
  filter(`Login ID` == "535dc8c1b776fc5451e8d24b922f")


```

4. B9cb44638fc728f7ade0b43419bd

Different 1) age, 2) marital status, 3) member of vulnerable group
```{r}

ramp.dem.raw %>%
  filter(`Login ID` == "d301f9a79573ee7b36d5736eb298")


```

# Demographics 
## COPING NBR
### Read in data
```{r}
nbr.dem.raw <- readRDS(file = "../data_raw/nbr/demographics_coping_nbr.rds")
dim(nbr.dem.raw)
colnames(nbr.dem.raw)

```

##Idenfitying duplicate IDs in BASELINE
```{r}
##Identify dup IDs in baseline
nbr.dem.raw %>%
   group_by(subjectid) %>%
   summarize(N = n()) %>%
   filter(N > 1)

```

##Dup IDs at baseline
00a413507bcf49e779fbeafcd17a			
0293a9c8fcb9bfe99aa9549cde6a			
040ee95bb4cec8404a12173c3dac			
0453d89659acba2bdc59431bb2e1		
053f9ade945d23c679cfc3c854b5			
058350a67b100df156b55cfb8979			
069a1280a6f43fe5a9feb78f8ca4			
07a0206753423fb55e65d26dab90			
0b8dd8c25b78600ae4ae37e70098	
0d43a8f9414ec930a5bb11fa1a86

1. 00a413507bcf49e779fbeafcd17a

Likely same person
```{r}

nbr.dem.raw %>%
  filter(subjectid == "00a413507bcf49e779fbeafcd17a")


```
2. 0293a9c8fcb9bfe99aa9549cde6a

Likely same person
```{r}

nbr.dem.raw %>%
  filter(subjectid == "0293a9c8fcb9bfe99aa9549cde6a")


```

3. 069a1280a6f43fe5a9feb78f8ca4

Likely same person
```{r}

nbr.dem.raw %>%
  filter(subjectid == "069a1280a6f43fe5a9feb78f8ca4")


```

4. 0d43a8f9414ec930a5bb11fa1a86

Likely same person
```{r}

nbr.dem.raw %>%
  filter(subjectid == "0d43a8f9414ec930a5bb11fa1a86")


```