---
title: "EDEQ_Descriptives"
author: "Helena Davies"
date: "08/03/2021"
output: html_document
---


```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```


### Read in EDEQ data
```{r}
dat.edeq <- readRDS(file = "../data_cleaned/dat.edeq.rds")
dim(dat.edeq)
colnames(dat.edeq)
```

##Exclude participants who are missing for EVERY edeq variable (i.e., retroprepan, baseline, and every wave)
```{r}


##Remove participants who have ALL missing data
dat.edeq.all.missing <- dat.edeq %>%
  filter(
           is.na(`edeq.deliberately_limit_amount_influence_baseline`                           ) &
           is.na(`edeq.calories_made_body_shape_baseline`                                     ) &
           is.na(`edeq.weight_influenced_person_baseline`                                      ) &
           is.na(`edeq.dissatisfied_shape_weight_baseline`                                    ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_baseline`                                  ) &
           is.na(`edeq.felt_anxious_blue_bored_baseline`                                      ) &
           is.na(`edeq.felt_anxious_blue_bored.1_baseline`                                     ) &
           is.na(`edeq.eating_behaviours_concerns_distressed_baseline`                        ) &
           is.na(`edeq.deliberately_limit_amount_influence.1_baseline`                         ) &
           is.na(`edeq.calories_made_body_shape.1_baseline`                                   ) &
           is.na(`edeq.weight_influenced_person.1_baseline`                                    ) &
           is.na(`edeq.dissatisfied_shape_weight.1_baseline`                                  ) &
           is.na(`edeq.eating_behaviours_concerns_distressed.1_baseline`                       ) &
           is.na(`edeq.feelings_pandemic_felt_baseline`                                       ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_baseline`                 ) &
           is.na(`edeq.regard_lost_control_eaten_baseline`                                    ) &
           is.na(`edeq.sick_means_made_shape_baseline`                                         ) &
           is.na(`edeq.diuretics_laxatives_means_shape_baseline`                              ) &
           is.na(`edeq.compulsive_driven_burn_calories_baseline`                               ) &
           is.na(`edeq.nibbled_picked_snacks_grazed.1_baseline`                               ) &
           is.na(`edeq.felt_anxious_blue_bored.2_baseline`                                     ) &
           is.na(`edeq.felt_anxious_blue_bored.3_baseline`                                    ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline`              ) &
           is.na(`edeq.regard_lost_control_eaten.1_baseline`                                  ) &
           is.na(`edeq.sick_means_made_shape.1_baseline`                                       ) &
           is.na(`edeq.diuretics_laxatives_means_shape.1_baseline`                            ) &
           is.na(`edeq.compulsive_driven_burn_calories.1_baseline`                             ) &
           is.na(`edeq.deliberately_limit_amount_influence_baseline_numeric`                  ) &
           is.na(`edeq.calories_made_body_shape_baseline_numeric`                              ) &
           is.na(`edeq.weight_influenced_person_baseline_numeric`                             ) &
           is.na(`edeq.dissatisfied_shape_weight_baseline_numeric`                             ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_baseline_numeric`                         ) &
           is.na(`edeq.felt_anxious_blue_bored_baseline_numeric`                               ) &
           is.na(`edeq.felt_anxious_blue_bored.1_baseline_numeric`                            ) &
           is.na(`edeq.eating_behaviours_concerns_distressed_baseline_numeric`                 ) &
           is.na(`edeq.deliberately_limit_amount_influence.1_baseline_numeric`                ) &
           is.na(`edeq.calories_made_body_shape.1_baseline_numeric`                            ) &
           is.na(`edeq.weight_influenced_person.1_baseline_numeric`                           ) &
           is.na(`edeq.dissatisfied_shape_weight.1_baseline_numeric`                           ) &
           is.na(`edeq.eating_behaviours_concerns_distressed.1_baseline_numeric`              ) &
           is.na(`edeq.feelings_pandemic_felt_baseline_numeric`                                ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_baseline_numeric`        ) &
           is.na(`edeq.regard_lost_control_eaten_baseline_numeric`                             ) &
           is.na(`edeq.sick_means_made_shape_baseline_numeric`                                ) &
           is.na(`edeq.diuretics_laxatives_means_shape_baseline_numeric`                       ) &
           is.na(`edeq.compulsive_driven_burn_calories_baseline_numeric`                      ) &
           is.na(`edeq.nibbled_picked_snacks_grazed.1_baseline_numeric`                        ) &
           is.na(`edeq.felt_anxious_blue_bored.2_baseline_numeric`                            ) &
           is.na(`edeq.felt_anxious_blue_bored.3_baseline_numeric`                             ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.1_baseline_numeric`     ) &
           is.na(`edeq.regard_lost_control_eaten.1_baseline_numeric`                           ) &
           is.na(`edeq.sick_means_made_shape.1_baseline_numeric`                              ) &
           is.na(`edeq.diuretics_laxatives_means_shape.1_baseline_numeric`                     ) &
           is.na(`edeq.compulsive_driven_burn_calories.1_baseline_numeric`                    ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wavebaseline`                      ) &
           is.na(`edeq.calories_made_body_shape_.Wavebaseline`                                ) &
           is.na(`edeq.weight_influenced_person_.Wavebaseline`                                 ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wavebaseline`                               ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wavebaseline`       ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wavebaseline`                                 ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wavebaseline`                                ) &
           is.na(`edeq.eating_behaviours_concerns_distressed_.Wavebaseline`                   ) &
           is.na(`edeq.deliberately_limit_amount_influence.1_.Wavebaseline`                    ) &
           is.na(`edeq.calories_made_body_shape.1_.Wavebaseline`                              ) &
           is.na(`edeq.weight_influenced_person.1_.Wavebaseline`                               ) &
           is.na(`edeq.dissatisfied_shape_weight.1_.Wavebaseline`                             ) &
           is.na(`edeq.eating_behaviours_concerns_distressed.1_.Wavebaseline`                  ) &
           is.na(`edeq.feelings_pandemic_felt_.Wavebaseline`                                  ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wavebaseline`            ) &
           is.na(`edeq.regard_lost_control_eaten_.Wavebaseline`                               ) &
           is.na(`edeq.sick_means_made_shape_.Wavebaseline`                                    ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wavebaseline`                         ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wavebaseline`                          ) &
           is.na(`edeq.nibbled_picked_snacks_grazed.1_.Wavebaseline`                          ) &
           is.na(`edeq.felt_anxious_blue_bored.2_.Wavebaseline`                                ) &
           is.na(`edeq.felt_anxious_blue_bored.3_.Wavebaseline`                               ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.1_.Wavebaseline`         ) &
           is.na(`edeq.regard_lost_control_eaten.1_.Wavebaseline`                             ) &
           is.na(`edeq.sick_means_made_shape.1_.Wavebaseline`                                  ) &
           is.na(`edeq.diuretics_laxatives_means_shape.1_.Wavebaseline`                       ) &
           is.na(`edeq.compulsive_driven_burn_calories.1_.Wavebaseline`                        ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wavebaseline_numeric`             ) &
           is.na(`edeq.calories_made_body_shape_.Wavebaseline_numeric`                         ) &
           is.na(`edeq.weight_influenced_person_.Wavebaseline_numeric`                        ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wavebaseline_numeric`                        ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wavebaseline_numeric`                    ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wavebaseline_numeric`                          ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wavebaseline_numeric`                       ) &
           is.na(`edeq.eating_behaviours_concerns_distressed_.Wavebaseline_numeric`            ) &
           is.na(`edeq.deliberately_limit_amount_influence.1_.Wavebaseline_numeric`           ) &
           is.na(`edeq.calories_made_body_shape.1_.Wavebaseline_numeric`                       ) &
           is.na(`edeq.weight_influenced_person.1_.Wavebaseline_numeric`                      ) &
           is.na(`edeq.dissatisfied_shape_weight.1_.Wavebaseline_numeric`                      ) &
           is.na(`edeq.eating_behaviours_concerns_distressed.1_.Wavebaseline_numeric`         ) &
           is.na(`edeq.feelings_pandemic_felt_.Wavebaseline_numeric`                           ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wavebaseline_numeric`   ) &
           is.na(`edeq.regard_lost_control_eaten_.Wavebaseline_numeric`                        ) &
           is.na(`edeq.sick_means_made_shape_.Wavebaseline_numeric`                           ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wavebaseline_numeric`             ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wavebaseline_numeric`                 ) &
           is.na(`edeq.nibbled_picked_snacks_grazed.1_.Wavebaseline_numeric`                   ) &
           is.na(`edeq.felt_anxious_blue_bored.2_.Wavebaseline_numeric`                       ) &
           is.na(`edeq.felt_anxious_blue_bored.3_.Wavebaseline_numeric`                        ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.1_.Wavebaseline_numeric`) &
           is.na(`edeq.regard_lost_control_eaten.1_.Wavebaseline_numeric`                      ) &
           is.na(`edeq.sick_means_made_shape.1_.Wavebaseline_numeric`                         ) &
           is.na(`edeq.diuretics_laxatives_means_shape.1_.Wavebaseline_numeric`                ) &
           is.na(`edeq.compulsive_driven_burn_calories.1_.Wavebaseline_numeric`               ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 1b`                           ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 2b`                          ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 3b`                           ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 4b`                          ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 6`                            ) &
           is.na(`edeq.deliberately_limit_amount_influence_.Wave 8`                           ) &
           is.na(`edeq.calories_made_body_shape_.Wave 1b`                                      ) &
           is.na(`edeq.calories_made_body_shape_.Wave 2b`                                     ) &
           is.na(`edeq.calories_made_body_shape_.Wave 3b`             ) &
           is.na(`edeq.calories_made_body_shape_.Wave 4b`                                     ) &
           is.na(`edeq.calories_made_body_shape_.Wave 6`                                       ) &
           is.na(`edeq.calories_made_body_shape_.Wave 8`                                      ) &
           is.na(`edeq.weight_influenced_person_.Wave 1b`                                      ) &
           is.na(`edeq.weight_influenced_person_.Wave 2b`                                     ) &
           is.na(`edeq.weight_influenced_person_.Wave 3b`                                      ) &
           is.na(`edeq.weight_influenced_person_.Wave 4b`                                     ) &
           is.na(`edeq.weight_influenced_person_.Wave 6`                                       ) &
           is.na(`edeq.weight_influenced_person_.Wave 8`                                      ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 1b`                                     ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 2b`                                    ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 3b`                                     ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 4b`                                    ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 6`                                      ) &
           is.na(`edeq.dissatisfied_shape_weight_.Wave 8`                                     ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 1b`                         ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 2b`                        ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 3b`                         ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 4b`                        ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 6`                          ) &
           is.na(`edeq.eating_behaviours_distressed_concerns_.Wave 8`                         ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 1b`                 ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 2b`                ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 3b`     ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 4b`                ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 6`                  ) &
           is.na(`edeq.actively_been_monitoring_your_shape_or_weight_.Wave 8`                 ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 1b`                                     ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 2b`                                    ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 3b`                                     ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 4b`                                    ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 6`                                      ) &
           is.na(`edeq.regard_lost_control_eaten_.Wave 8`                                     ) &
           is.na(`edeq.sick_means_made_shape_.Wave 1b`                                         ) &
           is.na(`edeq.sick_means_made_shape_.Wave 2b`                                        ) &
           is.na(`edeq.sick_means_made_shape_.Wave 3b`                                         ) &
           is.na(`edeq.sick_means_made_shape_.Wave 4b`                                        ) &
           is.na(`edeq.sick_means_made_shape_.Wave 6`                                          ) &
           is.na(`edeq.sick_means_made_shape_.Wave 8`                                         ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 1b`                               ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 2b`                              ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 3b`                               ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 4b`                              ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 6`                                ) &
           is.na(`edeq.diuretics_laxatives_means_shape_.Wave 8`                               ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 1b`                               ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 2b`                              ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 3b`                               ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 4b`                              ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 6`                                ) &
           is.na(`edeq.compulsive_driven_burn_calories_.Wave 8`                               ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 1b`                                  ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 2b`                                 ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 3b`                                  ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 4b`                                 ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 6`                                   ) &
           is.na(`edeq.nibbled_picked_snacks_grazed_.Wave 8`                                  ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 1b`                                       ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 2b`                                      ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 3b`                                       ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 4b`                                      ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 6`                                        ) &
           is.na(`edeq.felt_anxious_blue_bored_.Wave 8`                                       ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 1b`                                     ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 2b`                                    ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 3b`                                     ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 4b`                                    ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 6`                                      ) &
           is.na(`edeq.felt_anxious_blue_bored.1_.Wave 8` ))
             

nrow(dat.edeq.all.missing)

```

```{r}
##Filter out those with ALL missing data in main dataset
'%!in%' <- function(x,y)!('%in%'(x,y))

dat.edeq <- dat.edeq %>%
  filter(ID %!in% dat.edeq.all.missing$ID)

nrow(dat.edeq) ##TOTAL == 7457

```

##Demographics - EDEQ
#cohort
```{r}
freq(dat.edeq$cohort_name)
```

#age
```{r}
freq(dat.edeq$age_category)
```

#gender
```{r}
freq(dat.edeq$gender)
```

#ethnicity
```{r}
freq(dat.edeq$ethnicity)
##Lots of missing data from NBR - have checked ethnicity source script and seems that the original dataset contains a lot of NAs...

##Check which cohort missing data is from
x <- dat.edeq %>%
  filter(is.na(ethnicity))

freq(x$cohort_name)

```

#highest level of education
```{r}
freq(dat.edeq$highest_education)

##Check which cohort missing data is from
x <- dat.edeq %>%
  filter(is.na(highest_education))

freq(x$cohort_name)

```

#Self-reported diagnoses
##Depression
```{r}
freq(dat.edeq$depressive_disorders_numeric) 

```

##Mania
```{r}
freq(dat.edeq$mhd.mania_hypomania_bipolar_or_manicdepression_numeric) 

```

##anxiety
```{r}
  freq(dat.edeq$anxiety_disorders_numeric)

```



##eating disorders
```{r}
freq(dat.edeq$eating_disorders_numeric)

#PARTICIPANTS WITH NO ED DIAGNOSIS
X <- dat.edeq %>%
  filter(eating_disorders_numeric == 0)

freq(X$cohort_name)

#PARTICIPANTS WHO ANSWERED NO  TO SUSPECTED ED (i.e., should not have answered EDEQ?)
freq(dat.edeq$mhd.suspected_eating_disorder_diagnosed_numeric)

Y <- dat.edeq %>%
  filter(mhd.suspected_eating_disorder_diagnosed_numeric == 0)


freq(Y$cohort_name)

#PARTICIPANTS WHO are NA for diagnosed ED?
missing <- dat.edeq %>%
  filter(is.na(eating_disorders_numeric))

freq(missing$cohort_name)
freq(missing$mhd.suspected_eating_disorder_diagnosed_numeric)

```

##OCD
```{r}
  freq(dat.edeq$obsessive_compulsive_disorders_numeric)

```

##Psychotic disorder
```{r}
  freq(dat.edeq$psychotic_disorders_numeric)
```

##PTSD
```{r}
freq(dat.edeq$mhd.posttraumatic_stress_disorder_ptsd_numeric)

```
##Autism
```{r}
freq(dat.edeq$autism_spectrum_disorder_numeric)
```

##ADHD
```{r}
freq(dat.edeq$mhd.attention_deficit_hyperactivity_disorder_numeric)

```

##Personality disorder
```{r}
freq(dat.edeq$mhd.personality_disorder_numeric)
```

##BDD
```{r}
freq(dat.edeq$mhd.body_dysmorphic_disorder_bdd_numeric)
```
##Anorexia
```{r}
freq(dat.edeq$mhd.anorexia_nervosa_numeric)
```

##Atypical Anorexia
```{r}
freq(dat.edeq$mhd.atypical_anorexia_nervosa_numeric)
```

##Bulimia nervosa
```{r}
freq(dat.edeq$mhd.bulimia_nervosa_numeric)
```

##atypical bulimia
```{r}
freq(dat.edeq$mhd.atypical_bulimia_nervosa_numeric)
```

##atypical bulimia
```{r}
freq(dat.edeq$mhd.atypical_bulimia_nervosa_numeric)
```

##binge-eating disorder (and psychological overeating in RAMP)
```{r}
freq(dat.edeq$mhd.bingeeating_disorder_numeric)
```
##atypical binge eating disorder
```{r}
freq(dat.edeq$mhd.atypical_bingeeating_disorder_numeric)
```

#Purging disorder
```{r}
freq(dat.edeq$mhd.purging_disorder_numeric)
```
#Night eating syndrome
```{r}
freq(dat.edeq$mhd.night_eating_syndrome_numeric)
```
#Pica
```{r}
freq(dat.edeq$mhd.pica_numeric)
```
#ARFID
```{r}
freq(dat.edeq$mhd.avoidantrestrictive_food_intake_disorder_numeric)
```
#Rumination disorder
```{r}
freq(dat.edeq$mhd.rumination_disorder_numeric)
```
#OSFED or EDNOS
```{r}
freq(dat.edeq$mhd.feeding_eating_disorder_numeric)
```
#OTHER EATING DISORDER
```{r}
freq(dat.edeq$mhd.other_eating_disorder_numeric)
```
#SUSPECTED EATING DISORDER
```{r}
freq(dat.edeq$mhd.suspected_eating_disorder_diagnosed_numeric)


x <- dat.edeq %>%
  filter(is.na(mhd.suspected_eating_disorder_diagnosed_numeric))

freq(x$cohort_name)
```


#NO PSYCHIATRIC DIAGNOSES
```{r}
freq(dat.edeq$control_numeric)

```




















