---
title: "Untitled"
author: "Helena Davies"
date: "21/06/2022"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  ) 
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "naniar",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Highest education
NB: highest education AT COVID ASSESSMENT (i.e., EDGI and GLAD COPING baseline questionnaire NOT GLAD/EDGI signup)
## Read in EDGI highest education data
```{r read in highest education cleaned data EDGI}
# EDGI
highest_education_edgi_coping_raw <- readRDS(file = paste0(filepath_raw_latest_freeze, "coping_edgi/employ_coping_edgi.rds"))
dim(highest_education_edgi_coping_raw)
colnames(highest_education_edgi_coping_raw)

highest_education_edgi_coping <- highest_education_edgi_coping_raw %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  remove_duplicates("externalDataReference") %>% # Remove duplicates based on ID
  add_column(sample = "EDGI", .before = "startDate") %>% #create new column 
  select(
         ID = externalDataReference, # ID
         sample, # Sample
         employ.phd,
         employ.masters_degree_or_equivalent,
         employ.postgraduate_degree_or_equivalent,   
         employ.bachelors_degree_or_equivalent,
         employ.a_levelsas_levels_or_equivalent,
         employ.o_levelsgcses_or_equivalent, 
         employ.cses_or_equivalent,
         employ.nvq_or_hnd_or_hnc_or_equivalent,
         employ.other_professional_qualifications_,        
         employ.other_professional_qualifications_text.txt,
employ.none_of_the_above
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(highest_education_edgi_coping)
# Inspect colnames
colnames(highest_education_edgi_coping)
#Differences
dim(highest_education_edgi_coping)[1]-dim(highest_education_edgi_coping_raw)[1]
```

## Read in GLAD highest education data
```{r read in highest education cleaned data GLAD}
# GLAD
highest_education_glad_coping_raw <- readRDS(file = paste0(filepath_raw_latest_freeze, "coping_glad/employ_coping_glad.rds"))
dim(highest_education_glad_coping_raw)
colnames(highest_education_glad_coping_raw)

highest_education_glad_coping <- highest_education_glad_coping_raw %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  remove_duplicates("externalDataReference") %>% # Remove duplicates based on ID
  add_column(sample = "GLAD", .before = "startDate") %>% #create new column 
  select(
         ID = externalDataReference, # ID
         sample, # Sample
      employ.phd,                                        
      employ.masters_degree_or_equivalent,            
      employ.postgraduate_degree_or_equivalent,          
      employ.bachelors_degree_or_equivalent,             
      employ.a_levelsas_levels_or_equivalent,          
      employ.o_levelsgcses_or_equivalent,                
      employ.cses_or_equivalent,                        
      employ.nvq_or_hnd_or_hnc_or_equivalent,          
      employ.other_professional_qualifications_,        
      employ.other_professional_qualifications_text.txt,
      employ.none_of_the_above
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(highest_education_glad_coping)
# Inspect colnames
colnames(highest_education_glad_coping)
#Differences
dim(highest_education_glad_coping)[1]-dim(highest_education_glad_coping_raw)[1]
```

## Read in NBR highest education data
```{r read in highest education cleaned data NBR}
# NBR
highest_education_nbr_raw <- readRDS(file = paste0(filepath_raw_latest_freeze, "coping_nbr/employ_coping_nbr.rds"))
dim(highest_education_nbr_raw)
colnames(highest_education_nbr_raw)

highest_education_nbr <- highest_education_nbr_raw%>% #new dataset with ID
  drop_na(subjectid) %>% # Drop NAs
  remove_duplicates("subjectid") %>% # Remove duplicates based on ID
  add_column(sample = "NBR", .before = "startDate") %>% #create new column 
  select(
         ID = subjectid, # ID
         sample, # Sample
         employ.phd,
         employ.masters_degree_or_equivalent,
         employ.postgraduate_degree_or_equivalent,
         employ.bachelors_degree_or_equivalent,            
         employ.a_levelsas_levels_or_equivalent,
         employ.o_levelsgcses_or_equivalent,
         employ.cses_or_equivalent, 
         employ.nvq_or_hnd_or_hnc_or_equivalent,
         employ.other_professional_qualifications_,
         employ.other_professional_qualifications_text.txt,
         employ.none_of_the_above    
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(highest_education_nbr)
# Inspect colnames
colnames(highest_education_nbr)
#Differences
dim(highest_education_nbr)[1]-dim(highest_education_nbr_raw)[1]
```

## Read in RAMP highest education data
```{r read in highest education cleaned data RAMP}
# RAMP
highest_education_ramp_raw <- readRDS(file = paste0(filepath_raw_latest_freeze, "ramp/employ_ramp.rds"))
dim(highest_education_ramp_raw)
colnames(highest_education_ramp_raw)

highest_education_ramp <- highest_education_ramp_raw %>% #new dataset with ID
  drop_na(`Login ID`) %>% # Drop NAs
  remove_duplicates("Login ID") %>% # Remove duplicates based on ID
  add_column(sample = "RAMP", .before = "startDate") %>% #create new column 
  select(
         ID = `Login ID`, # ID
         sample, # Sample
         employ.what_is_your_highest_level_of_education
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(highest_education_ramp)
# Inspect colnames
colnames(highest_education_ramp)
#Differences
dim(highest_education_ramp)[1]-dim(highest_education_ramp_raw)[1]
```
# Bind data
```{r bind data}
highest_education <- highest_education_ramp %>%
  bind_rows(highest_education_nbr,
            highest_education_glad_coping,
            highest_education_edgi_coping)

highest_education %>%
  colnames()
```
# Recode categories and combine
NB: Order matters here!
```{r recode and combine categories}
highest_education <- highest_education %>%
  mutate(merged_highest_education =
           case_when(
             employ.what_is_your_highest_level_of_education == 6 |
             employ.phd == 1 ~ "PhD",
             
             employ.what_is_your_highest_level_of_education == 5 |
             employ.postgraduate_degree_or_equivalent == 1 ~ "Postgraduate degree or equivalent",
            
             employ.what_is_your_highest_level_of_education == 4 |
             employ.masters_degree_or_equivalent == 1 ~ "Masters degree or equivalent",
             
             employ.what_is_your_highest_level_of_education == 3 |
             employ.bachelors_degree_or_equivalent == 1 ~ "Bachelors degree or equivalent",
            
              employ.other_professional_qualifications_ == 1 ~ "Other professional qualification",
             
             
             employ.what_is_your_highest_level_of_education == 2 |
              employ.a_levelsas_levels_or_equivalent == 1 ~ "A levels or equivalent",
             
             employ.nvq_or_hnd_or_hnc_or_equivalent == 1 ~ "NVQ, HND, or HNC or equivalent",
            
            
              employ.what_is_your_highest_level_of_education == 1 |
              employ.o_levelsgcses_or_equivalent == 1 |
              employ.cses_or_equivalent == 1 ~ "GCSEs/CSEs or equivalent",
            
              
             employ.what_is_your_highest_level_of_education == 0 |
             employ.none_of_the_above == 1 ~ "No formal qualifications"
             
           ))

# Check
highest_education %>%
  freq(merged_highest_education)
```

# Save data
```{r save data}
highest_education %>%
  saveRDS(paste(filepath_saved_data, "highest_education_refined.rds"))
```

