---
title: "Data_Analysis_EDBeh_SelfHarm"
author: "Helena Davies"
date: "28/01/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

#### Call in library script

```{r source files}
source("./libraries.R")
```

### Read in TAF data
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

##Look at numbers for sample sizes of stratified plots - BINGE EATING 
```{r}

dat.taf %>%
  freq(control)

dat.taf %>%
  freq(eating_disorders_numeric)

dat.taf %>%
  freq(gender_unc)

dat.taf %>%
  freq(age_category)

dat.taf %>%
  freq(cohort_name)
```


#######PLOTS - TAF 

#PLOT - Many people have thoughts that life is not worth living. Have you felt that way?

##**RETRO PREPAN - need to rename these the same as baseline / waves

taf.pandemic_felt_.Wavebaseline: Had you felt that way [life not worth living] before the pandemic?
taf.pandemic_felt.1_.Wavebaseline: Had you felt that way [contemplated harm] before the pandemic?
taf.meant_end_life_pandemic_.Wavebaseline: Before the pandemic, had you deliberately harmed yourself, whether or not you meant to end your life?
```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.worth_living_life_people_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline,
   taf.have_you_contemplated_harming_yourself_.Waveretro_prepan = taf.pandemic_felt.1_.Wavebaseline,
   taf.meant_life_end_weeks_.Waveretro_prepan = taf.meant_end_life_pandemic_.Wavebaseline
    )

```


# First, need to re-structure data so that "wave" is a single column with rows of "1", "2", "3", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```


# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.worth_living_life_people),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.worth_living_life_people_factor <- factor(dat.no.nas$taf.worth_living_life_people)
```

#2. Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```


#4. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.worth_living_life_people_factor) / sum(table(taf.worth_living_life_people_factor))) %>%
  ungroup() %>%
  mutate(taf.worth_living_life_people_factor = rep(levels(dat.no.nas[["taf.worth_living_life_people_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

5. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.worth_living_life_people_factor = fct_relevel(taf.worth_living_life_people_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes, once",
                           "Yes, more than once"))


```


6. PLOT ! [**WHAT TO DO WITH "YES" FROM RAMP RETRO PREPAN?]
```{r}
ggplot(dat_plot,
       aes(x = taf.worth_living_life_people_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent)+ 
  labs(title = str_wrap("Many people have thoughts that life is not worth living. Have you felt that way?", 60),
       x = "Life not worth living",
       y = "Percentage of participants",
       fill = "Time of survey") +
scale_x_discrete(guide = guide_axis(n.dodge=3))

```


##PLOTS - TAF (LIFE NOT WORTH LIVING, 2 WEEKS)
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
#colnames(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```

# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.felt_weeks_past_factor <- factor(dat.no.nas$taf.felt_weeks_past)
```

# Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```

#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past_factor) / sum(table(taf.felt_weeks_past_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past_factor = fct_relevel(taf.felt_weeks_past_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```

7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = str_wrap("Many people have thoughts that life is not worth living. Have you felt that way in the past two weeks?", 60),
       x = "Life not worth living (past 2 weeks)",
       y = "Percentage of participants",
       fill = "Time of survey") +
scale_x_discrete(guide = guide_axis(n.dodge=3))

```

##Check how many participants answered each wave RAMP: taf.felt_weeks_past
```{r}

dat.taf.retroprepan <- dat.taf %>%
  filter(wave == "retro_prepan" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.retroprepan$wave)


dat.taf.baseline <- dat.taf %>%
  filter(wave == "baseline" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.baseline$wave)

dat.taf.0 <- dat.taf %>%
  filter(wave == " 0" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.0$wave)

dat.taf.1 <- dat.taf %>%
  filter(wave == " 1" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.1$wave)

dat.taf.2 <- dat.taf %>%
  filter(wave == " 2" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )


table(dat.taf.2$wave)


dat.taf.3 <- dat.taf %>%
  filter(wave == " 3" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.3$wave)

dat.taf.4 <- dat.taf %>%
  filter(wave == " 4" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.4$wave)


dat.taf.5 <- dat.taf %>%
  filter(wave == " 5" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.5$wave)

dat.taf.6 <- dat.taf %>%
  filter(wave == " 6" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.6$wave)

dat.taf.7 <- dat.taf %>%
  filter(wave == " 7" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.7$wave)

dat.taf.8 <- dat.taf %>%
  filter(wave == " 8" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.8$wave)

dat.taf.9 <- dat.taf %>%
  filter(wave == " 9" &
           cohort_name == "ramp" &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.9$wave)
```
##Check how many participants answered each wave COPING: taf.felt_weeks_past
```{r}

dat.taf.retroprepan <- dat.taf %>%
  filter(wave == "retro_prepan" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.retroprepan$wave)


dat.taf.baseline <- dat.taf %>%
  filter(wave == "baseline" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.baseline$wave)

dat.taf.0 <- dat.taf %>%
  filter(wave == " 0" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.0$wave)

dat.taf.1 <- dat.taf %>%
  filter(wave == " 1" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.1$wave)

dat.taf.2 <- dat.taf %>%
  filter(wave == " 2" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )


table(dat.taf.2$wave)


dat.taf.3 <- dat.taf %>%
  filter(wave == " 3" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.3$wave)

dat.taf.4 <- dat.taf %>%
  filter(wave == " 4" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.4$wave)


dat.taf.5 <- dat.taf %>%
  filter(wave == " 5" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.5$wave)

dat.taf.6 <- dat.taf %>%
  filter(wave == " 6" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.6$wave)

dat.taf.7 <- dat.taf %>%
  filter(wave == " 7" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.7$wave)

dat.taf.8 <- dat.taf %>%
  filter(wave == " 8" &
           (cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad") &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.8$wave)

dat.taf.9 <- dat.taf %>%
  filter(wave == " 9" &
           ((cohort_name == "nbr" |            cohort_name == "coping_edgi" |            cohort_name == "coping_glad")) &
           !is.na(taf.felt_weeks_past)
         )
  

table(dat.taf.9$wave)
```


######STRATIFIED - LIFE NOT WORTH LIVING , 2 WEEKS##########


1. PSYCH DISORDERS

##PLOTS - TAF (LIFE NOT WORTH LIVING, 2 WEEKS) 
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
#colnames(dat.taf)

```

##Filter by PSYCH DISORDER CASES
```{r}

dat.taf <- dat.taf %>%
  filter(control_numeric == 0)

nrow(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```

# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.felt_weeks_past_factor <- factor(dat.no.nas$taf.felt_weeks_past)
```

# Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```

#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past_factor) / sum(table(taf.felt_weeks_past_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past_factor = fct_relevel(taf.felt_weeks_past_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = str_wrap("SELF-REPORTED PSYCH DISORDER ONLY: Many people have thoughts that life is not worth living. Have you felt that way in the past two weeks?", 60),
       x = "Life not worth living (past 2 weeks)",
       y = "Percentage of participants",
       fill = "Time of survey") +
scale_x_discrete(guide = guide_axis(n.dodge=3))

```


1. NO PSYCH DISORDERS

##PLOTS - TAF (LIFE NOT WORTH LIVING, 2 WEEKS) 
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
#colnames(dat.taf)

```

##Filter by PSYCH DISORDER CASES
```{r}

dat.taf <- dat.taf %>%
  filter(control_numeric == 1)

nrow(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past_.Waveretro_prepan = taf.pandemic_felt_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

colnames(dat.taf)

```

# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past),]

#change taf to factor (get rid of 'yes' as its an empty level)
dat.no.nas$taf.felt_weeks_past_factor <- factor(dat.no.nas$taf.felt_weeks_past)
```

# Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```

#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past_factor) / sum(table(taf.felt_weeks_past_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past_factor = fct_relevel(taf.felt_weeks_past_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = str_wrap("NO SELF-REPORTED PSYCH DISORDER ONLY: Many people have thoughts that life is not worth living. Have you felt that way in the past two weeks?", 60),
       x = "Life not worth living (past 2 weeks)",
       y = "Percentage of participants",
       fill = "Time of survey") +
scale_x_discrete(guide = guide_axis(n.dodge=3))

```

















##PLOTS - TAF (CONTEMPLATED HARM, 2 WEEKS)
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.felt_weeks_past.1_.Waveretro_prepan = taf.pandemic_felt.1_.Wavebaseline)

 
```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

#colnames(dat.taf)

```

# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.felt_weeks_past.1),]

#change taf to factor
dat.no.nas$taf.felt_weeks_past.1_factor <- factor(dat.no.nas$taf.felt_weeks_past.1)
```

# Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```

#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.felt_weeks_past.1_factor) / sum(table(taf.felt_weeks_past.1_factor))) %>%
  ungroup() %>%
  mutate(taf.felt_weeks_past.1_factor = rep(levels(dat.no.nas[["taf.felt_weeks_past.1_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.felt_weeks_past.1_factor = fct_relevel(taf.felt_weeks_past.1_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.felt_weeks_past.1_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = str_wrap("Have you contemplated harming yourself in the last two weeks?", 60),
       x = "Contemplated harming yourself (past 2 weeks)",
       y = "Percentage of participants",
       fill = "Time of survey") 

```
##PLOTS - TAF (ACTUAL HARM, 2 WEEKS)
### Read in TAF data (again, because variable needs to be renamed again and data restructured)
taf.meant_life_end_weeks
```{r}
dat.taf <- readRDS(file = "../data_cleaned/dat.taf.rds")
dim(dat.taf)
colnames(dat.taf)

```

##**RETRO PREPAN - need to rename these the same as baseline / waves

```{r}
dat.taf <- dat.taf %>% 
  rename(
   taf.meant_life_end_weeks_.Waveretro_prepan = taf.meant_end_life_pandemic_.Wavebaseline)

```

#1. First, need to re-structure data so that "wave" is a single column with rows of "baseline, 2a, 2b etc", and each taf item is a separate column in which rows are values
```{r}
dat.taf <- dat.taf %>%
  pivot_longer(
    cols = (starts_with("taf") &
              contains(".Wave")),
    names_to = "wave_taf",
    values_to = "value") %>%
  separate(wave_taf, into = c("taf", "wave"), sep = "_.Wave", remove = TRUE) %>%
  pivot_wider(
     names_from = "taf",
     values_from = "value")

#colnames(dat.taf)

```

# Get rid of NAs and change taf to factor
```{r}
#get rid of nas
dat.no.nas <- dat.taf[!is.na(dat.taf$taf.meant_life_end_weeks),]

#change taf to factor
dat.no.nas$taf.meant_life_end_weeks_factor <- factor(dat.no.nas$taf.meant_life_end_weeks)
```

# Change wave to factor and re-order
```{r}

# change order of wave factor 1
dat.no.nas <- dat.no.nas %>%
 mutate(wave_factor = fct_relevel(wave,
                                  "retro_prepan",
                                  "baseline",
                                  "0",
                           "1",
                           "2",
                           "3",
                           "4",
                           "5",
                           "6",
                           "7",
                           "8",
                           "9")
        )


#Check that this worked

summary(dat.no.nas$wave_factor)
```

#3. Rename waves to dates
```{r}

##Rename waves

levels(dat.no.nas$wave_factor)[1] <- "Retrospective prepandemic"

levels(dat.no.nas$wave_factor)[2] <- "March 2020"

levels(dat.no.nas$wave_factor)[3] <- "April 2020" 

levels(dat.no.nas$wave_factor)[4] <- "May 2020"

levels(dat.no.nas$wave_factor)[5] <- "June 2020"

levels(dat.no.nas$wave_factor)[6] <- "July 2020"

levels(dat.no.nas$wave_factor)[7] <- "August 2020"

levels(dat.no.nas$wave_factor)[8] <- "September 2020"

levels(dat.no.nas$wave_factor)[9] <- "October 2020"

levels(dat.no.nas$wave_factor)[10] <- "November 2020"

levels(dat.no.nas$wave_factor)[11] <- "December 2020"

levels(dat.no.nas$wave_factor)[12] <- "January 2020"

```

#5. Format data to plot
```{r}
#get data in format to plot
dat_plot <- dat.no.nas %>%
  group_by(wave_factor) %>%
  dplyr::summarise(wcount = table(taf.meant_life_end_weeks_factor) / sum(table(taf.meant_life_end_weeks_factor))) %>%
  ungroup() %>%
  mutate(taf.meant_life_end_weeks_factor = rep(levels(dat.no.nas[["taf.meant_life_end_weeks_factor"]]),
                    length(levels(dat.no.nas[["wave_factor"]]))))


```

6. Change taf variable to ordered factor
```{r}
dat_plot <- dat_plot %>%
  mutate(taf.meant_life_end_weeks_factor = fct_relevel(taf.meant_life_end_weeks_factor,
                           "Prefer not to answer",
                           "No",
                           "Yes"))



```


7. PLOT !
```{r}
ggplot(dat_plot,
       aes(x = taf.meant_life_end_weeks_factor,
           y = wcount,
           fill = wave_factor)) +
  geom_bar(aes(group = wave_factor),
           stat = "identity",
           position = "dodge",
           colour = "black") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = str_wrap("In the last two weeks, have you deliberately harmed yourself, whether or not you meant to end your life?", 60),
       x = "Contemplated harming yourself (past 2 weeks)",
       y = "Percentage of participants",
       fill = "Time of survey") 

```































